---
title: "MR fed HP Data Analysis"
author: "Holly V. Moeller"
date: "2024-05-11"
output: html_document
---

# Setup

## Optional commands
```{r}
# rm(list = ls()) # clear the environment

```

## Loading packages:
```{r}
knitr::opts_chunk$set(echo = TRUE)

package.list <- c("dplyr","ggplot2","stringr","pracma",
                  "Rmisc","tidyr","cowplot",
                  "lemon",'flowPeaks',"sciplot",'ggExtra')

if(!all(package.list %in% installed.packages()[,"Package"])){
  install.packages(package.list[!(package.list %in% installed.packages()[,"Package"])])
}

library(dplyr)
library(ggplot2)
library(stringr)
library(pracma)
library(Rmisc)
library(tidyr)
library(cowplot)
library(lemon)
library(flowPeaks)
library(sciplot)
library(ggExtra)
```

## Loading special functions:
The Meso.flowPeaks function is a wrapper for flowPeaks that tailors its use to FlowCam data with Mesodinium and cryptophytes. The function takes a subset of data with just one organism type (either Mesodinium or cryptophytes) and partitions it using the k-means algorithm in flowPeaks. It then uses breakpoints (that can be set by the user, or which are automated) to identify the plastid colours associated with each cluster identified by flowPeaks.

The function outputs an annotated dataset as well as summary statistics.
```{r}
Meso.flowPeaks <- function(dataset,flask,day,create_plot = F,unknown.partition = 5.5, bluegreen.partition = 4.5){
  
  # Function last updated: 21 November 2023
  
  # Function inputs:
  #  dataset = csv file from the FlowCam
  #  flask = ID number for the flask
  #  day = experimental day
  #  create_plot argument (T = makes plots, F = automatic setting; doesn't make plots)
  #  unknown.partition = channel 1 partition for "unknown" cell types. Default is at 5.5
  #  bluegreen.partition = channel 2 partition for bluegreen plastids. Default is at 4.5
  
  
  # Step 1: Partition dataset to just fluorescent particles
  dataset.fluo <- dataset[dataset$Ch1.Peak>0,]
  dataset.fluo <- dataset.fluo[dataset.fluo$Ch2.Peak>0,]
  
  # Step 2: Use flowPeaks package to fit and visualize the number of clusters of points
  invisible(capture.output(fp <- suppressMessages(flowPeaks(dataset.fluo[,c("Ch1.Peak",'Ch2.Peak')],tol=.1,h0=.4))))
      # The "capture.output" function captures the printed output of the flowPeaks function
      # The "invisible" function suppresses that output so it doesn't automatically print.
      # The "suppressMessages" function suppresses the messages output of flowPeaks

  # Step 3: Extract cluster assignments
  dataset.fluo$peak <- fp$peaks.cluster

  # Step 4: Assign clusters to colors (or unknown)
  fp.data <- as.data.frame(summary(fp))
  fp.data$plastid.color <- 'red' # Presume plastids are red in color
  for(i in 1:dim(fp.data)[1]){
    if(fp.data$Ch1.Peak.center[i] < unknown.partition){ # If they fall below the unknown threshold, assign them "black" color for unknown
      fp.data$plastid.color[i] <- 'black'
    } else{ #If not unknown, then assign them "blue" color for bluegreen plastid type
    if(fp.data$Ch2.Peak.center[i] < bluegreen.partition){
      fp.data$plastid.color[i] <- 'blue'
    }
  }}
  dataset.fluo$peak.Ch1 <- fp.data$Ch1.Peak.center[match(dataset.fluo$peak,fp.data$cluster.id)]
  dataset.fluo$peak.Ch2 <- fp.data$Ch2.Peak.center[match(dataset.fluo$peak,fp.data$cluster.id)]
  dataset.fluo$plastidcolor <- fp.data$plastid.color[match(dataset.fluo$peak,fp.data$cluster.id)]
  
  # Step 5: Map fluorescent data back onto the dataset for export.
  dataset.analyzed <- dataset
  dataset.analyzed$plastidcolor <- dataset.fluo$plastidcolor[match(dataset.analyzed$Capture.ID,dataset.fluo$Capture.ID)]
  if(dim(dataset.analyzed[is.na(dataset.analyzed$plastidcolor),])[1]>0){
  dataset.analyzed[is.na(dataset.analyzed$plastidcolor),]$plastidcolor <- 'nonfluorescent'}
  dataset.analyzed$plastidcolor <- factor(dataset.analyzed$plastidcolor,levels=c('red','blue','black','nonfluorescent'))
  
  # Step 6: Calculate summary statistics
  counts <- as.data.frame(t(as.matrix(table(dataset.analyzed$plastidcolor))))
  counts$tot.red <- counts$red + (counts$black + counts$nonfluorescent)*counts$red/(counts$red+counts$blue)
  counts$tot.blue <- counts$blue + (counts$black + counts$nonfluorescent)*counts$blue/(counts$red+counts$blue)
  counts$tot.meso <- counts$tot.blue+counts$tot.red
  Ch1.peaks <- as.data.frame(t(as.matrix(tapply(dataset.analyzed$Ch1.Peak,dataset.analyzed$plastidcolor,FUN=mean))))
  Ch2.peaks <- as.data.frame(t(as.matrix(tapply(dataset.analyzed$Ch2.Peak,dataset.analyzed$plastidcolor,FUN=mean))))
  Ch1.peaks.sd <- as.data.frame(t(as.matrix(tapply(dataset.analyzed$Ch1.Peak,dataset.analyzed$plastidcolor,FUN=sd))))
  Ch2.peaks.sd <- as.data.frame(t(as.matrix(tapply(dataset.analyzed$Ch2.Peak,dataset.analyzed$plastidcolor,FUN=sd))))
  
  # Step 7: Make plots if desired
  if(create_plot==T){
    
    # 1. Baseline plot of all data
    par(mfrow=c(2,2))
    par(mar=c(2,4,2.5,0.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,ylab='Channel 2 peak (phycoerythrin)')
    text(min(dataset.fluo$Ch1.Peak),max(dataset.fluo$Ch2.Peak),dataset.fluo$Class[1],pos=4)
    text(min(dataset.fluo$Ch1.Peak),max(dataset.fluo$Ch2.Peak)-.15,paste(flask,', Day ',day),pos=4)
    
    # 2. Plot of flowpeaks package partitions
    par(mar=c(2,2,2.5,2.5))
    plot(fp)
    
    # 3. Plot of data with cluster assignments
    par(mar=c(4,4,.5,.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,col=c('red','blue','cyan','green')[as.factor(dataset.fluo$peak)],xlab='Channel 1 peak (chlorophyll)',ylab='Channel 2 peak (phycoerythrin)')
    
    # 4. Plot of data assigned by plastid type
    par(mar=c(4,2,.5,2.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,col=dataset.fluo$plastidcolor,xlab='Channel 1 peak (chlorophyll)')
    
  }

  Res <- list('dataset.analyzed' = dataset.analyzed, 'counts' = counts, 'Ch1.peaks' = Ch1.peaks, 'Ch2.peaks' = Ch2.peaks,'Ch1.peaks.sd' = Ch1.peaks.sd, 'Ch2.peaks.sd' = Ch2.peaks.sd)
  Res
  
  
}
```

Transparency for color ramps: https://github.com/mylesmharrison/colorRampPaletteAlpha/blob/master/colorRampPaletteAlpha.R
```{r}
# addalpha()
addalpha <- function(colors, alpha=1.0) {
  r <- col2rgb(colors, alpha=T)
  # Apply alpha
  r[4,] <- alpha*255
  r <- r/255.0
  return(rgb(r[1,], r[2,], r[3,], r[4,]))
}

# colorRampPaletteAlpha()
colorRampPaletteAlpha <- function(colors, n=32, interpolate='linear') {
  # Create the color ramp normally
  cr <- colorRampPalette(colors, interpolate=interpolate)(n)
  # Find the alpha channel
  a <- col2rgb(colors, alpha=T)[4,]
  # Interpolate
	if (interpolate=='linear') {
		l <- approx(a, n=n)
	} else {
		l <- spline(a, n=n)
	}
	l$y[l$y > 255] <- 255 # Clamp if spline is > 255
	cr <- addalpha(cr, l$y/255.0)
	return(cr)
}
```


## Setting up plotting commands:
```{r}
# Colors from Hiroshige and Cassatt2, Metbrewer, https://github.com/BlakeRMills/MetBrewer
TAcol <- rgb(230/255,98/255,84/255)
TAcol.bg <- rgb(230/255,98/255,84/255,.5)
HPcol <- rgb(114/255,187/255,213/255)
HPcol.bg <- rgb(114/255,187/255,213/255,.5)
Bothcol <- rgb(144/255,113/255,158/255)
Bothcol.bg <- rgb(144/255,113/255,158/255,.5)

Chlcol <- rgb(127/255,160/255,116/255)
Chlcol.bg <- rgb(127/255,160/255,116/255,.5)

HPcols <- c('white',HPcol)
HPcols.bg <- c('white',HPcol.bg)
TAcols <- c('white',TAcol)
TAcols.bg <- c('white',TAcol.bg)
Chlcols <- c('white',Chlcol)
Chlcols.bg <- c('white',Chlcol.bg)

# Color ramps
#TAto00cols2 <- colorRampPalette(c('indianred3','gray90'))
#TAto00cols2 <- colorRampPalette(c(TAcol,'goldenrod'))
#TAto00colset2 <- addalpha(TAto00cols2(length(expt.day)),.5)

#TAtoHPcols2 <- colorRampPalette(c('indianred3','gray90','paleturquoise4'))
TAtoHPcols2 <- colorRampPalette(c(TAcol,'gray90',HPcol))
```


## Loading datasets:
```{r}

```


# Supplement: FlowCam - Confocal calibration

### Setup FlowCam file structure
```{r}
#Input the location of your main folder for the current experiment.
root_folder <- "/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/FlowCam/DataFiles"

#In the main folder create a folder name CSV_files, if named other wise change "/CSV_files" accordingly
CSV_folder <- paste(root_folder,"/CSV_files",sep = "")

#List the sub-folders of the current experiment, this would usually be one folder for each sampling day.
Folder_list <- c("D1","D3","D6","D9","D12","D15","D17","D19")

expt.day <- Folder_list

knitr::opts_knit$set(root.dir = root_folder)

#A .csv file should be created with extra meta-data, such as data for sampling time and dilution. If other data is acquired, such as pigment extractions, include these in the this file as well.
expt.meta <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/FlowCam/Mrubrum_fedHP_FunctionalResponseCurves - Calib_DilTime.csv")

calib.counts <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Mrubrum_fedHP_FunctionalResponseCurves - Calib_Counts.csv",header=T)

```

### Analyze FlowCam raw data to generate spreadsheet summarizing results

This chunk loops over the specified folders to generate a spreadsheet summarizing the Mesodinium and cryptophyte abundances by plastid type and experimental conditions.

```{r,fig.height=8,fig.width=8}
#Using the previously defined Folder_list, a for loop is created to access each folder one at a time, and within those folder each sample is then accessed one at a time.
#Each data set is being processed using the MRMC.partitioning function, which distinguished Red Chloroplast MC from blue-green Chloroplast MC. By using the meta-data stored in the file-name a new data-sheet is created with the desired data where each row is from a single sample from a single day.

create_plot_meso = F #If TRUE, the partitioning will output partitioned Ch1 vs Ch2 plots -- MESODINIUM VERSION
create_plot_prey = F #If TRUE, the partitioning will output partitioned Ch1 vs Ch2 plots -- PREY VERSION

unk.part.Meso = 5.5 # unknown partition for Mesodinium
bg.part.Meso = 4.5 # blue-green partition for Mesodinium
unk.part.prey = 0 # unknown partition for cryptophytes
bg.part.prey = 4.5 # blue-green partition for cryptophytes

#The first for-loop is created to open the folder of the individual sampling day in the order as they were defined (usually chronologically)
for(dir_idx in 1:length(Folder_list)){
  
  #The working directory is set to the folder containing one days worth of data.
  current_folder <- paste(root_folder,"/",Folder_list[dir_idx],sep = "")
  
  #Recording the current experimental day
  today <- expt.day[dir_idx]
  
  #here the columns to retrieve timestamp and dilution is defined.
  dil_name <- paste("Dil.",today,sep = "")
  time_name <- paste("TS.",today,sep = "")
  
  #The function list.files(current_folder), will create a list of files that are located in the folder, and by using this list of files, a new for-loop is created accessing each file consecutively.
  for(i in 1:length(list.files(current_folder))){
    
    #extracting meta data from the file name
    #Characters 1 to 7 is the Flask index
    name_flask <- substring(list.files(current_folder)[i],
                            first = 1,
                            last = 7)
    
    #assigning flask index as a number
    num_flask <- as.integer(substring(list.files(current_folder)[i],
                                      first = 6,
                                      last = 7))
    
    #Characters 9 to 12 is the Mesodinium pre-experiment plastid type
    Meso_designation <- substring(list.files(current_folder)[i],
                                  first = 9,
                                  last = 12)
    
    #Characters 14 through 15 indicate the prey being fed during the experiment
    prey_designation <- substring(list.files(current_folder)[i],
                                  first = 14,
                                  last = 15)
    
    #Character 20 is the replicate indicator
    expt_rep <- substring(list.files(current_folder)[i],
                          first = 20,
                          last = 20)
    
    #The dilution factor is extracted from the meta-data data-sheet in the root-folder
    flask_dil <- expt.meta[expt.meta$Flask == num_flask,
                           names(expt.meta) == dil_name]
    
    #Relative time from beginning of experiment is extracted
    flask_time <- expt.meta[expt.meta$Flask == num_flask,
                           names(expt.meta) == time_name]
    
    medium <- expt.meta[expt.meta$Flask == num_flask,"Medium"]
    
    #The .csv file is loaded here, and extra columns are added with the additional meta-data required for the data-processing
    file.name <- paste(current_folder,"/",list.files(current_folder)[i],sep = "")
    
    vec <- read.csv(file.name) %>% 
      mutate(Flask = name_flask,
             replicate = expt_rep,
             Meso = Meso_designation,
             Prey = prey_designation,
             Day = as.numeric(substring(expt.day[dir_idx],2)))
    
    #Because the flow-cam keeps counting the seconds when resetting the pump, a constant is multiplied to the Elapsed time to get the correct volume aspirated. This constant however was calculated from using the 0.5 ml pump, so a new value is probably needed for the 1 ml pump.
    Asp.vol <- (max(vec$Elapsed.Time*0.967)/60)*0.150
    
    #R-vector containing the raw data-set with both Mesodinium and Crypotphyte data
    vec.raw <- vec
    
    Meso_filter <- vec.raw$Class == "Mesodinium"
    
    #Creating an R-vector that only contains the data classified as Mesodinium
    vec <- vec.raw[Meso_filter,]
    
    #Creating an R-vector that only contains the data classified as Cryptophyte (or rather it only contains data that has not been classified as Meosdinium)
    vec2 <- vec.raw[!Meso_filter,]
    
    #On the first sample of each experimental day, an empty spreadsheet is created for both Prey and Mesodinium. This will be populated as the for-loop iterates through each sample.
    if(i == 1){
      FCDP_meso <- vec
      FCDP_prey <- vec2
      
      #Creating data-frame for partitioned data results
      All.Results <- as.data.frame(1:length(list.files(current_folder)))
      
      colnames(All.Results) <- c("Flask")     # Columns 1-8: Metadata
      All.Results$Day <- NaN
      All.Results$Time <- NaN                 
      All.Results$Dilution <- NaN             
      All.Results$Aspirated.vol <- NaN        
      All.Results$Meso <- NaN                 
      All.Results$Prey <- NaN                 
      All.Results$Replicate <- NaN            
      All.Results$Medium <- NaN               
      All.Results$M.Red <- NaN               # Columns 10-16; from Res$counts
      All.Results$M.Blue <- NaN              
      All.Results$M.Undefined <- NaN         
      All.Results$M.Nonfluorescent <- NaN
      All.Results$M.TotRed <- NaN
      All.Results$M.TotBlue <- NaN
      All.Results$TotalMeso <- NaN          
      All.Results$M.Red.meanCh1peak <- NaN               # Columns 17-20; from Res$Ch1.peaks
      All.Results$M.Blue.meanCh1peak <- NaN              
      All.Results$M.Undefined.meanCh1peak <- NaN         
      All.Results$M.Nonfluorescent.meanCh1peak <- NaN
      All.Results$M.Red.sdCh1peak <- NaN               # Columns 21-24; from Res$Ch1.sds
      All.Results$M.Blue.sdCh1peak <- NaN              
      All.Results$M.Undefined.sdCh1peak <- NaN         
      All.Results$M.Nonfluorescent.sdCh1peak <- NaN
      All.Results$M.Red.meanCh2peak <- NaN               # Columns 25-28; from Res$Ch2.peaks
      All.Results$M.Blue.meanCh2peak <- NaN              
      All.Results$M.Undefined.meanCh2peak <- NaN         
      All.Results$M.Nonfluorescent.meanCh2peak <- NaN  
      All.Results$M.Red.sdCh2peak <- NaN               # Columns 29-32; from Res$Ch2.sds
      All.Results$M.Blue.sdCh2peak <- NaN              
      All.Results$M.Undefined.sdCh2peak <- NaN         
      All.Results$M.Nonfluorescent.sdCh2peak <- NaN  
      
      #Adding columns for cryptophytes
      All.Results$C.Red <- NaN               # Columns 9-15; from Res$counts
      All.Results$C.Blue <- NaN              
      All.Results$C.Undefined <- NaN         
      All.Results$C.Nonfluorescent <- NaN
      All.Results$C.TotRed <- NaN
      All.Results$C.TotBlue <- NaN
      All.Results$TotalCrypto <- NaN          
      All.Results$C.Red.meanCh1peak <- NaN               # Columns 16-19; from Res$Ch1.peaks
      All.Results$C.Blue.meanCh1peak <- NaN              
      All.Results$C.Undefined.meanCh1peak <- NaN         
      All.Results$C.Nonfluorescent.meanCh1peak <- NaN
      All.Results$C.Red.sdCh1peak <- NaN               # Columns 20-23; from Res$Ch1.sds
      All.Results$C.Blue.sdCh1peak <- NaN              
      All.Results$C.Undefined.sdCh1peak <- NaN         
      All.Results$C.Nonfluorescent.sdCh1peak <- NaN
      All.Results$C.Red.meanCh2peak <- NaN               # Columns 24-27; from Res$Ch2.peaks
      All.Results$C.Blue.meanCh2peak <- NaN              
      All.Results$C.Undefined.meanCh2peak <- NaN         
      All.Results$C.Nonfluorescent.meanCh2peak <- NaN  
      All.Results$C.Red.sdCh2peak <- NaN               # Columns 28-31; from Res$Ch2.sds
      All.Results$C.Blue.sdCh2peak <- NaN              
      All.Results$C.Undefined.sdCh2peak <- NaN         
      All.Results$C.Nonfluorescent.sdCh2peak <- NaN  
      
    } else{
      FCDP_prey <- rbind(FCDP_prey,vec2)
      FCDP_meso <- rbind(FCDP_meso,vec)
    }
    
    # Add relevant data for this sample
    All.Results$Flask[i] <- name_flask
    All.Results$Day[i] <- today
    All.Results$Time[i] <- flask_time
    All.Results$Dilution[i] <- flask_dil
    All.Results$Aspirated.vol[i] <- round(Asp.vol,3)
    All.Results$Meso[i] <- Meso_designation
    All.Results$Prey[i] <- prey_designation
    All.Results$Replicate[i] <- expt_rep
    All.Results$Medium[i] <- medium
    
    #Running the partitioning function for Mesodinium

    if(dim(vec)[1] > 0){ # If there are Mesodinium in the dataset
      Res <- Meso.flowPeaks(vec,name_flask,today,create_plot = create_plot_meso,unknown.partition = unk.part.Meso, bluegreen.partition = bg.part.Meso)
      #Assigning partitioned data for Mesodinium
      All.Results[i,10:16] <- Res$counts
      All.Results[i,17:20] <- Res$Ch1.peaks
      All.Results[i,21:24] <- Res$Ch1.peaks.sd
      All.Results[i,25:28] <- Res$Ch2.peaks
      All.Results[i,29:32] <- Res$Ch2.peaks.sd
    }
    
    if(dim(vec2)[1] > 0){ # If there are cryptophytes in the dataset
      #Running flowPeaks for Prey
      Res.crypto <- Meso.flowPeaks(vec2,name_flask,today,create_plot = create_plot_prey,unknown.partition = unk.part.prey, bluegreen.partition = bg.part.prey)
      #Assigning partitioned data for Prey
      All.Results[i,33:39] <- Res.crypto$counts
      All.Results[i,40:43] <- Res.crypto$Ch1.peaks
      All.Results[i,44:47] <- Res.crypto$Ch1.peaks.sd
      All.Results[i,48:51] <- Res.crypto$Ch2.peaks
      All.Results[i,52:55] <- Res.crypto$Ch2.peaks.sd
    }
    
    if(i == length(list.files(current_folder))){
        FCDP_prey <- FCDP_prey %>% mutate(Partition = "Prey")
        FCDP_meso <- FCDP_meso %>% mutate(Partition = "Mesodinium")
        FCDP_all <- rbind(FCDP_meso,FCDP_prey)
      
      
      Res_name <- paste(CSV_folder,"/Summary_",expt.day[dir_idx],".csv",sep = "")
      FCDP_name <- paste(CSV_folder,"/FCDP_all_",expt.day[dir_idx],".csv",sep = "")
      
      write.csv(All.Results,Res_name,row.names = F)
      write.csv(FCDP_all,FCDP_name,row.names = F)
    }
  }
  
  if(dir_idx == 1){
    All.Results.Concat <- All.Results
  } else{
    All.Results.Concat <- rbind(All.Results.Concat, All.Results)
  }
  
  if(dir_idx == length(Folder_list)){
    All_res_name <- paste("All_Summary",".csv",sep='')
    write.csv(All.Results.Concat,All_res_name,row.names = F)
  }
  
}

```

Next, we concatenate the relevant data into a single spreadsheet, and filter to make sure we are only using data from Mesodinium cells that had a fluorescent signal.

```{r}
# Concatenate FlowCam data
FCDP_name <- paste(CSV_folder,"/FCDP_all_",expt.day[1],".csv",sep = "")
FCDP <- read.csv(FCDP_name)
FCDP.Meso.00 <- FCDP[FCDP$Class=='Mesodinium' & FCDP$Prey=='00',]
FCDP.Meso.HP <- FCDP[FCDP$Class=='Mesodinium' & FCDP$Prey=='HP',]
FCDP.Meso.TA <- FCDP[FCDP$Class=='Mesodinium' & FCDP$Prey=='TA',]

for(i in 2:length(expt.day)){
  FCDP_name <- paste(CSV_folder,"/FCDP_all_",expt.day[i],".csv",sep = "")
  FCDP <- read.csv(FCDP_name)
  FCDP.Meso.00 <- rbind(FCDP.Meso.00,FCDP[FCDP$Class=='Mesodinium' & FCDP$Prey=='00',])
  FCDP.Meso.HP <- rbind(FCDP.Meso.HP,FCDP[FCDP$Class=='Mesodinium' & FCDP$Prey=='HP',])
  FCDP.Meso.TA <- rbind(FCDP.Meso.TA,FCDP[FCDP$Class=='Mesodinium' & FCDP$Prey=='TA',])
}

# Extract just fluorescent Mesodinium cells
# Step 1: Partition dataset to just fluorescent particles
dataset.fluo <- FCDP.Meso.HP[FCDP.Meso.HP$Ch1.Peak>0,]
dataset.fluo <- dataset.fluo[dataset.fluo$Ch2.Peak>0,]
  
# Step 2: Use flowPeaks package to fit and visualize the number of clusters of points
invisible(capture.output(fp <- suppressMessages(flowPeaks(dataset.fluo[,c("Ch1.Peak",'Ch2.Peak')],tol=.1,h0=.4))))

# Step 3: Extract cluster assignments
dataset.fluo$peak <- fp$peaks.cluster

# Step 4: Assign clusters to colors (or unknown)
fp.data <- as.data.frame(summary(fp))
fp.data$plastid.color <- 'red' # Presume plastids are red in color
for(i in 1:dim(fp.data)[1]){
  if(fp.data$Ch1.Peak.center[i] < unk.part.Meso){ # If they fall below the unknown threshold, assign them "black" color for unknown
    fp.data$plastid.color[i] <- 'black'
  } else{ #If not unknown, then assign them "blue" color for bluegreen plastid type
  if(fp.data$Ch2.Peak.center[i] < bg.part.Meso){
    fp.data$plastid.color[i] <- 'blue'
  }
}}
dataset.fluo$peak.Ch1 <- fp.data$Ch1.Peak.center[match(dataset.fluo$peak,fp.data$cluster.id)]
dataset.fluo$peak.Ch2 <- fp.data$Ch2.Peak.center[match(dataset.fluo$peak,fp.data$cluster.id)]
dataset.fluo$plastidcolor <- fp.data$plastid.color[match(dataset.fluo$peak,fp.data$cluster.id)]
  
# Step 5: Map fluorescent data back onto the dataset for export.
dataset.analyzed <- FCDP.Meso.HP
dataset.analyzed$plastidcolor <- dataset.fluo$plastidcolor[match(dataset.analyzed$Capture.ID,dataset.fluo$Capture.ID)]
if(dim(dataset.analyzed[is.na(dataset.analyzed$plastidcolor),])[1]>0){
dataset.analyzed[is.na(dataset.analyzed$plastidcolor),]$plastidcolor <- 'nonfluorescent'}
dataset.analyzed$plastidcolor <- factor(dataset.analyzed$plastidcolor,levels=c('red','blue','black','nonfluorescent'))
  
# 1. Baseline plot of all data
    par(mfrow=c(2,2))
    par(mar=c(2,4,2.5,0.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,ylab='Channel 2 peak (phycoerythrin)')
    
    # 2. Plot of flowpeaks package partitions
    par(mar=c(2,2,2.5,2.5))
    plot(fp)
    
    # 3. Plot of data with cluster assignments
    par(mar=c(4,4,.5,.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,col=c('red','blue','cyan','green')[as.factor(dataset.fluo$peak)],xlab='Channel 1 peak (chlorophyll)',ylab='Channel 2 peak (phycoerythrin)')
    
    # 4. Plot of data assigned by plastid type
    par(mar=c(4,2,.5,2.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,col=dataset.fluo$plastidcolor,xlab='Channel 1 peak (chlorophyll)')

FCDP.Meso.HP.hasplastid <- dataset.fluo[dataset.fluo$plastidcolor!='black',]


# Extract just fluorescent Mesodinium cells
# Step 1: Partition dataset to just fluorescent particles
dataset.fluo <- FCDP.Meso.00[FCDP.Meso.00$Ch1.Peak>0,]
dataset.fluo <- dataset.fluo[dataset.fluo$Ch2.Peak>0,]
  
# Step 2: Use flowPeaks package to fit and visualize the number of clusters of points
invisible(capture.output(fp <- suppressMessages(flowPeaks(dataset.fluo[,c("Ch1.Peak",'Ch2.Peak')],tol=.1,h0=.4))))

# Step 3: Extract cluster assignments
dataset.fluo$peak <- fp$peaks.cluster

# Step 4: Assign clusters to colors (or unknown)
fp.data <- as.data.frame(summary(fp))
fp.data$plastid.color <- 'red' # Presume plastids are red in color
for(i in 1:dim(fp.data)[1]){
  if(fp.data$Ch1.Peak.center[i] < unk.part.Meso){ # If they fall below the unknown threshold, assign them "black" color for unknown
    fp.data$plastid.color[i] <- 'black'
  } else{ #If not unknown, then assign them "blue" color for bluegreen plastid type
  if(fp.data$Ch2.Peak.center[i] < bg.part.Meso){
    fp.data$plastid.color[i] <- 'blue'
  }
}}
dataset.fluo$peak.Ch1 <- fp.data$Ch1.Peak.center[match(dataset.fluo$peak,fp.data$cluster.id)]
dataset.fluo$peak.Ch2 <- fp.data$Ch2.Peak.center[match(dataset.fluo$peak,fp.data$cluster.id)]
dataset.fluo$plastidcolor <- fp.data$plastid.color[match(dataset.fluo$peak,fp.data$cluster.id)]
  
# Step 5: Map fluorescent data back onto the dataset for export.
dataset.analyzed <- FCDP.Meso.00
dataset.analyzed$plastidcolor <- dataset.fluo$plastidcolor[match(dataset.analyzed$Capture.ID,dataset.fluo$Capture.ID)]
if(dim(dataset.analyzed[is.na(dataset.analyzed$plastidcolor),])[1]>0){
dataset.analyzed[is.na(dataset.analyzed$plastidcolor),]$plastidcolor <- 'nonfluorescent'}
dataset.analyzed$plastidcolor <- factor(dataset.analyzed$plastidcolor,levels=c('red','blue','black','nonfluorescent'))
  
# 1. Baseline plot of all data
    par(mfrow=c(2,2))
    par(mar=c(2,4,2.5,0.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,ylab='Channel 2 peak (phycoerythrin)')
    
    # 2. Plot of flowpeaks package partitions
    par(mar=c(2,2,2.5,2.5))
    plot(fp)
    
    # 3. Plot of data with cluster assignments
    par(mar=c(4,4,.5,.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,col=c('red','blue','cyan','green')[as.factor(dataset.fluo$peak)],xlab='Channel 1 peak (chlorophyll)',ylab='Channel 2 peak (phycoerythrin)')
    
    # 4. Plot of data assigned by plastid type
    par(mar=c(4,2,.5,2.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,col=dataset.fluo$plastidcolor,xlab='Channel 1 peak (chlorophyll)')

FCDP.Meso.00.hasplastid <- dataset.fluo[dataset.fluo$plastidcolor!='black',]

# Extract just fluorescent Mesodinium cells
# Step 1: Partition dataset to just fluorescent particles
dataset.fluo <- FCDP.Meso.TA[FCDP.Meso.TA$Ch1.Peak>0,]
dataset.fluo <- dataset.fluo[dataset.fluo$Ch2.Peak>0,]
  
# Step 2: Use flowPeaks package to fit and visualize the number of clusters of points
invisible(capture.output(fp <- suppressMessages(flowPeaks(dataset.fluo[,c("Ch1.Peak",'Ch2.Peak')],tol=.1,h0=.4))))

# Step 3: Extract cluster assignments
dataset.fluo$peak <- fp$peaks.cluster

# Step 4: Assign clusters to colors (or unknown)
fp.data <- as.data.frame(summary(fp))
fp.data$plastid.color <- 'red' # Presume plastids are red in color
for(i in 1:dim(fp.data)[1]){
  if(fp.data$Ch1.Peak.center[i] < unk.part.Meso){ # If they fall below the unknown threshold, assign them "black" color for unknown
    fp.data$plastid.color[i] <- 'black'
  } else{ #If not unknown, then assign them "blue" color for bluegreen plastid type
  if(fp.data$Ch2.Peak.center[i] < bg.part.Meso){
    fp.data$plastid.color[i] <- 'blue'
  }
}}
dataset.fluo$peak.Ch1 <- fp.data$Ch1.Peak.center[match(dataset.fluo$peak,fp.data$cluster.id)]
dataset.fluo$peak.Ch2 <- fp.data$Ch2.Peak.center[match(dataset.fluo$peak,fp.data$cluster.id)]
dataset.fluo$plastidcolor <- fp.data$plastid.color[match(dataset.fluo$peak,fp.data$cluster.id)]
  
# Step 5: Map fluorescent data back onto the dataset for export.
dataset.analyzed <- FCDP.Meso.TA
dataset.analyzed$plastidcolor <- dataset.fluo$plastidcolor[match(dataset.analyzed$Capture.ID,dataset.fluo$Capture.ID)]
if(dim(dataset.analyzed[is.na(dataset.analyzed$plastidcolor),])[1]>0){
dataset.analyzed[is.na(dataset.analyzed$plastidcolor),]$plastidcolor <- 'nonfluorescent'}
dataset.analyzed$plastidcolor <- factor(dataset.analyzed$plastidcolor,levels=c('red','blue','black','nonfluorescent'))
  
# 1. Baseline plot of all data
    par(mfrow=c(2,2))
    par(mar=c(2,4,2.5,0.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,ylab='Channel 2 peak (phycoerythrin)')
    
    # 2. Plot of flowpeaks package partitions
    par(mar=c(2,2,2.5,2.5))
    plot(fp)
    
    # 3. Plot of data with cluster assignments
    par(mar=c(4,4,.5,.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,col=c('red','blue','cyan','green')[as.factor(dataset.fluo$peak)],xlab='Channel 1 peak (chlorophyll)',ylab='Channel 2 peak (phycoerythrin)')
    
    # 4. Plot of data assigned by plastid type
    par(mar=c(4,2,.5,2.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,col=dataset.fluo$plastidcolor,xlab='Channel 1 peak (chlorophyll)')

FCDP.Meso.TA.hasplastid <- dataset.fluo[dataset.fluo$plastidcolor!='black',]
```

### Import and concatenate Confocal data
```{r}
# Day 01
F01D01 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F01_D01_StarvedA_Data_processeddata.csv"); F01D01$Rep <- "A"
F03D01 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F03_D01_StarvedB_Data_processeddata.csv"); F03D01$Rep <- "B"
F05D01 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F05_D01_StarvedC_Data_processeddata.csv"); F05D01$Rep <- "C"
StarvedD01 <- rbind(F01D01,F03D01,F05D01)
colnames(StarvedD01) <- c("StackID","Pixels","PropDAPI","PropPE","PropPC","Rep")

F02D01 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F02_D01_HPFedA_Data_processeddata.csv"); F02D01$Rep <- "A"
F04D01 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F04_D01_HPFedB_Data_processeddata.csv"); F04D01$Rep <- "B"
F06D01 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F06_D01_HPFedC_Data_processeddata.csv"); F06D01$Rep <- "C"
HPFedD01 <- rbind(F02D01,F04D01,F06D01)
colnames(HPFedD01) <- c("StackID","Pixels","PropDAPI","PropPE","PropPC","Rep")

# Day 03
F01D03 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F01_D03_StarvedA_Data_processeddata.csv"); F01D03$Rep <- "A"
F03D03 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F03_D03_StarvedB_Data_processeddata.csv"); F03D03$Rep <- "B"
F05D03 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F05_D03_StarvedC_Data_processeddata.csv"); F05D03$Rep <- "C"
StarvedD03 <- rbind(F01D03,F03D03,F05D03)
colnames(StarvedD03) <- c("StackID","Pixels","PropDAPI","PropPE","PropPC","Rep")

F02D03 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F02_D03_HPFedA_Data_processeddata.csv"); F02D03$Rep <- "A"
F04D03 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F04_D03_HPFedB_Data_processeddata.csv"); F04D03$Rep <- "B"
F06D03 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F06_D03_HPFedC_Data_processeddata.csv"); F06D03$Rep <- "C"
HPFedD03 <- rbind(F02D03,F04D03,F06D03)
colnames(HPFedD03) <- c("StackID","Pixels","PropDAPI","PropPE","PropPC","Rep")

# Day 06
F01D06 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F01_D06_StarvedA_Data_processeddata.csv"); F01D06$Rep <- "A"
F03D06 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F03_D06_StarvedB_Data_processeddata.csv"); F03D06$Rep <- "B"
F05D06 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F05_D06_StarvedC_Data_processeddata.csv"); F05D06$Rep <- "C"
StarvedD06 <- rbind(F01D06,F03D06,F05D06)
colnames(StarvedD06) <- c("StackID","Pixels","PropDAPI","PropPE","PropPC","Rep")

F02D06 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F02_D06_HPFedA_Data_processeddata.csv"); F02D06$Rep <- "A"
F04D06 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F04_D06_HPFedB_Data_processeddata.csv"); F04D06$Rep <- "B"
F06D06 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F06_D06_HPFedC_Data_processeddata.csv"); F06D06$Rep <- "C"
HPFedD06 <- rbind(F02D06,F04D06,F06D06)
colnames(HPFedD06) <- c("StackID","Pixels","PropDAPI","PropPE","PropPC","Rep")

# Day 09
F01D09 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F01_D09_StarvedA_Data_processeddata.csv"); F01D09$Rep <- "A"
F03D09 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F03_D09_StarvedB_Data_processeddata.csv"); F03D09$Rep <- "B"
F05D09 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F05_D09_StarvedC_Data_processeddata.csv"); F05D09$Rep <- "C"
StarvedD09 <- rbind(F01D09,F03D09,F05D09)
colnames(StarvedD09) <- c("StackID","Pixels","PropDAPI","PropPE","PropPC","Rep")

F02D09 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F02_D09_HPFedA_Data_processeddata.csv"); F02D09$Rep <- "A"
F04D09 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F04_D09_HPFedB_Data_processeddata.csv"); F04D09$Rep <- "B"
F06D09 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F06_D09_HPFedC_Data_processeddata.csv"); F06D09$Rep <- "C"
HPFedD09 <- rbind(F02D09,F04D09,F06D09)
colnames(HPFedD09) <- c("StackID","Pixels","PropDAPI","PropPE","PropPC","Rep")

# Day 12
F01D12 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F01_D12_StarvedA_Data_processeddata.csv"); F01D12$Rep <- "A"
F03D12 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F03_D12_StarvedB_Data_processeddata.csv"); F03D12$Rep <- "B"
F05D12 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F05_D12_StarvedC_Data_processeddata.csv"); F05D12$Rep <- "C"
StarvedD12 <- rbind(F01D12,F03D12,F05D12)
colnames(StarvedD12) <- c("StackID","Pixels","PropDAPI","PropPE","PropPC","Rep")

F02D12 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F02_D12_HPFedA_Data_processeddata.csv"); F02D12$Rep <- "A"
F04D12 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F04_D12_HPFedB_Data_processeddata.csv"); F04D12$Rep <- "B"
F06D12 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F06_D12_HPFedC_Data_processeddata.csv"); F06D12$Rep <- "C"
HPFedD12 <- rbind(F02D12,F04D12,F06D12)
colnames(HPFedD12) <- c("StackID","Pixels","PropDAPI","PropPE","PropPC","Rep")

# Day 15
F01D15 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F01_D15_StarvedA_Data_processeddata.csv"); F01D15$Rep <- "A"
F03D15 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F03_D15_StarvedB_Data_processeddata.csv"); F03D15$Rep <- "B"
F05D15 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F05_D15_StarvedC_Data_processeddata.csv"); F05D15$Rep <- "C"
StarvedD15 <- rbind(F01D15,F03D15,F05D15)
colnames(StarvedD15) <- c("StackID","Pixels","PropDAPI","PropPE","PropPC","Rep")

F02D15 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F02_D15_HPFedA_Data_processeddata.csv"); F02D15$Rep <- "A"
F04D15 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F04_D15_HPFedB_Data_processeddata.csv"); F04D15$Rep <- "B"
F06D15 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F06_D15_HPFedC_Data_processeddata.csv"); F06D15$Rep <- "C"
HPFedD15 <- rbind(F02D15,F04D15,F06D15)
colnames(HPFedD15) <- c("StackID","Pixels","PropDAPI","PropPE","PropPC","Rep")

# Day 17
F07D17 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F07_D17_MR+HP+0_A_Data_processeddata.csv"); F07D17$Rep <- "A"
F08D17 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F08_D17_MR+HP+0_B_Data_processeddata.csv"); F08D17$Rep <- "B"
F09D17 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F09_D17_MR+HP+0_C_Data_processeddata.csv"); F09D17$Rep <- "C"
StarvedD17 <- rbind(F07D17,F08D17,F09D17)
colnames(StarvedD17) <- c("StackID","Pixels","PropDAPI","PropPE","PropPC","Rep")

F10D17 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F10_D17_MR+HP+TA_A_Data_processeddata.csv"); F10D17$Rep <- "A"
F11D17 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F11_D17_MR+HP+TA_B_Data_processeddata.csv"); F11D17$Rep <- "B"
F12D17 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F12_D17_MR+HP+TA_C_Data_processeddata.csv"); F12D17$Rep <- "C"
TAFedD17 <- rbind(F10D17,F11D17,F12D17)
colnames(TAFedD17) <- c("StackID","Pixels","PropDAPI","PropPE","PropPC","Rep")

# Day 19
F07D19 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F07_D19_MR+HP+0_A_Data_processeddata.csv"); F07D19$Rep <- "A"
F08D19 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F08_D19_MR+HP+0_B_Data_processeddata.csv"); F08D19$Rep <- "B"
F09D19 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F09_D19_MR+HP+0_C_Data_processeddata.csv"); F09D19$Rep <- "C"
StarvedD19 <- rbind(F07D19,F08D19,F09D19)
colnames(StarvedD19) <- c("StackID","Pixels","PropDAPI","PropPE","PropPC","Rep")

F10D19 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F10_D19_MR+HP+TA_A_Data_processeddata.csv"); F10D19$Rep <- "A"
F11D19 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F11_D19_MR+HP+TA_B_Data_processeddata.csv"); F11D19$Rep <- "B"
F12D19 <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/FlowCamCalibration/Confocal/CSVs/F12_D19_MR+HP+TA_C_Data_processeddata.csv"); F12D19$Rep <- "C"
TAFedD19 <- rbind(F10D19,F11D19,F12D19)
colnames(TAFedD19) <- c("StackID","Pixels","PropDAPI","PropPE","PropPC","Rep")
```

### Combine FlowCam and Confocal data into the same data frame
```{r}
comparative.data <- as.data.frame(cbind(rep(expt.day,each=2),c(rep(c("00","HP"),6),rep(c("00","TA"),2))))
colnames(comparative.data) <- c('Expt.Day','Prey')
comparative.data$Expt.Day <- factor(comparative.data$Expt.Day,levels=expt.day)
comparative.data$Flowcam.chl.mean <- NaN
comparative.data$Flowcam.chl.sd <- NaN
comparative.data$Flowcam.pe.mean <- NaN
comparative.data$Flowcam.pe.sd <- NaN
comparative.data$Confocal.chl.mean <- NaN
comparative.data$Confocal.chl.sd <- NaN
comparative.data$Confocal.pe.mean <- NaN
comparative.data$Confocal.pe.sd <- NaN

expt.day2 <- c(1,3,6,9,12,15,17,19)
for(i in 1:6){
  daychoice = expt.day[i]
  # 00 treatment
  comparative.data[comparative.data$Expt.Day==daychoice&comparative.data$Prey=='00',]$Flowcam.chl.mean <- mean(FCDP.Meso.00.hasplastid[FCDP.Meso.00.hasplastid$Day==expt.day2[i],]$Ch1.Peak)
  comparative.data[comparative.data$Expt.Day==daychoice&comparative.data$Prey=='00',]$Flowcam.chl.sd <- sd(FCDP.Meso.00.hasplastid[FCDP.Meso.00.hasplastid$Day==expt.day2[i],]$Ch1.Peak)
  comparative.data[comparative.data$Expt.Day==daychoice&comparative.data$Prey=='00',]$Flowcam.pe.mean <- mean(FCDP.Meso.00.hasplastid[FCDP.Meso.00.hasplastid$Day==expt.day2[i],]$Ch2.Peak)
  comparative.data[comparative.data$Expt.Day==daychoice&comparative.data$Prey=='00',]$Flowcam.pe.sd <- sd(FCDP.Meso.00.hasplastid[FCDP.Meso.00.hasplastid$Day==expt.day2[i],]$Ch2.Peak)
  
  # HP treatment
  comparative.data[comparative.data$Expt.Day==daychoice&comparative.data$Prey=='HP',]$Flowcam.chl.mean <- mean(FCDP.Meso.HP.hasplastid[FCDP.Meso.HP.hasplastid$Day==expt.day2[i],]$Ch1.Peak)
  comparative.data[comparative.data$Expt.Day==daychoice&comparative.data$Prey=='HP',]$Flowcam.chl.sd <- sd(FCDP.Meso.HP.hasplastid[FCDP.Meso.HP.hasplastid$Day==expt.day2[i],]$Ch1.Peak)
  comparative.data[comparative.data$Expt.Day==daychoice&comparative.data$Prey=='HP',]$Flowcam.pe.mean <- mean(FCDP.Meso.HP.hasplastid[FCDP.Meso.HP.hasplastid$Day==expt.day2[i],]$Ch2.Peak)
  comparative.data[comparative.data$Expt.Day==daychoice&comparative.data$Prey=='HP',]$Flowcam.pe.sd <- sd(FCDP.Meso.HP.hasplastid[FCDP.Meso.HP.hasplastid$Day==expt.day2[i],]$Ch2.Peak)

}

for(i in 7:8){
  daychoice = expt.day[i]
  # 00 treatment
  comparative.data[comparative.data$Expt.Day==daychoice&comparative.data$Prey=='00',]$Flowcam.chl.mean <- mean(FCDP.Meso.00.hasplastid[FCDP.Meso.00.hasplastid$Day==expt.day2[i],]$Ch1.Peak)
  comparative.data[comparative.data$Expt.Day==daychoice&comparative.data$Prey=='00',]$Flowcam.chl.sd <- sd(FCDP.Meso.00.hasplastid[FCDP.Meso.00.hasplastid$Day==expt.day2[i],]$Ch1.Peak)
  comparative.data[comparative.data$Expt.Day==daychoice&comparative.data$Prey=='00',]$Flowcam.pe.mean <- mean(FCDP.Meso.00.hasplastid[FCDP.Meso.00.hasplastid$Day==expt.day2[i],]$Ch2.Peak)
  comparative.data[comparative.data$Expt.Day==daychoice&comparative.data$Prey=='00',]$Flowcam.pe.sd <- sd(FCDP.Meso.00.hasplastid[FCDP.Meso.00.hasplastid$Day==expt.day2[i],]$Ch2.Peak)
  
  # TA treatment
  comparative.data[comparative.data$Expt.Day==daychoice&comparative.data$Prey=='TA',]$Flowcam.chl.mean <- mean(FCDP.Meso.TA.hasplastid[FCDP.Meso.TA.hasplastid$Day==expt.day2[i],]$Ch1.Peak)
  comparative.data[comparative.data$Expt.Day==daychoice&comparative.data$Prey=='TA',]$Flowcam.chl.sd <- sd(FCDP.Meso.TA.hasplastid[FCDP.Meso.TA.hasplastid$Day==expt.day2[i],]$Ch1.Peak)
  comparative.data[comparative.data$Expt.Day==daychoice&comparative.data$Prey=='TA',]$Flowcam.pe.mean <- mean(FCDP.Meso.TA.hasplastid[FCDP.Meso.TA.hasplastid$Day==expt.day2[i],]$Ch2.Peak)
  comparative.data[comparative.data$Expt.Day==daychoice&comparative.data$Prey=='TA',]$Flowcam.pe.sd <- sd(FCDP.Meso.TA.hasplastid[FCDP.Meso.TA.hasplastid$Day==expt.day2[i],]$Ch2.Peak)

}

comparative.data[comparative.data$Expt.Day=='D1'&comparative.data$Prey=='00',]$Confocal.chl.mean <- mean(StarvedD01$PropPC+StarvedD01$PropPE)
comparative.data[comparative.data$Expt.Day=='D1'&comparative.data$Prey=='00',]$Confocal.chl.sd <- sd(StarvedD01$PropPC+StarvedD01$PropPE)
comparative.data[comparative.data$Expt.Day=='D3'&comparative.data$Prey=='00',]$Confocal.chl.mean <- mean(StarvedD03$PropPC+StarvedD03$PropPE)
comparative.data[comparative.data$Expt.Day=='D3'&comparative.data$Prey=='00',]$Confocal.chl.sd <- sd(StarvedD03$PropPC+StarvedD03$PropPE)
comparative.data[comparative.data$Expt.Day=='D6'&comparative.data$Prey=='00',]$Confocal.chl.mean <- mean(StarvedD06$PropPC+StarvedD06$PropPE)
comparative.data[comparative.data$Expt.Day=='D6'&comparative.data$Prey=='00',]$Confocal.chl.sd <- sd(StarvedD06$PropPC+StarvedD06$PropPE)
comparative.data[comparative.data$Expt.Day=='D9'&comparative.data$Prey=='00',]$Confocal.chl.mean <- mean(StarvedD09$PropPC+StarvedD09$PropPE)
comparative.data[comparative.data$Expt.Day=='D9'&comparative.data$Prey=='00',]$Confocal.chl.sd <- sd(StarvedD09$PropPC+StarvedD09$PropPE)
comparative.data[comparative.data$Expt.Day=='D12'&comparative.data$Prey=='00',]$Confocal.chl.mean <- mean(StarvedD12$PropPC+StarvedD12$PropPE)
comparative.data[comparative.data$Expt.Day=='D12'&comparative.data$Prey=='00',]$Confocal.chl.sd <- sd(StarvedD12$PropPC+StarvedD12$PropPE)
comparative.data[comparative.data$Expt.Day=='D15'&comparative.data$Prey=='00',]$Confocal.chl.mean <- mean(StarvedD15$PropPC+StarvedD15$PropPE)
comparative.data[comparative.data$Expt.Day=='D15'&comparative.data$Prey=='00',]$Confocal.chl.sd <- sd(StarvedD15$PropPC+StarvedD15$PropPE)
comparative.data[comparative.data$Expt.Day=='D17'&comparative.data$Prey=='00',]$Confocal.chl.mean <- mean(StarvedD17$PropPC+StarvedD17$PropPE)
comparative.data[comparative.data$Expt.Day=='D17'&comparative.data$Prey=='00',]$Confocal.chl.sd <- sd(StarvedD17$PropPC+StarvedD17$PropPE)
comparative.data[comparative.data$Expt.Day=='D19'&comparative.data$Prey=='00',]$Confocal.chl.mean <- mean(StarvedD19$PropPC+StarvedD19$PropPE)
comparative.data[comparative.data$Expt.Day=='D19'&comparative.data$Prey=='00',]$Confocal.chl.sd <- sd(StarvedD19$PropPC+StarvedD19$PropPE)

comparative.data[comparative.data$Expt.Day=='D1'&comparative.data$Prey=='HP',]$Confocal.chl.mean <- mean(HPFedD01$PropPC+HPFedD01$PropPE)
comparative.data[comparative.data$Expt.Day=='D1'&comparative.data$Prey=='HP',]$Confocal.chl.sd <- sd(HPFedD01$PropPC+HPFedD01$PropPE)
comparative.data[comparative.data$Expt.Day=='D3'&comparative.data$Prey=='HP',]$Confocal.chl.mean <- mean(HPFedD03$PropPC+HPFedD03$PropPE)
comparative.data[comparative.data$Expt.Day=='D3'&comparative.data$Prey=='HP',]$Confocal.chl.sd <- sd(HPFedD03$PropPC+HPFedD03$PropPE)
comparative.data[comparative.data$Expt.Day=='D6'&comparative.data$Prey=='HP',]$Confocal.chl.mean <- mean(HPFedD06$PropPC+HPFedD06$PropPE)
comparative.data[comparative.data$Expt.Day=='D6'&comparative.data$Prey=='HP',]$Confocal.chl.sd <- sd(HPFedD06$PropPC+HPFedD06$PropPE)
comparative.data[comparative.data$Expt.Day=='D9'&comparative.data$Prey=='HP',]$Confocal.chl.mean <- mean(HPFedD09$PropPC+HPFedD09$PropPE)
comparative.data[comparative.data$Expt.Day=='D9'&comparative.data$Prey=='HP',]$Confocal.chl.sd <- sd(HPFedD09$PropPC+HPFedD09$PropPE)
comparative.data[comparative.data$Expt.Day=='D12'&comparative.data$Prey=='HP',]$Confocal.chl.mean <- mean(HPFedD12$PropPC+HPFedD12$PropPE)
comparative.data[comparative.data$Expt.Day=='D12'&comparative.data$Prey=='HP',]$Confocal.chl.sd <- sd(HPFedD12$PropPC+HPFedD12$PropPE)
comparative.data[comparative.data$Expt.Day=='D15'&comparative.data$Prey=='HP',]$Confocal.chl.mean <- mean(HPFedD15$PropPC+HPFedD15$PropPE)
comparative.data[comparative.data$Expt.Day=='D15'&comparative.data$Prey=='HP',]$Confocal.chl.sd <- sd(HPFedD15$PropPC+HPFedD15$PropPE)

comparative.data[comparative.data$Expt.Day=='D17'&comparative.data$Prey=='TA',]$Confocal.chl.mean <- mean(TAFedD17$PropPC+TAFedD17$PropPE)
comparative.data[comparative.data$Expt.Day=='D17'&comparative.data$Prey=='TA',]$Confocal.chl.sd <- sd(TAFedD17$PropPC+TAFedD17$PropPE)
comparative.data[comparative.data$Expt.Day=='D19'&comparative.data$Prey=='TA',]$Confocal.chl.mean <- mean(TAFedD19$PropPC+TAFedD19$PropPE)
comparative.data[comparative.data$Expt.Day=='D19'&comparative.data$Prey=='TA',]$Confocal.chl.sd <- sd(TAFedD19$PropPC+TAFedD19$PropPE)


comparative.data[comparative.data$Expt.Day=='D1'&comparative.data$Prey=='00',]$Confocal.pe.mean <- mean(StarvedD01$PropPE)
comparative.data[comparative.data$Expt.Day=='D1'&comparative.data$Prey=='00',]$Confocal.pe.sd <- sd(StarvedD01$PropPE)
comparative.data[comparative.data$Expt.Day=='D3'&comparative.data$Prey=='00',]$Confocal.pe.mean <- mean(StarvedD03$PropPE)
comparative.data[comparative.data$Expt.Day=='D3'&comparative.data$Prey=='00',]$Confocal.pe.sd <- sd(StarvedD03$PropPE)
comparative.data[comparative.data$Expt.Day=='D6'&comparative.data$Prey=='00',]$Confocal.pe.mean <- mean(StarvedD06$PropPE)
comparative.data[comparative.data$Expt.Day=='D6'&comparative.data$Prey=='00',]$Confocal.pe.sd <- sd(StarvedD06$PropPE)
comparative.data[comparative.data$Expt.Day=='D9'&comparative.data$Prey=='00',]$Confocal.pe.mean <- mean(StarvedD09$PropPE)
comparative.data[comparative.data$Expt.Day=='D9'&comparative.data$Prey=='00',]$Confocal.pe.sd <- sd(StarvedD09$PropPE)
comparative.data[comparative.data$Expt.Day=='D12'&comparative.data$Prey=='00',]$Confocal.pe.mean <- mean(StarvedD12$PropPE)
comparative.data[comparative.data$Expt.Day=='D12'&comparative.data$Prey=='00',]$Confocal.pe.sd <- sd(StarvedD12$PropPE)
comparative.data[comparative.data$Expt.Day=='D15'&comparative.data$Prey=='00',]$Confocal.pe.mean <- mean(StarvedD15$PropPE)
comparative.data[comparative.data$Expt.Day=='D15'&comparative.data$Prey=='00',]$Confocal.pe.sd <- sd(StarvedD15$PropPE)
comparative.data[comparative.data$Expt.Day=='D17'&comparative.data$Prey=='00',]$Confocal.pe.mean <- mean(StarvedD17$PropPE)
comparative.data[comparative.data$Expt.Day=='D17'&comparative.data$Prey=='00',]$Confocal.pe.sd <- sd(StarvedD17$PropPE)
comparative.data[comparative.data$Expt.Day=='D19'&comparative.data$Prey=='00',]$Confocal.pe.mean <- mean(StarvedD19$PropPE)
comparative.data[comparative.data$Expt.Day=='D19'&comparative.data$Prey=='00',]$Confocal.pe.sd <- sd(StarvedD19$PropPE)

comparative.data[comparative.data$Expt.Day=='D1'&comparative.data$Prey=='HP',]$Confocal.pe.mean <- mean(HPFedD01$PropPE)
comparative.data[comparative.data$Expt.Day=='D1'&comparative.data$Prey=='HP',]$Confocal.pe.sd <- sd(HPFedD01$PropPE)
comparative.data[comparative.data$Expt.Day=='D3'&comparative.data$Prey=='HP',]$Confocal.pe.mean <- mean(HPFedD03$PropPE)
comparative.data[comparative.data$Expt.Day=='D3'&comparative.data$Prey=='HP',]$Confocal.pe.sd <- sd(HPFedD03$PropPE)
comparative.data[comparative.data$Expt.Day=='D6'&comparative.data$Prey=='HP',]$Confocal.pe.mean <- mean(HPFedD06$PropPE)
comparative.data[comparative.data$Expt.Day=='D6'&comparative.data$Prey=='HP',]$Confocal.pe.sd <- sd(HPFedD06$PropPE)
comparative.data[comparative.data$Expt.Day=='D9'&comparative.data$Prey=='HP',]$Confocal.pe.mean <- mean(HPFedD09$PropPE)
comparative.data[comparative.data$Expt.Day=='D9'&comparative.data$Prey=='HP',]$Confocal.pe.sd <- sd(HPFedD09$PropPE)
comparative.data[comparative.data$Expt.Day=='D12'&comparative.data$Prey=='HP',]$Confocal.pe.mean <- mean(HPFedD12$PropPE)
comparative.data[comparative.data$Expt.Day=='D12'&comparative.data$Prey=='HP',]$Confocal.pe.sd <- sd(HPFedD12$PropPE)
comparative.data[comparative.data$Expt.Day=='D15'&comparative.data$Prey=='HP',]$Confocal.pe.mean <- mean(HPFedD15$PropPE)
comparative.data[comparative.data$Expt.Day=='D15'&comparative.data$Prey=='HP',]$Confocal.pe.sd <- sd(HPFedD15$PropPE)

comparative.data[comparative.data$Expt.Day=='D17'&comparative.data$Prey=='TA',]$Confocal.pe.mean <- mean(TAFedD17$PropPE)
comparative.data[comparative.data$Expt.Day=='D17'&comparative.data$Prey=='TA',]$Confocal.pe.sd <- sd(TAFedD17$PropPE)
comparative.data[comparative.data$Expt.Day=='D19'&comparative.data$Prey=='TA',]$Confocal.pe.mean <- mean(TAFedD19$PropPE)
comparative.data[comparative.data$Expt.Day=='D19'&comparative.data$Prey=='TA',]$Confocal.pe.sd <- sd(TAFedD19$PropPE)

comparative.data$Confocal.pc.mean <- comparative.data$Confocal.chl.mean-comparative.data$Confocal.pe.mean
```

### Determine correlations between measures
```{r SUPPFIG 1,fig.height=4,fig.width=8,warning=F}

par(mar=c(4,4,1,1),mfrow=c(1,2))
TAtoHPcolset2 <- addalpha(TAtoHPcols2(length(expt.day)),.5)

## Plot One: Chlorophyll
# Base plot
plot(comparative.data$Confocal.chl.mean,comparative.data$Flowcam.chl.mean,xlab='Confocal chlorophyll proportion volume',ylab='FlowCam channel 1 peak',xlim=c(min(comparative.data$Confocal.chl.mean-comparative.data$Confocal.chl.sd,na.rm=T),max(comparative.data$Confocal.chl.mean+comparative.data$Confocal.chl.sd,na.rm=T)),ylim=c(min(comparative.data$Flowcam.chl.mean-comparative.data$Flowcam.chl.sd,na.rm=T),max(comparative.data$Flowcam.chl.mean+comparative.data$Flowcam.chl.sd,na.rm=T)),type='n',las=1)

# Error bars
arrows(comparative.data$Confocal.chl.mean,comparative.data$Flowcam.chl.mean+comparative.data$Flowcam.chl.sd,comparative.data$Confocal.chl.mean,comparative.data$Flowcam.chl.mean-comparative.data$Flowcam.chl.sd,length=0.05,angle=90,code=3,col='gray50')
arrows(comparative.data$Confocal.chl.mean-comparative.data$Confocal.chl.sd,comparative.data$Flowcam.chl.mean,comparative.data$Confocal.chl.mean+comparative.data$Confocal.chl.sd,comparative.data$Flowcam.chl.mean,length=0.05,angle=90,code=3,col='gray50')

# Linear models
lm1 <- lm(Flowcam.chl.mean~Confocal.chl.mean, data=comparative.data[comparative.data$Prey=='HP',])
abline(lm1,lty=2)
lm1 <- lm(Flowcam.chl.mean~Confocal.chl.mean, data=comparative.data[comparative.data$Prey!='HP',])
abline(lm1,lty=1)

# Points
points(comparative.data$Confocal.chl.mean,comparative.data$Flowcam.chl.mean,pch=c(21,24,22)[as.factor(comparative.data$Prey)],bg=TAtoHPcolset2[as.factor(comparative.data$Expt.Day)])
points(comparative.data$Confocal.chl.mean,comparative.data$Flowcam.chl.mean,pch=c(21,24,22)[as.factor(comparative.data$Prey)],bg=TAtoHPcolset2[as.factor(comparative.data$Expt.Day)])
points(comparative.data$Confocal.chl.mean,comparative.data$Flowcam.chl.mean,pch=c(21,24,22)[as.factor(comparative.data$Prey)],bg=TAtoHPcolset2[as.factor(comparative.data$Expt.Day)])

legend(x='bottomright',inset=c(0.01,0.01),legend=c('PE plastids only','Mixed plastids'),pt.cex=c(0,0),lwd=1,lty=c(1,2))


## Plot two: phycoerythrin
# Base plot
plot(comparative.data$Confocal.pe.mean,comparative.data$Flowcam.pe.mean,xlab='Confocal phycoerythrin proportion volume',ylab='FlowCam channel 2 peak',xlim=c(min(comparative.data$Confocal.pe.mean-comparative.data$Confocal.pe.sd,na.rm=T),max(comparative.data$Confocal.pe.mean+comparative.data$Confocal.pe.sd,na.rm=T)),ylim=c(min(comparative.data$Flowcam.pe.mean-comparative.data$Flowcam.pe.sd,na.rm=T),max(comparative.data$Flowcam.pe.mean+comparative.data$Flowcam.pe.sd,na.rm=T)),type='n',las=1)

# Error bars
arrows(comparative.data$Confocal.pe.mean,comparative.data$Flowcam.pe.mean+comparative.data$Flowcam.pe.sd,comparative.data$Confocal.pe.mean,comparative.data$Flowcam.pe.mean-comparative.data$Flowcam.pe.sd,length=0.05,angle=90,code=3,col='gray50')
arrows(comparative.data$Confocal.pe.mean-comparative.data$Confocal.pe.sd,comparative.data$Flowcam.pe.mean,comparative.data$Confocal.pe.mean+comparative.data$Confocal.pe.sd,comparative.data$Flowcam.pe.mean,length=0.05,angle=90,code=3,col='gray50')

# Linear model
lm1 <- lm(Flowcam.pe.mean~Confocal.pe.mean, data=comparative.data)
abline(lm1,lty=3,lwd=1.5)
summary(lm1)

# Log model
nls1 <- nls(Flowcam.pe.mean~a*log(Confocal.pe.mean)+b, data = comparative.data, start=list(a=1,b=1))
xset <- seq(from=min(comparative.data$Confocal.pe.mean,na.rm=T)-1,to=max(comparative.data$Confocal.pe.mean,na.rm=T)+1,length.out=100)
yset <- summary(nls1)$parameters[1,1]*log(xset) + summary(nls1)$parameters[2,1]
lines(xset,yset,lty=2,lwd=1.5)
summary(nls1)

# Sqrt model
nls1 <- nls(Flowcam.pe.mean~a*sqrt(Confocal.pe.mean)+b, data = comparative.data, start=list(a=1,b=1))
xset <- seq(from=min(comparative.data$Confocal.pe.mean,na.rm=T)-1,to=max(comparative.data$Confocal.pe.mean,na.rm=T)+1,length.out=100)
yset <- summary(nls1)$parameters[1,1]*sqrt(xset) + summary(nls1)$parameters[2,1]
lines(xset,yset,lty=1,lwd=1.5)
summary(nls1)

# Plotting points
points(comparative.data$Confocal.pe.mean,comparative.data$Flowcam.pe.mean,pch=c(21,24,22)[as.factor(comparative.data$Prey)],bg=TAtoHPcolset2[as.factor(comparative.data$Expt.Day)])
points(comparative.data$Confocal.pe.mean,comparative.data$Flowcam.pe.mean,pch=c(21,24,22)[as.factor(comparative.data$Prey)],bg=TAtoHPcolset2[as.factor(comparative.data$Expt.Day)])
points(comparative.data$Confocal.pe.mean,comparative.data$Flowcam.pe.mean,pch=c(21,24,22)[as.factor(comparative.data$Prey)],bg=TAtoHPcolset2[as.factor(comparative.data$Expt.Day)])

legend(x='bottomright',inset=c(0.01,0.01),legend=c('Starved',expression(paste('Fed ',italic('H. pac.'))),expression(paste('Fed ',italic('T. amp.'))),'Linear model','Log model','Sqrt model'),pch=c(21,24,22,0,0),pt.cex=c(1,1,1,0,0,0),lwd=c(1.5),lty=c(0,0,0,3,2,1),pt.bg='gray80')
```

### Check algorithm performance
```{r SUPPFIG 2,fig.height=3,fig.width=9,warning=F}
par(mar=c(4,4,1,1),mfrow=c(1,3))

sqrt.PE.model <- nls(Flowcam.pe.mean~a*sqrt(Confocal.pe.mean)+b, data = comparative.data, start=list(a=1,b=1))
summary(sqrt.PE.model)
sqrt.PE.a <- summary(sqrt.PE.model)$parameters[1,1]
sqrt.PE.b <- summary(sqrt.PE.model)$parameters[2,1]

lm.Chl.model <- lm(Flowcam.chl.mean~Confocal.pc.mean+Confocal.pe.mean ,data=comparative.data)
summary(lm.Chl.model)
lm.Chl.a <- summary(lm.Chl.model)$coefficients[1,1]
lm.Chl.b <- summary(lm.Chl.model)$coefficients[2,1]
lm.Chl.c <- summary(lm.Chl.model)$coefficients[3,1]

# Check 1: Square-root model of phycoerythrin
comparative.data$Confocal.pe.predict <- ((comparative.data$Flowcam.pe.mean-sqrt.PE.b)/sqrt.PE.a)^2

plot(comparative.data$Confocal.pe.predict ~ comparative.data$Confocal.pe.mean,xlab='Measured prop. PE plastids',ylab='Predicted prop. PE plastids',las=1,type='n')
abline(a=0,b=1)
points(comparative.data$Confocal.pe.mean,comparative.data$Confocal.pe.predict,pch=c(21,24,22)[as.factor(comparative.data$Prey)],bg=TAtoHPcolset2[as.factor(comparative.data$Expt.Day)],cex=1.5);
points(comparative.data$Confocal.pe.mean,comparative.data$Confocal.pe.predict,pch=c(21,24,22)[as.factor(comparative.data$Prey)],bg=TAtoHPcolset2[as.factor(comparative.data$Expt.Day)],cex=1.5);
points(comparative.data$Confocal.pe.mean,comparative.data$Confocal.pe.predict,pch=c(21,24,22)[as.factor(comparative.data$Prey)],bg=TAtoHPcolset2[as.factor(comparative.data$Expt.Day)],cex=1.5)

lm1 <- lm(comparative.data$Confocal.pe.predict ~ comparative.data$Confocal.pe.mean)
text(max(comparative.data$Confocal.pe.mean,na.rm=T),min(comparative.data$Confocal.pe.predict,na.rm=T),c(expression(paste(R^2,' =          ')),format(summary(lm1)$r.squared,digits=3)),pos=2)

legend(x='topleft',inset=c(0.01,0.01),legend=c('Starved',expression(paste('Fed ',italic('H. pac.'))),expression(paste('Fed ',italic('T. amp.')))),pch=c(21,24,22),pt.cex=1.5,lwd=c(1.5),lty=c(0,0,0,3,2,1),pt.bg='gray80')

# Check 2: Linear model of chlorophyll
comparative.data$Flowcam.chl.predict <- lm.Chl.a + comparative.data$Confocal.pc.mean*lm.Chl.b + comparative.data$Confocal.pe.mean*lm.Chl.c

plot(comparative.data$Flowcam.chl.predict~comparative.data$Flowcam.chl.mean,xlab='Measured chl. fluorescence',ylab='Mixed model predicted chl. fluorescence',las=1,type='n')
abline(a=0,b=1)
points(comparative.data$Flowcam.chl.mean,comparative.data$Flowcam.chl.predict,pch=c(21,24,22)[as.factor(comparative.data$Prey)],bg=TAtoHPcolset2[as.factor(comparative.data$Expt.Day)],cex=1.5); 
points(comparative.data$Flowcam.chl.mean,comparative.data$Flowcam.chl.predict,pch=c(21,24,22)[as.factor(comparative.data$Prey)],bg=TAtoHPcolset2[as.factor(comparative.data$Expt.Day)],cex=1.5); 
points(comparative.data$Flowcam.chl.mean,comparative.data$Flowcam.chl.predict,pch=c(21,24,22)[as.factor(comparative.data$Prey)],bg=TAtoHPcolset2[as.factor(comparative.data$Expt.Day)],cex=1.5)

lm1 <- lm(comparative.data$Flowcam.chl.predict~comparative.data$Flowcam.chl.mean)
text(max(comparative.data$Flowcam.chl.mean,na.rm=T),min(comparative.data$Flowcam.chl.predict,na.rm=T),c(expression(paste(R^2,' =          ')),format(summary(lm1)$r.squared,digits=3)),pos=2)

# Check 3: Predict volume of PC plastids
comparative.data$Confocal.pc.predict <- (comparative.data$Flowcam.chl.mean-lm.Chl.a-lm.Chl.c*comparative.data$Confocal.pe.predict)/lm.Chl.b

plot(comparative.data$Confocal.pc.predict~comparative.data$Confocal.pc.mean,xlab='Measured prop. PC plastids',ylab='Predicted prop. PC plastids',las=1,type='n')
abline(a=0,b=1)
points(comparative.data$Confocal.pc.mean,comparative.data$Confocal.pc.predict,pch=c(21,24,22)[as.factor(comparative.data$Prey)],bg=TAtoHPcolset2[as.factor(comparative.data$Expt.Day)],cex=1.5); 
points(comparative.data$Confocal.pc.mean,comparative.data$Confocal.pc.predict,pch=c(21,24,22)[as.factor(comparative.data$Prey)],bg=TAtoHPcolset2[as.factor(comparative.data$Expt.Day)],cex=1.5); 
points(comparative.data$Confocal.pc.mean,comparative.data$Confocal.pc.predict,pch=c(21,24,22)[as.factor(comparative.data$Prey)],bg=TAtoHPcolset2[as.factor(comparative.data$Expt.Day)],cex=1.5)

lm1 <- lm(Confocal.pc.predict~Confocal.pc.mean,data=comparative.data[comparative.data$Confocal.pc.predict>0,])
text(max(comparative.data$Confocal.pc.mean,na.rm=T),min(comparative.data$Confocal.pc.predict,na.rm=T),c(expression(paste(R^2,' =          ')),format(summary(lm1)$r.squared,digits=3)),pos=2)
```

### Look at plastid dynamics
```{r}
head(FCDP.Meso.HP.hasplastid)
```

Find composite fluorescence values
```{r}
ARC <- All.Results.Concat
# Calculating concentrations of cells (in cells per mL), normalizing to the aspirated volume and adjusting for dilution
ARC$M.pmL <- ARC$TotalMeso/ARC$Aspirated.vol*ARC$Dilu
ARC$M.pmL.red <- ARC$M.TotRed/ARC$Aspirated.vol*ARC$Dilu
ARC$M.pmL.blue <- ARC$M.TotBlue/ARC$Aspirated.vol*ARC$Dilu

ARC$C.pmL <- ARC$TotalCrypto/ARC$Aspirated.vol*ARC$Dilu
ARC$C.pmL.red <- ARC$C.TotRed/ARC$Aspirated.vol*ARC$Dilu
ARC$C.pmL.blue <- ARC$C.TotBlue/ARC$Aspirated.vol*ARC$Dilu

# Calculating proportion of blue-green cryptophytes
ARC$C.propblue <- ARC$C.pmL.blue/ARC$C.pmL

# Rounding day to whole number so that we can group by timepoint in downstream calculations
ARC$Day.Numeric <- round(ARC$Time,digits=0)

ARC$M.meanch1peak <- (ARC$M.pmL.red*ARC$M.Red.meanCh1peak+ARC$M.pmL.blue*ARC$M.Blue.meanCh1peak)/ARC$M.pmL
ARC$M.meanch2peak <- (ARC$M.pmL.red*ARC$M.Red.meanCh2peak+ARC$M.pmL.blue*ARC$M.Blue.meanCh2peak)/ARC$M.pmL
for(i in 1:dim(ARC)[1]){
  if(is.na(ARC$M.meanch1peak[i])){
    if(is.na(ARC$M.Blue.meanCh1peak[i])){ 
      ARC$M.meanch1peak[i] <- ARC$M.Red.meanCh1peak[i]
    }
  }
  if(is.na(ARC$M.meanch2peak[i])){
    if(is.na(ARC$M.Blue.meanCh2peak[i])){
      ARC$M.meanch2peak[i] <- ARC$M.Red.meanCh2peak[i]
    }
  }
  if(is.na(ARC$M.meanch1peak[i])){
    if(is.na(ARC$M.Red.meanCh1peak[i])){
      ARC$M.meanch1peak[i] <- ARC$M.Blue.meanCh1peak[i]
    }
  }
  if(is.na(ARC$M.meanch2peak[i])){
    if(is.na(ARC$M.Red.meanCh2peak[i])){
      ARC$M.meanch2peak[i] <- ARC$M.Blue.meanCh2peak[i]
    }
  }
}

```

Using calibration to turn into prop cell volume with PC and PE plastids
```{r}
ARC$prop.PE.predict <- ((ARC$M.meanch2peak-sqrt.PE.b)/sqrt.PE.a)^2
ARC$prop.PC.predict <- (ARC$M.meanch1peak-lm.Chl.a-lm.Chl.c*ARC$prop.PE.predict)/lm.Chl.b
for(i in 1:dim(ARC)[1]){
  ARC$prop.PC.predict[i] <- max(0,ARC$prop.PC.predict[i])
}
ARC$prop.plastid.predict <- ARC$prop.PE.predict+ARC$prop.PC.predict
```

Generating labeling scheme for plotting
```{r}
ARC$FirstPrey <- ARC$Prey
ARC[ARC$Flask%in%c('Flask07','Flask08','Flask09','Flask10','Flask11','Flask12'),]$FirstPrey <- 'HP'
ARC$Prey.Sequence <- paste(ARC$FirstPrey,ARC$Prey,sep='.')
```


```{r SUPPFIG Long Term Plastid Dynamics, fig.height=2.5, fig.width=7.5,warning=F}
par(mar=c(4,4,1,1),mfrow=c(1,3))

pointcolor <- 'black'
pointcolor.bg <- 'gray80'

# Panel A: T. amphioxeia plastids
plot(jitter(ARC$Day.Numeric,.4),ARC$prop.PE.predict,las=1,xlab='Time (days)',ylab=expression(paste('Prop. cell volume ',italic('T. amphioxeia'),' plastids')),pch=c(21,22,22,24)[as.factor(ARC$Prey.Sequence)],bg=c('white','white',pointcolor.bg,TAcol.bg)[as.factor(ARC$Prey.Sequence)],col=c(pointcolor.bg,pointcolor.bg,pointcolor.bg,TAcol.bg)[as.factor(ARC$Prey.Sequence)],cex=c(1.5,1.5,1.5,1.3)[as.factor(ARC$Prey.Sequence)],ylim=c(0,.62))

Summ.Prey <- summarySE(data=ARC, 'prop.PE.predict', groupvars=c('Day.Numeric','Prey'))
Summ.Prey$PlotPrey <- Summ.Prey$Prey
Summ.Prey[Summ.Prey$Prey=='00' & Summ.Prey$Day.Numeric > 16,]$PlotPrey <- 'HP'
arrows(Summ.Prey$Day.Numeric,Summ.Prey$prop.PE.predict+Summ.Prey$se,Summ.Prey$Day.Numeric,Summ.Prey$prop.PE.predict-Summ.Prey$se,code=3,angle=90,length=.02)
subdat <- Summ.Prey[Summ.Prey$Prey=='00' & Summ.Prey$Day.Numeric < 16,]; lines(subdat$Day.Numeric,subdat$prop.PE.predict)
subdat1 <- Summ.Prey[Summ.Prey$Prey=='HP' & Summ.Prey$Day.Numeric < 16,];
subdat2 <- Summ.Prey[Summ.Prey$Prey=='00' & Summ.Prey$Day.Numeric > 16,];
subdat <- rbind(subdat1,subdat2); lines(subdat$Day.Numeric,subdat$prop.PE.predict)
subdat2 <- Summ.Prey[Summ.Prey$Prey=='TA' & Summ.Prey$Day.Numeric > 16,];
subdat <- rbind(subdat1,subdat2); lines(subdat$Day.Numeric,subdat$prop.PE.predict)

points(Summ.Prey$Day.Numeric,Summ.Prey$prop.PE.predict,pch=c(21,22,24)[as.factor(Summ.Prey$PlotPrey)],cex=c(1.5,1.5,1.3)[as.factor(Summ.Prey$PlotPrey)],bg=c('white',pointcolor,TAcol)[as.factor(Summ.Prey$Prey)])

legend(x='bottomleft',inset=c(0.0,0.0),legend=c('Starved',expression(paste('Fed ',italic('H. pacifica'))),expression(paste('Starved after ',italic('Hp'),'-fed')),expression(paste('Fed ',italic('Ta'),' after ',italic('Hp'),'-fed'))),pch=c(21,22,22,24),col='black',pt.bg=c('white',pointcolor,'white',TAcol),pt.cex=c(1.5,1.5,1.5,1.3),cex=1,bty='n')
text(x=1.3,y=0.615,'(A)')


# Panel B: Phycocyanin plastids
plot(jitter(ARC$Day.Numeric,.4),ARC$prop.PC.predict,las=1,xlab='Time (days)',ylab=expression(paste('Prop. cell volume ',italic('H. pacifica'),' plastids')),pch=c(21,22,22,24)[as.factor(ARC$Prey.Sequence)],bg=c('white','white',pointcolor.bg,TAcol.bg)[as.factor(ARC$Prey.Sequence)],col=c(pointcolor.bg,pointcolor.bg,pointcolor.bg,TAcol.bg)[as.factor(ARC$Prey.Sequence)],cex=c(1.5,1.5,1.5,1.3)[as.factor(ARC$Prey.Sequence)])#,ylim=c(0,.62))

Summ.Prey <- summarySE(data=ARC, 'prop.PC.predict', groupvars=c('Day.Numeric','Prey'))
Summ.Prey$PlotPrey <- Summ.Prey$Prey
Summ.Prey[Summ.Prey$Prey=='00' & Summ.Prey$Day.Numeric > 16,]$PlotPrey <- 'HP'
arrows(Summ.Prey$Day.Numeric,Summ.Prey$prop.PC.predict+Summ.Prey$se,Summ.Prey$Day.Numeric,Summ.Prey$prop.PC.predict-Summ.Prey$se,code=3,angle=90,length=.02)
subdat <- Summ.Prey[Summ.Prey$Prey=='00' & Summ.Prey$Day.Numeric < 16,]; lines(subdat$Day.Numeric,subdat$prop.PC.predict)
subdat1 <- Summ.Prey[Summ.Prey$Prey=='HP' & Summ.Prey$Day.Numeric < 16,];
subdat2 <- Summ.Prey[Summ.Prey$Prey=='00' & Summ.Prey$Day.Numeric > 16,];
subdat <- rbind(subdat1,subdat2); lines(subdat$Day.Numeric,subdat$prop.PC.predict)
subdat2 <- Summ.Prey[Summ.Prey$Prey=='TA' & Summ.Prey$Day.Numeric > 16,];
subdat <- rbind(subdat1,subdat2); lines(subdat$Day.Numeric,subdat$prop.PC.predict)

points(Summ.Prey$Day.Numeric,Summ.Prey$prop.PC.predict,pch=c(21,22,24)[as.factor(Summ.Prey$PlotPrey)],cex=c(1.5,1.5,1.3)[as.factor(Summ.Prey$PlotPrey)],bg=c('white',pointcolor,TAcol)[as.factor(Summ.Prey$Prey)])

text(x=1.3,y=0.167,'(B)')


# Panel C: All Plastids
plot(jitter(ARC$Day.Numeric,.4),ARC$prop.plastid.predict,las=1,xlab='Time (days)',ylab='Prop. cell volume containing plastids',pch=c(21,22,22,24)[as.factor(ARC$Prey.Sequence)],bg=c('white','white',pointcolor.bg,TAcol.bg)[as.factor(ARC$Prey.Sequence)],col=c(pointcolor.bg,pointcolor.bg,pointcolor.bg,TAcol.bg)[as.factor(ARC$Prey.Sequence)],cex=c(1.5,1.5,1.5,1.3)[as.factor(ARC$Prey.Sequence)],ylim=c(0.14,.62))

Summ.Prey <- summarySE(data=ARC, 'prop.plastid.predict', groupvars=c('Day.Numeric','Prey'))
Summ.Prey$PlotPrey <- Summ.Prey$Prey
Summ.Prey[Summ.Prey$Prey=='00' & Summ.Prey$Day.Numeric > 16,]$PlotPrey <- 'HP'
arrows(Summ.Prey$Day.Numeric,Summ.Prey$prop.plastid.predict+Summ.Prey$se,Summ.Prey$Day.Numeric,Summ.Prey$prop.plastid.predict-Summ.Prey$se,code=3,angle=90,length=.02)
subdat <- Summ.Prey[Summ.Prey$Prey=='00' & Summ.Prey$Day.Numeric < 16,]; lines(subdat$Day.Numeric,subdat$prop.plastid.predict)
subdat1 <- Summ.Prey[Summ.Prey$Prey=='HP' & Summ.Prey$Day.Numeric < 16,];
subdat2 <- Summ.Prey[Summ.Prey$Prey=='00' & Summ.Prey$Day.Numeric > 16,];
subdat <- rbind(subdat1,subdat2); lines(subdat$Day.Numeric,subdat$prop.plastid.predict)
subdat2 <- Summ.Prey[Summ.Prey$Prey=='TA' & Summ.Prey$Day.Numeric > 16,];
subdat <- rbind(subdat1,subdat2); lines(subdat$Day.Numeric,subdat$prop.plastid.predict)

points(Summ.Prey$Day.Numeric,Summ.Prey$prop.plastid.predict,pch=c(21,22,24)[as.factor(Summ.Prey$PlotPrey)],cex=c(1.5,1.5,1.3)[as.factor(Summ.Prey$PlotPrey)],bg=c('white',pointcolor,TAcol)[as.factor(Summ.Prey$Prey)])

text(x=1.3,y=0.615,'(C)')

#plot(jitter(ARC$Day.Numeric,.4),ARC$prop.plastid.predict,las=1,xlab='Time (days)',ylab='Prop. cell volume containing plastids',pch=21,bg=c('white',pointcolor.bg)[as.factor(ARC$Prey)],col=pointcolor.bg,cex=1.5,ylim=c(0,0.61))


```

### Examine decay rate of plastids vs growth rate of cultures
```{r,fig.height=4,fig.width=4}
calib.days <- c(15,16,17,18,19)
calib.cols <- c(6:10)

subdat <- calib.counts[calib.counts$CountSp=='MR',]

plot(calib.days,subdat[1,calib.cols],type='n',xlab='Time (days)',ylab=expression(paste(italic('M. rubrum'),' popn. (cells/mL)')),las=1,ylim=c(1200,5500))
for(i in 1:dim(subdat)[1]){
  if(subdat[i,]$Prey=='TA'){
    #lines(calib.days,subdat[i,calib.cols])
    points(jitter(calib.days,.2),subdat[i,calib.cols],bg=TAcol.bg,col=TAcol.bg,pch=24)
  } else {
    #lines(calib.days,subdat[i,calib.cols])
    points(jitter(calib.days,.2),subdat[i,calib.cols],pch=22,,bg=pointcolor.bg,col=pointcolor.bg)
  }
}

calib.counts.MR.fed <- calib.counts[calib.counts$Prey=='TA'&calib.counts$CountSp=='MR',]
calib.counts.MR.starv <- calib.counts[calib.counts$Prey!='TA'&calib.counts$CountSp=='MR',]

lines(calib.days,colMeans(calib.counts.MR.fed[,calib.cols]),col='black')
points(calib.days,colMeans(calib.counts.MR.fed[,calib.cols]),pch=24,col='black',bg=TAcol)
lines(calib.days,colMeans(calib.counts.MR.starv[,calib.cols]),col='black')
points(calib.days,colMeans(calib.counts.MR.starv[,calib.cols]),pch=22,col='black',bg='white')

```
Amalgamate data for calculations
```{r}
pd <- as.data.frame(c(7:12))
colnames(pd) <- 'Flask'
pd$Treat <- rep(c('Starved','TA Fed'),each=3)
pd$Rep <- rep(c('A','B','C'),2)
pd$mu.15to17 <- NaN
pd$mu.17to19 <- NaN
pd$mu.15to19 <- NaN
pd$PC.15 <- NaN
pd$PC.17 <- NaN
pd$PC.19 <- NaN

for(i in 1:dim(pd)[1]){
  # Calculate growth rates
  subdat <- calib.counts[calib.counts$CountSp=='MR'&calib.counts$Flask==pd$Flask[i],]
  pd$mu.15to17[i] <- lm(t(log(subdat[,calib.cols[1:3]]))~calib.days[1:3])$coefficients[2]
  pd$mu.17to19[i] <- lm(t(log(subdat[,calib.cols[3:5]]))~calib.days[3:5])$coefficients[2]
  pd$mu.15to19[i] <- lm(t(log(subdat[,calib.cols[1:5]]))~calib.days[1:5])$coefficients[2]
  
  # Append plastid contents
  if(i %in% c(1,4)){ parentflask <- 'Flask02' }
  if(i %in% c(2,5)){ parentflask <- 'Flask04' }
  if(i %in% c(3,6)){ parentflask <- 'Flask06' }
  if(i < 4){ focalflask <- paste('Flask0',pd$Flask[i],sep='')} else {
    focalflask <- paste('Flask',pd$Flask[i],sep='')
  }
  subdat <- rbind(ARC[ARC$Flask==parentflask & ARC$Day.Numeric==15,],ARC[ARC$Flask==focalflask,])
  pd$PC.15[i] <- subdat$prop.PC.predict[1]; pd$PC.17[i] <- subdat$prop.PC.predict[2]; pd$PC.19[i] <- subdat$prop.PC.predict[3]
  
}

# Append cell volumes
pd$Vol.15 <- rep(aggregate(FCDP.Meso.HP.hasplastid[FCDP.Meso.HP.hasplastid$Day==15,]$Volume..ABD.~FCDP.Meso.HP.hasplastid[FCDP.Meso.HP.hasplastid$Day==15,]$replicate, FUN=mean)[,2],2)
pd$Vol.17 <- NaN
pd$Vol.17[1:3] <- aggregate(FCDP.Meso.00.hasplastid[FCDP.Meso.00.hasplastid$Day==17,]$Volume..ABD.~FCDP.Meso.00.hasplastid[FCDP.Meso.00.hasplastid$Day==17,]$replicate, FUN=mean)[,2]
pd$Vol.17[4:6] <- aggregate(FCDP.Meso.TA.hasplastid[FCDP.Meso.TA.hasplastid$Day==17,]$Volume..ABD.~FCDP.Meso.TA.hasplastid[FCDP.Meso.TA.hasplastid$Day==17,]$replicate, FUN=mean)[,2]
pd$Vol.19 <- NaN
pd$Vol.19[1:3] <- aggregate(FCDP.Meso.00.hasplastid[FCDP.Meso.00.hasplastid$Day==19,]$Volume..ABD.~FCDP.Meso.00.hasplastid[FCDP.Meso.00.hasplastid$Day==19,]$replicate, FUN=mean)[,2]
pd$Vol.19[4:6] <- aggregate(FCDP.Meso.TA.hasplastid[FCDP.Meso.TA.hasplastid$Day==19,]$Volume..ABD.~FCDP.Meso.TA.hasplastid[FCDP.Meso.TA.hasplastid$Day==19,]$replicate, FUN=mean)[,2]
```

Calculate plastid volumes and rates
```{r}
pd$PCvol.15 <- pd$PC.15*pd$Vol.15; pd$PCvol.17 <- pd$PC.17*pd$Vol.17; pd$PCvol.19 <- pd$PC.19*pd$Vol.19
pd$PCvol.mu.15to17 <- NaN
pd$PCvol.mu.17to19 <- NaN
pd$PCvol.mu.15to19 <- NaN

for(i in 1:dim(pd)[1]){
  pd$PCvol.mu.15to17[i] <- (log(pd$PCvol.17[i])-log(pd$PCvol.15[i]))/2
  pd$PCvol.mu.17to19[i] <- (log(pd$PCvol.19[i])-log(pd$PCvol.17[i]))/2
  pd$PCvol.mu.15to19[i] <- lm(log(c(pd$PCvol.15[i],pd$PCvol.17[i],pd$PCvol.19[i]))~c(15,17,19))$coefficients[2]
  
  pd$PCvol.mu.15to17.growthcorr[i] <- pd$PCvol.mu.15to17[i] + max(0,pd$mu.15to17[i])
  pd$PCvol.mu.17to19.growthcorr[i] <- pd$PCvol.mu.17to19[i] + max(0,pd$mu.17to19[i])
  pd$PCvol.mu.15to19.growthcorr[i] <- pd$PCvol.mu.15to19[i] + max(0,pd$mu.15to19[i])
}

```


Composite figure
```{r, fig.height=4,fig.width=5}

layout(matrix(data=c(1,1,1,2,2,2,1,1,1,2,2,2,1,1,1,2,2,2,3,3,4,4,5,5,3,3,4,4,5,5,3,3,4,4,5,5,3,3,4,4,5,5),nrow=6,ncol=7,byrow=F))

# Panel A: Population timeseries
par(mar=c(0.5,4,3,0))
subdat <- calib.counts[calib.counts$CountSp=='MR',]
plot(calib.days,subdat[1,calib.cols],type='n',xlab='Time (days)',ylab=expression(paste(italic('M. rubrum'),' popn. (cells/mL)')),las=1,ylim=c(1200,5500),xaxt='n'); axis(side=1,labels=F)
for(i in 1:dim(subdat)[1]){
  if(subdat[i,]$Prey=='TA'){
    #lines(calib.days,subdat[i,calib.cols])
    points(jitter(calib.days,.2),subdat[i,calib.cols],bg=TAcol.bg,col=TAcol.bg,pch=24)
  } else {
    #lines(calib.days,subdat[i,calib.cols])
    points(jitter(calib.days,.2),subdat[i,calib.cols],pch=22,,bg=pointcolor.bg,col=pointcolor.bg)
  }
}
calib.counts.MR.fed <- calib.counts[calib.counts$Prey=='TA'&calib.counts$CountSp=='MR',]
calib.counts.MR.starv <- calib.counts[calib.counts$Prey!='TA'&calib.counts$CountSp=='MR',]
lines(calib.days,colMeans(calib.counts.MR.fed[,calib.cols]),col='black')
points(calib.days,colMeans(calib.counts.MR.fed[,calib.cols]),pch=24,col='black',bg=TAcol)
lines(calib.days,colMeans(calib.counts.MR.starv[,calib.cols]),col='black')
points(calib.days,colMeans(calib.counts.MR.starv[,calib.cols]),pch=22,col='black',bg='white')
legend(x='topleft',inset=c(0,0),legend='',title='(a)',bty='n')
legend(x='bottomleft',inset=c(0,0),legend=c('Starved',expression(paste('Fed ',italic('T. amphioxeia')))),pch=c(22,24),pt.bg=c('white',TAcol),bty='n')

# Panel B: PC Plastid timeseries
par(mar=c(3,4,0.5,0))
plot(c(15,17,19),pd[1,13:15],type='n',xlab='Time (days)',ylab=expression(paste('Volume ',italic('H. pacifica'),' plastids (',m^3,')')),las=1,ylim=c(50,1800))
mtext('Time (days)',side=1,line=2,cex=.65)
for(i in 1:dim(pd)[1]){
  if(pd[i,]$Treat=='TA Fed'){
    #lines(calib.days,subdat[i,calib.cols])
    points(jitter(c(15,17,19),.2),pd[i,13:15],bg=TAcol.bg,col=TAcol.bg,pch=24)
  } else {
    #lines(calib.days,subdat[i,calib.cols])
    points(jitter(c(15,17,19),.2),pd[i,13:15],pch=22,,bg=pointcolor.bg,col=pointcolor.bg)
  }
}

vol.fed <- pd[pd$Treat=='TA Fed',]
vol.starv <- pd[pd$Treat!='TA Fed',]

lines(c(15,17,19),colMeans(vol.fed[,13:15]),col='black')
points(c(15,17,19),colMeans(vol.fed[,13:15]),pch=24,col='black',bg=TAcol)
lines(c(15,17,19),colMeans(vol.starv[,13:15]),col='black')
points(c(15,17,19),colMeans(vol.starv[,13:15]),pch=22,col='black',bg='white')
legend(x='topright',inset=c(0,0),legend='',title='(b)',bty='n')


# Panel C: Barplot of population growth rates
par(mar=c(0.5,5,3,1))
pd.mu <- as.data.frame(cbind(rep(pd$Treat,3),c(pd$mu.15to17,pd$mu.17to19,pd$mu.15to19),rep(c(1:3),each=6)))
pd.mu$V2 <- as.numeric(as.character(pd.mu$V2))
bargraph.CI(V3,V2,group=V1,data=pd.mu,las=1,col=c(pointcolor.bg,TAcol.bg),ylab=expression(paste('Growth rate (',d^-1,')')),space=c(0.05,0.5),err.width=0.05,xlab='Experimental date range',names=c('','','')); abline(h=0)
legend(x='topleft',inset=c(0,-.05),legend='',title='(c)',bty='n')

# Panel D: Barplot of plastid decay rates
par(mar=c(2,5,1.5,1))
pd.decay <- as.data.frame(cbind(rep(pd$Treat,3),c(pd$PCvol.mu.15to17,pd$PCvol.mu.17to19,pd$PCvol.mu.15to19),rep(c(1:3),each=6)))
pd.decay$V2 <- as.numeric(as.character(pd.decay$V2))
bargraph.CI(V3,-1*V2,group=V1,data=pd.decay,las=1,col=c(pointcolor.bg,TAcol.bg),ylab=expression(paste(italic('Hp'),' plastid loss rate (',d^-1,')')),err.width=0.05,space=c(0.05,0.5),xlab='Experimental date range',names=c('','','')); abline(h=0)
legend(x='topleft',inset=c(0,0),legend='',title='(d)',bty='n')

# Panel E: Barplot of plastid decay rates, correcting for population growth
par(mar=c(3,5,0.5,1))
pd.decay.corr <- as.data.frame(cbind(rep(pd$Treat,3),c(pd$PCvol.mu.15to17.growthcorr,pd$PCvol.mu.17to19.growthcorr,pd$PCvol.mu.15to19.growthcorr),rep(c(1:3),each=6)))
pd.decay.corr$V2 <- as.numeric(as.character(pd.decay.corr$V2))
bargraph.CI(V3,-1*V2,group=V1,data=pd.decay.corr,las=1,col=c(pointcolor.bg,TAcol.bg),ylab=expression(paste('Corr. loss rate (',d^-1,')')),err.width=0.05,space=c(0.05,0.5),xlab='Experimental date range',names=c('15 to 17','17 to 19','15 to 19')); abline(h=0)
mtext('Experimental date range',side=1,line=2,cex=.65)
legend(x='topleft',inset=c(0,0),legend='',title='(e)',bty='n')

```

```{r}
bargraph.CI(V3,-1*V2,group=V1,data=pd.decay.corr,las=1,col=c(pointcolor.bg,TAcol.bg),ylab=expression(paste('Growth-corrected plastid loss rate (',d^-1,')')),space=c(0.05,0.5),xlab='Experimental date range',names=c('15 to 17','17 to 19','15 to 19')); abline(h=0)

```



# Experiment 1: Grazing functional response

### Data import
```{r}
# Load data
dat <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/Mrubrum_fedHP_FunctionalResponseCurves - Exp2_22Nov2023.csv")
dat <- dat[!is.na(dat$Treat),]

ratio.summ <- summarySE(data=dat[dat$TargetMR>0,],'R_D0',groupvars='TargetHP')
dat$InitRatio <- ratio.summ$R_D0[match(dat$TargetHP,ratio.summ$TargetHP)]

fire <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/Mrubrum_fedHP_FunctionalResponseCurves - Exp2_PECurves.csv")

# Make a list of all the different prey concentrations
preyconc <- levels(as.factor(dat$TargetHP))

# Dates for plotting
days <- c(0,1,2,3,4,6,8)

# Select the columns to use for plotting
preycolumns <- c(15:21) # columns with H. pacifica data
predcolumns <- c(5:11) # columns with M. rubrum data
```

### Figure setup
```{r}
# Set up colors for each prey concentration; using VanGogh3 palette from MetBrewer https://github.com/BlakeRMills/MetBrewer
ltteal <- rgb(223/255,249/255,252/255) # random teal color ramp
dkteal <- rgb(27/255,116/255,129/255)
ctrlcol <- 'gray80'
colfunc <- colorRampPalette(c(ltteal,dkteal))
col2use <- colfunc(length(preyconc))

# Set up line types for different predation treatments
predtreats <- levels(as.factor(dat$TargetMR))
ltys <- c(1:length(predtreats))
```


### Estimating growth rates and plotting results
```{r}
# Add new columns to our data frame that we will use for prey and predator growth rates and y-intercepts. We'll consider both 24 and 48hr windows.
dat$prey.mu.96 <- NaN
dat$prey.yint.96 <- NaN

dat$pred.mu.96 <- NaN
dat$pred.yint.96 <- NaN

dat$prey.mu.48 <- NaN
dat$prey.yint.48 <- NaN

dat$pred.mu.48 <- NaN
dat$pred.yint.48 <- NaN

# Fit the growth curves line-by-line, using lm()

for( i in 1:dim(dat)[1] ){ # for each row in the data table
  
  if(dat[i,]$TargetHP!=0){ # Only fit prey if we expect positive densities
  # Fit all prey
  lm1 <- lm(log(t(dat[i,preycolumns[1:3]]))~days[1:3])
  dat$prey.mu.48[i] <- summary(lm1)$coefficients[2,1]
  dat$prey.yint.48[i] <- summary(lm1)$coefficients[1,1]
  
  lm1 <- lm(log(t(dat[i,preycolumns[1:5]]))~days[1:5])
  dat$prey.mu.96[i] <- summary(lm1)$coefficients[2,1]
  dat$prey.yint.96[i] <- summary(lm1)$coefficients[1,1]
  
  
  }
  
  if( dat[i,]$TargetMR!=0 ){ # Only fit predators if we expect non-zero densities
  # Fit predator
  lm1 <- lm(log(t(dat[i,predcolumns[1:3]]))~days[1:3])
  dat$pred.mu.48[i] <- summary(lm1)$coefficients[2,1]
  dat$pred.yint.48[i] <- summary(lm1)$coefficients[1,1]
  
  lm1 <- lm(log(t(dat[i,predcolumns[1:5]]))~days[1:5])
  dat$pred.mu.96[i] <- summary(lm1)$coefficients[2,1]
  dat$pred.yint.96[i] <- summary(lm1)$coefficients[1,1]
  }
}


```


Let's check our work by adding our growth curves to our plot!

```{r,fig.height=4,fig.width=8}

par(mar=c(4,5,1,1),mfrow=c(1,2))

dat2 <- dat[dat$TargetHP!=0,]

plot(days,dat2[1,preycolumns],las=1,xlab='Time (days)',ylab='',log='y',ylim=c((min(dat2[,preycolumns],na.rm=T)),(max(dat2[,preycolumns],na.rm=T))),type='n',main='Prey')
mtext('Population size (cells/mL)',side=2,line=4)

for(i in 2:length(preyconc)){
  subdat <- dat2[dat2$TargetHP==preyconc[i],]
  for(j in 1:dim(subdat)[1]){
    if(subdat[j,]$TargetMR==0){
      points(days,subdat[j,preycolumns],col=col2use[i],pch=21,bg=col2use[i])
      lines(days,subdat[j,preycolumns],col=col2use[i],lty=3)
    
      # 48hr growth curve
      #xcoords <- seq(from = min(days), to = max(days[3]), length.out = 100)
      #ycoords <- exp(subdat[j,]$prey.yint.48)*exp(subdat[j,]$prey.mu.48*xcoords)
      #lines(xcoords,ycoords,col=col2use[i])
      
      # 96hr growth curve
      xcoords <- seq(from = min(days), to = max(days[5]), length.out = 100)
      ycoords <- exp(subdat[j,]$prey.yint.96)*exp(subdat[j,]$prey.mu.96*xcoords)
      lines(xcoords,ycoords,col=col2use[i],lwd=2)
      
    }      else{
      
      points(days,subdat[j,preycolumns],col=col2use[i],pch=22,bg=col2use[i])
      lines(days,subdat[j,preycolumns],col=col2use[i],lty=3)
      # 48hr growth curve
      #xcoords <- seq(from = min(days), to = max(days[3]), length.out = 100)
      #ycoords <- exp(subdat[j,]$prey.yint.48)*exp(subdat[j,]$prey.mu.48*xcoords)
      #lines(xcoords,ycoords,col=col2use[i],lty=2)
      
      # 96hr growth curve
      xcoords <- seq(from = min(days), to = max(days[5]), length.out = 100)
      ycoords <- exp(subdat[j,]$prey.yint.96)*exp(subdat[j,]$prey.mu.96*xcoords)
      lines(xcoords,ycoords,col=col2use[i],lty=2,lwd=2)
    }
  }
}


dat2 <- dat[dat$TargetMR!=0,]
plot(days,dat2[1,predcolumns],las=1,xlab='Time (days)',ylab='Population size (cells/mL)',log='y',ylim=c((min(dat2[,predcolumns],na.rm=T)),(max(dat2[,predcolumns],na.rm=T))),type='n',main='Predator')
#mtext('Population size (cells/mL)',side=2,line=4)

for(i in 1:length(preyconc)){
  subdat <- dat2[dat2$TargetHP==preyconc[i],]
  for(j in 1:dim(subdat)[1]){
    points(days,subdat[j,predcolumns],col=col2use[i],pch=21,bg=col2use[i])
    lines(days,subdat[j,predcolumns],col=col2use[i],lty=3)
    # 48hr growth curve
      #xcoords <- seq(from = min(days), to = max(days[3]), length.out = 100)
      #ycoords <- exp(subdat[j,]$pred.yint.48)*exp(subdat[j,]$pred.mu.48*xcoords)
      #lines(xcoords,ycoords,col=col2use[i])
      
    # 96hr growth curve
      xcoords <- seq(from = min(days), to = max(days[5]), length.out = 100)
      ycoords <- exp(subdat[j,]$pred.yint.96)*exp(subdat[j,]$pred.mu.96*xcoords)
      lines(xcoords,ycoords,col=col2use[i],lwd=2)
  }
}


```

### Jeong & Latz calculations

Mean population sizes
```{r}
dat$prey.popn.48 <- dat$HP_D0*(exp(2*dat$prey.mu.48)-1)/(2*dat$prey.mu.48) # mean prey population
dat$prey.popn.96 <- dat$HP_D0*(exp(4*dat$prey.mu.96)-1)/(4*dat$prey.mu.96) # mean prey population

dat[dat$TargetHP==0,]$prey.popn.48 <- 0
dat[dat$TargetHP==0,]$prey.popn.96 <- 0
```

Prey population dynamics
```{r,fig.height=6,fig.width=9,warning=F}
subdat <- dat[dat$TargetHP==max(dat$TargetHP) & dat$TargetMR==0,]

tset <- seq(from = 0, to = 15, length.out = 100)
HP.r <- mean(c(dat[dat$TargetMR==0,]$prey.mu.48,dat[dat$TargetMR==0,]$prey.mu.96))
HP.r <- mean(dat[dat$TargetMR==0,]$prey.mu.96)
HP.K <- 2e6
HP.0 <- mean(subdat$HP_D0)

HPset <- NaN*tset; HPset[1] <- HP.0
for(i in 2:length(tset)){
  HPset[i] <- HPset[i-1] + (tset[i]-tset[i-1])*(HP.r*HPset[i-1]*(1-HPset[i-1]/HP.K))
}

par(mar=c(4,5,1,1))

font.mult <- 1.5
pt.mult <- 1.5
plot(days,subdat[1,preycolumns]/1e6,las=1,xlim=c(min(tset),max(tset)),ylim=c(0,2),xlab='Time (days)',ylab=expression(paste(italic(Hemiselmis),' abundance, ',10^6,' cells/mL')),bg=col2use[length(preyconc)],col=col2use[length(preyconc)],pch=21,cex.axis=font.mult,cex.lab=font.mult,cex=pt.mult)
points(days,subdat[2,preycolumns]/1e6,bg=col2use[length(preyconc)],col=col2use[length(preyconc)],pch=21,cex=pt.mult)
lines(tset,HPset/1e6,col=col2use[length(preyconc)],lwd=2*pt.mult)


for(j in 1:length(preyconc)){
  subdat <- dat[dat$TargetHP==preyconc[j] & dat$TargetMR==0,]
  # Plot points
  for(k in 1:dim(subdat)[1]){
    points(days,subdat[k,preycolumns]/1e6,bg=col2use[j],col=col2use[j],pch=21,cex=pt.mult)
  }
  # Run simulation
  HP.0 <- mean(subdat$HP_D0)
  if(j == 6){HP.0 <- 1.5*HP.0}
  HPset <- NaN*tset; HPset[1] <- HP.0
  for(i in 2:length(tset)){
    HPset[i] <- HPset[i-1] + (tset[i]-tset[i-1])*(HP.r*HPset[i-1]*(1-HPset[i-1]/HP.K))
  }
  lines(tset,HPset/1e6,col=col2use[j],lwd=2*pt.mult)
}

u <- par("usr")
v <- c(
  grconvertX(u[1:2], "user", "ndc"),
  grconvertY(u[3:4], "user", "ndc")
)
v <- c( (v[1]+v[2])/2, v[2], (v[3]+v[4])/2, v[4] )
v <- c( .18*(v[1]+v[2])/2, .65*(v[1]+v[2])/2, .75*(v[3]+v[4])/2, v[4] )
par( fig=v, new=TRUE, mar=c(2,3,1,.1) )
bargraph.CI(TargetHP,prey.mu.96,data=dat[dat$TargetMR==0,],err.width = .05,las=1,col=col2use,ylim=c(0,.9),ylab='',names='')
#plot(c(1:3),c(1:3))
mtext(expression(paste('Initial growth rate (',d^-1,')')),side=2,line=2.5)
axis(side=1,at=seq(from = 0.7, to = 7, by = 1.2),labels= c(round(unique(dat$InitRatio)[2:5],1),round(unique(dat$InitRatio)[6:7])), tick = F,padj=-1.5,cex.axis=1)
mtext(expression(paste('Initial ',italic(Hemiselmis),' ratio')),side=1,line=1.2)
abline(h=HP.r,lty=2); text(-0.2,HP.r+.037,'Average ',pos=4)
bargraph.CI(TargetHP,prey.mu.96,data=dat[dat$TargetMR==0,],err.width = .05,las=1,col=col2use,ylim=c(0,.9),ylab='',names='',add=T)

#plot(d0_inset, axes=FALSE, xlab="", ylab="")
box()

```

The first thing that we need to do is match up our control (predator-free) growth rates with our predator ones. We'll use the mean prey growth rates from the control studies to do this.
```{r}
# Make a data summary of the control growthrates using the summarySE function. Notice how I'm subsetting the dataframe to only include the "control" treatments.
summ.prey.mu.96 <- summarySE(data=dat[dat$TargetMR==0&dat$TargetHP>0,],'prey.mu.96',groupvars=c('TargetHP'))
summ.prey.mu.96

dat$ctrl.prey.mu.96 <- summ.prey.mu.96$prey.mu.96[match(dat$TargetHP,summ.prey.mu.96$TargetHP)] # the "match" function is a really powerful tool for linking data. Here, I'm using the "target prey" variable to make sure I match the correct average growth rates to each row in my data frame.

head(dat) # we can inspect the data frame to see if this worked. notice how the growth rates line up?

```

From here, we can compute our grazing rates as the difference between the control and +predator growth rates.
```{r}
dat$prey.g.96 <- dat$ctrl.prey.mu.96-dat$prey.mu.96
```

Computing the per-predator ingestion rate is a little trickier. Ask someone to show you the calculus on the whiteboard, but essentially what we are doing is using the growth rates of both predators and prey to compute mean populations of both, and then computing the per-predator ingestion rate from there. This method follows Jeong & Latz (1994) (https://www.int-res.com/articles/meps/106/m106p173.pdf)

```{r}
dat$pred.popn.96 <- dat$MR_D0*(exp(4*dat$pred.mu.96)-1)/(4*dat$pred.mu.96) # mean predator population
dat$prey.i.96 <- dat$prey.g.96*dat$prey.popn.96/dat$pred.popn.96 # ingestion = mean prey * grazing rate / mean predator

# Finally we'll manually fill in grazing and ingestion rates of 0 for 0 prey treatments.
dat[dat$TargetHP==0&dat$TargetMR!=0,]$prey.g.96 <- 0
dat[dat$TargetHP==0&dat$TargetMR!=0,]$prey.i.96 <- 0
dat[dat$TargetHP==0&dat$TargetMR!=0,]$prey.popn.96 <- 0
```

A scatterplot is even better because we can see our results as a function of the actual initial prey concentration. We can even work on fitting our data with a Holling Type II (saturating) functional response.

```{r,fig.width=5.5,fig.height=4}

par(mar=c(4,4,1,1))
subdat <- dat[dat$TargetMR!=0,]

plot((subdat$prey.popn.96/(10^3)),subdat$prey.i.96,las=1,xlab=expression(paste('Mean ',italic(Hp),' Population (',10^3,' cells/mL)')),ylab=expression(paste('Ingestion Rate (',italic(Hp),' per ',italic(Mr),' per day)')),pch=21,lwd=2,col=col2use[as.factor(subdat$TargetHP)],bg=col2use[as.factor(subdat$TargetHP)])

a.est <- summary(lm(subdat[1:7,]$prey.i.96~subdat[1:7,]$prey.popn.96))$coefficients[2,1] # estimate initial slope
h.est <- 1/max(subdat$prey.i.96,na.rm=T) # estimate handling time

fit1 <- nls(prey.i.96 ~ a*prey.popn.96/(1+a*h*prey.popn.96),data=subdat,start = list(a = a.est, h = h.est))
a.fit <- summary(fit1)$parameters[1,1]
h.fit <- summary(fit1)$parameters[2,1]

xcoords <- seq(from = 0, to = max(subdat$prey.popn.96,na.rm=T),length.out = 100)
ycoords <- a.fit*xcoords/(1+a.fit*h.fit*xcoords)
lines(xcoords/10^3,ycoords,lwd=2,col='gray50')

#text(0,0,summary(fit1)$parameters[1,])

#a.fit; h.fit
summary(fit1)
```

### Main text figure

```{r,fig.width=4.5,fig.height=6}

pointcolor <- 'gray50'

par(mar=c(1.5,4,2,1),mfrow=c(2,1))
subdat <- dat[dat$TargetMR!=0,]

plot((subdat$prey.popn.96/(10^3)),subdat$prey.i.96,las=1,xlab='',ylab='',pch=21,lwd=2,col=pointcolor,bg=pointcolor,cex=1.25,xaxt='n')
axis(side=1,labels=F)
mtext(expression(paste('Ingestion rate')),side=2,line=2.7)
mtext(expression(paste('(',italic('H. pacifica  '),italic('M. rubrum')^-1,'  ',d^-1,')')),side=2,line=1.6)
a.est <- summary(lm(subdat[1:7,]$prey.i.96~subdat[1:7,]$prey.popn.96))$coefficients[2,1] # estimate initial slope
h.est <- 1/max(subdat$prey.i.96,na.rm=T) # estimate handling time

fit1 <- nls(prey.i.96 ~ a*prey.popn.96/(1+a*h*prey.popn.96),data=subdat,start = list(a = a.est, h = h.est))
a.fit <- summary(fit1)$parameters[1,1]
h.fit <- summary(fit1)$parameters[2,1]

xcoords <- seq(from = 0, to = max(subdat$prey.popn.96,na.rm=T),length.out = 100)
ycoords <- a.fit*xcoords/(1+a.fit*h.fit*xcoords)
lines(xcoords/10^3,ycoords,lwd=2,col='black')

xdisp = 16.3
ydisp = 0.2
text(xdisp,ydisp+1.4, expression(paste("Holling Type II fit")),pos=2)
text(xdisp,ydisp+.7,expression(paste("a = 7.068 x ",10^-3)),pos=2)
text(xdisp,ydisp,expression(paste("h = 3.331 x ",10^-2)),pos=2)
text(0.3,7.5,'(A)')


par(mar=c(3.5,4,0,1))
subdat <- dat[dat$TargetMR!=0,]

plot((subdat$prey.popn.96/(10^3)),subdat$pred.mu.96,las=1,xlab='',ylab='',pch=21,lwd=2,col=pointcolor,bg=pointcolor,cex=1.25)
mtext(expression(paste('Mean ',italic('H. pacifica'),' population (',10^3,' cells  ',mL^-1,')')),side=1,line=2.5)
mtext(expression(paste(italic('M. rubrum'),' growth rate (',d^-1,')')),side=2,line=2.7)
a.est <- summary(lm(subdat[1:7,]$pred.mu.96~subdat[1:7,]$prey.popn.96))$coefficients[2,1] # estimate initial slope
h.est <- 1/max(subdat$pred.mu.96,na.rm=T) # estimate handling time
c.est <- 0

fit1 <- nls(pred.mu.96 ~ a*prey.popn.96/(1+a*h*prey.popn.96) + c,data=subdat,start = list(a = a.est, h = h.est, c = c.est))
a.fit <- summary(fit1)$parameters[1,1]
h.fit <- summary(fit1)$parameters[2,1]
c.fit <- summary(fit1)$parameters[3,1]

gmax.est <- 1/h.est
H.est <- 1/a.est/h.est

fit2 <- nls(pred.mu.96 ~ gmax*prey.popn.96/(H + prey.popn.96)+c, data = subdat, start = list(gmax = gmax.est, H=H.est, c = c.est))
gmax.fit <- summary(fit2)$parameters[1,1]
H.fit <- summary(fit2)$parameters[2,1]
c.fit <- summary(fit2)$parameters[3,1]

xcoords <- seq(from = 0, to = max(subdat$prey.popn.96,na.rm=T),length.out = 100)
ycoords <- gmax.fit*xcoords/(H.fit + xcoords) + c.fit
lines(xcoords/10^3,ycoords,lwd=2,col='black')

xdisp = 16.3
ydisp = 0.01
linespacing = 0.025
text(xdisp,ydisp+linespacing*3, expression(paste("Monod saturating fit")),pos=2)
text(xdisp,ydisp+linespacing*2,expression(paste(g[max]," = 0.4501")),pos=2)
text(xdisp,ydisp+linespacing*1,expression(paste("H = 1.588 x ",10^4)),pos=2)
text(xdisp,ydisp,expression(paste(g[0]," = 3.127 x ",10^-2)),pos=2)
text(0.3,0.245,'(B)')
```

### Revision: Comparison of linear and saturating functional responses

```{r,fig.width=4.5,fig.height=6}

pointcolor <- 'gray50'

par(mar=c(1.5,4,2,1),mfrow=c(2,1))

plot((subdat$prey.popn.96/(10^3)),subdat$prey.i.96,las=1,xlab='',ylab='',pch=21,lwd=2,col=pointcolor,bg=pointcolor,cex=1.25,xaxt='n')
axis(side=1,labels=F)
mtext(expression(paste('Ingestion rate')),side=2,line=2.7)
mtext(expression(paste('(',italic('H. pacifica  '),italic('M. rubrum')^-1,'  ',d^-1,')')),side=2,line=1.6)
a.est <- summary(lm(subdat[1:7,]$prey.i.96~subdat[1:7,]$prey.popn.96))$coefficients[2,1] # estimate initial slope
h.est <- 1/max(subdat$prey.i.96,na.rm=T) # estimate handling time

# Linear model, forcing y-intercept through 0
lm1 <- lm(prey.i.96 ~ -1 + prey.popn.96, data=subdat)
m.est <- lm1$coefficients[1]
xcoords <- seq(from = 0, to = max(subdat$prey.popn.96,na.rm=T),length.out = 100)
ycoords <- xcoords*m.est
lines(xcoords/10^3,ycoords,lwd=2,col='dodgerblue')

# Holling Type II
fit1 <- nls(prey.i.96 ~ a*prey.popn.96/(1+a*h*prey.popn.96),data=subdat,start = list(a = a.est, h = h.est))
a.fit <- summary(fit1)$parameters[1,1]
h.fit <- summary(fit1)$parameters[2,1]

ycoords <- a.fit*xcoords/(1+a.fit*h.fit*xcoords)
lines(xcoords/10^3,ycoords,lwd=2,col='black')

xdisp = 16.3
ydisp = 0.2
#text(xdisp,ydisp+1.4, expression(paste("Holling Type II fit")),pos=2)
#text(xdisp,ydisp+.7,expression(paste("a = 7.068 x ",10^-3)),pos=2)
#text(xdisp,ydisp,expression(paste("h = 3.331 x ",10^-2)),pos=2)
text(0.3,7.5,'(A)')

legend(x='bottomright',inset=c(0,0),legend=c('Linear Model','RSE = 0.7357, AIC = 36.32','Saturating Model','RSE = 0.6741, AIC = 34.59'),lwd=c(2,0,2,0),col=c('dodgerblue','dodgerblue','black','black'),bty = 'n',cex=.8)


par(mar=c(3.5,4,0,1))
subdat <- dat[dat$TargetMR!=0,]

plot((subdat$prey.popn.96/(10^3)),subdat$pred.mu.96,las=1,xlab='',ylab='',pch=21,lwd=2,col=pointcolor,bg=pointcolor,cex=1.25)
mtext(expression(paste('Mean ',italic('H. pacifica'),' population (',10^3,' cells  ',mL^-1,')')),side=1,line=2.5)
mtext(expression(paste(italic('M. rubrum'),' growth rate (',d^-1,')')),side=2,line=2.7)
a.est <- summary(lm(subdat[1:7,]$pred.mu.96~subdat[1:7,]$prey.popn.96))$coefficients[2,1] # estimate initial slope
h.est <- 1/max(subdat$pred.mu.96,na.rm=T) # estimate handling time
c.est <- 0

# Linear model
lm1 <- lm(pred.mu.96 ~ prey.popn.96, data=subdat)
m.est <- lm1$coefficients[2]
b.est <- lm1$coefficients[1]
xcoords <- seq(from = 0, to = max(subdat$prey.popn.96,na.rm=T),length.out = 100)
ycoords <- xcoords*m.est+b.est
lines(xcoords/10^3,ycoords,lwd=2,col='dodgerblue')

# Holling Type II
fit1 <- nls(pred.mu.96 ~ a*prey.popn.96/(1+a*h*prey.popn.96) + c,data=subdat,start = list(a = a.est, h = h.est, c = c.est))
a.fit <- summary(fit1)$parameters[1,1]
h.fit <- summary(fit1)$parameters[2,1]
c.fit <- summary(fit1)$parameters[3,1]

gmax.est <- 1/h.est
H.est <- 1/a.est/h.est

fit2 <- nls(pred.mu.96 ~ gmax*prey.popn.96/(H + prey.popn.96)+c, data = subdat, start = list(gmax = gmax.est, H=H.est, c = c.est))
gmax.fit <- summary(fit2)$parameters[1,1]
H.fit <- summary(fit2)$parameters[2,1]
c.fit <- summary(fit2)$parameters[3,1]

xcoords <- seq(from = 0, to = max(subdat$prey.popn.96,na.rm=T),length.out = 100)
ycoords <- gmax.fit*xcoords/(H.fit + xcoords) + c.fit
lines(xcoords/10^3,ycoords,lwd=2,col='black')

xdisp = 16.3
ydisp = 0.01
linespacing = 0.025
#text(xdisp,ydisp+linespacing*3, expression(paste("Monod saturating fit")),pos=2)
#text(xdisp,ydisp+linespacing*2,expression(paste(g[max]," = 0.4501")),pos=2)
#text(xdisp,ydisp+linespacing*1,expression(paste("H = 1.588 x ",10^4)),pos=2)
#text(xdisp,ydisp,expression(paste(g[0]," = 3.127 x ",10^-2)),pos=2)
text(0.3,0.245,'(B)')

legend(x='bottomright',inset=c(0,0),legend=c('Linear Model','RSE = 0.0331, AIC = -55.83','Saturating Model','RSE = 0.0103, AIC = -58.67'),lwd=c(2,0,2,0),col=c('dodgerblue','dodgerblue','black','black'),bty = 'n',cex=.8)
```

### Revision: GGE

I'm approximating gross growth efficiency as the growth rate divided by the ingestion rate
```{r,fig.height=3.5,fig.width=7.5}
par(mar=c(4,4,1,1),mfrow=c(1,2))
subdat$GGE <- subdat$pred.mu.96/subdat$prey.i.96
subdat2 <- subdat[subdat$prey.popn.96>0,]
plot(subdat2$prey.popn.96/1000,subdat2$GGE, xlab=expression(paste('Mean ',italic('H. pacifica'),' popn. (',10^3,' cells  ',mL^-1,')')), las=1, ylab=expression(paste('Gross growth efficiency, cellular')), pch=21, col = pointcolor, bg= pointcolor, cex=1.5 )

plot(subdat2$prey.popn.96/1000,1/subdat2$GGE, xlab=expression(paste('Mean ',italic('H. pacifica'),' popn. (',10^3,' cells  ',mL^-1,')')), las=1, ylab=expression(paste(italic('H. pacifica'), ' per ', italic('M. rubrum'))), pch=21, col = pointcolor, bg= pointcolor, cex=1.5 )
abline(h= mean(c(25.022388, 22.730732, 24.557177, 26.991875, 32.050628, 23.784593, 32.783537, 25.330859, 28.281495, 34.200815)), lty=2)
```

GGE per C

```{r,fig.height=3.5,fig.width=7.5}
par(mar=c(4,4,1,1),mfrow=c(1,2))
subdat$GGE.C <- subdat$pred.mu.96/subdat$prey.i.96*650/40
subdat2 <- subdat[subdat$prey.popn.96>0,]
plot(subdat2$prey.popn.96/1000,subdat2$GGE.C, xlab=expression(paste('Mean ',italic('H. pacifica'),' popn. (',10^3,' cells  ',mL^-1,')')), las=1, ylab=expression(paste('Gross growth efficiency, Carbon')), pch=21, col = pointcolor, bg= pointcolor, cex=1.5 )

plot(subdat2$prey.popn.96/1000,1/subdat2$GGE.C, xlab=expression(paste('Mean ',italic('H. pacifica'),' popn. (',10^3,' cells  ',mL^-1,')')), las=1, ylab=expression(paste(italic('H. pacifica'), ' C per ', italic('M. rubrum'),' C')), pch=21, col = pointcolor, bg= pointcolor, cex=1.5 )
abline(h= 1/mean(c(0.6494184, 0.7148912, 0.6617210, 0.6020330, 0.5070104, 0.6832154, 0.4956756, 0.6415100, 0.5745807, 0.4751349)), lty=2)
```



# Experiment 2: Prey selection
### Setup FlowCam file structure
```{r}
#Insert the location of your main folder for the current experiment.
#Alter this line to refer to the file location where the excel sheet is.
root_folder <- "/Users/hollyvm/GoogleSync/StudentWork/AmelieLEtoileGoga/MRpreychoice_Nov2023"

#In the main folder create a folder name CSV_files, if named other wise change "/CSV_files" accordingly
CSV_folder <- paste(root_folder,"/CSV_files",sep = "")

#List the sub-folders of the current experiment, this would usually be one folder for each sampling day.
Folder_list <- c("D0","D1","D2","D3","D4")

expt.day <- Folder_list

knitr::opts_knit$set(root.dir = root_folder)

#A .csv file should be created with extra meta-data, such as data for sampling time and dilution. If other data is acquired, such as pigment extractions, include these in the this file as well.
expt.meta <- read.csv("/Users/hollyvm/GoogleSync/StudentWork/AmelieLEtoileGoga/MRpreychoice_Nov2023/ALG_Expt2_OctNov2023_MRpreychoice - Dil_time.csv")
```

### Analyze FlowCam data and generate summary of results
```{r,fig.height=8,fig.width=8}
#Using the previously defined Folder_list, a for loop is created to access each folder one at a time, and within those folder each sample is then accessed one at a time.
#Each data set is being processed using the MRMC.partitioning function, which distinguished Red Chloroplast MC from blue-green Chloroplast MC. By using the meta-data stored in the file-name a new data-sheet is created with the desired data where each row is from a single sample from a single day.

create_plot_meso = F #If TRUE, the partitioning will output partitioned Ch1 vs Ch2 plots -- MESODINIUM VERSION
create_plot_prey = F #If TRUE, the partitioning will output partitioned Ch1 vs Ch2 plots -- PREY VERSION

unk.part.Meso = 5.5 # unknown partition for Mesodinium
bg.part.Meso = 4.5 # blue-green partition for Mesodinium
unk.part.prey = 0 # unknown partition for cryptophytes
bg.part.prey = 4.5 # blue-green partition for cryptophytes

#The first for-loop is created to open the folder of the individual sampling day in the order as they were defined (usually chronologically)
for(dir_idx in 1:length(Folder_list)){
  
  #The working directory is set to the folder containing one days worth of data.
  current_folder <- paste(root_folder,"/",Folder_list[dir_idx],sep = "")
  
  #Recording the current experimental day
  today <- expt.day[dir_idx]
  
  #here the columns to retrieve timestamp and dilution is defined.
  dil_name <- paste("Dil.",today,sep = "")
  time_name <- paste("TS.",today,sep = "")
  
  #The function list.files(current_folder), will create a list of files that are located in the folder, and by using this list of files, a new for-loop is created accessing each file consecutively.
  for(i in 1:length(list.files(current_folder))){
    
    #extracting meta data from the file name
    #Characters 1 to 7 is the Flask index
    name_flask <- substring(list.files(current_folder)[i],
                            first = 1,
                            last = 7)
    
    #assigning flask index as a number
    num_flask <- as.integer(substring(list.files(current_folder)[i],
                                      first = 6,
                                      last = 7))
    
    #Characters 9 to 12 is the Mesodinium pre-experiment plastid type
    Meso_designation <- substring(list.files(current_folder)[i],
                                  first = 9,
                                  last = 12)
    
    #Characters 14 through 18 indicate the prey being fed during the experiment
    prey_designation <- substring(list.files(current_folder)[i],
                                  first = 14,
                                  last = 18)
    
    #Character 20 is the replicate indicator
    expt_rep <- substring(list.files(current_folder)[i],
                          first = 20,
                          last = 20)
    
    #The dilution factor is extracted from the meta-data data-sheet in the root-folder
    flask_dil <- expt.meta[expt.meta$Flask == num_flask,
                           names(expt.meta) == dil_name]
    
    #Relative time from beginning of experiment is extracted
    flask_time <- expt.meta[expt.meta$Flask == num_flask,
                           names(expt.meta) == time_name]
    
    medium <- expt.meta[expt.meta$Flask == num_flask,"Medium"]
    
    #The .csv file is loaded here, and extra columns are added with the additional meta-data required for the data-processing
    file.name <- paste(current_folder,"/",list.files(current_folder)[i],sep = "")
    
    vec <- read.csv(file.name) %>% 
      mutate(Flask = name_flask,
             replicate = expt_rep,
             Meso = Meso_designation,
             Prey = prey_designation,
             Day = as.numeric(substring(expt.day[dir_idx],2)))
    
    #Because the flow-cam keeps counting the seconds when resetting the pump, a constant is multiplied to the Elapsed time to get the correct volume aspirated. This constant however was calculated from using the 0.5 ml pump, so a new value is probably needed for the 1 ml pump.
    Asp.vol <- (max(vec$Elapsed.Time*0.967)/60)*0.150
    
    #R-vector containing the raw data-set with both Mesodinium and Crypotphyte data
    vec.raw <- vec
    
    Meso_filter <- vec.raw$Class == "Mesodinium"
    
    #Creating an R-vector that only contains the data classified as Mesodinium
    vec <- vec.raw[Meso_filter,]
    
    #Creating an R-vector that only contains the data classified as Cryptophyte (or rather it only contains data that has not been classified as Meosdinium)
    vec2 <- vec.raw[!Meso_filter,]
    
    #On the first sample of each experimental day, an empty spreadsheet is created for both Prey and Mesodinium. This will be populated as the for-loop iterates through each sample.
    if(i == 1){
      FCDP_meso <- vec
      FCDP_prey <- vec2
      
      #Creating data-frame for partitioned data results
      All.Results <- as.data.frame(1:length(list.files(current_folder)))
      
      colnames(All.Results) <- c("Flask")     # Columns 1-8: Metadata
      All.Results$Day <- NaN
      All.Results$Time <- NaN                 
      All.Results$Dilution <- NaN             
      All.Results$Aspirated.vol <- NaN        
      All.Results$Meso <- NaN                 
      All.Results$Prey <- NaN                 
      All.Results$Replicate <- NaN            
      All.Results$Medium <- NaN               
      All.Results$M.Red <- NaN               # Columns 10-16; from Res$counts
      All.Results$M.Blue <- NaN              
      All.Results$M.Undefined <- NaN         
      All.Results$M.Nonfluorescent <- NaN
      All.Results$M.TotRed <- NaN
      All.Results$M.TotBlue <- NaN
      All.Results$TotalMeso <- NaN          
      All.Results$M.Red.meanCh1peak <- NaN               # Columns 17-20; from Res$Ch1.peaks
      All.Results$M.Blue.meanCh1peak <- NaN              
      All.Results$M.Undefined.meanCh1peak <- NaN         
      All.Results$M.Nonfluorescent.meanCh1peak <- NaN
      All.Results$M.Red.sdCh1peak <- NaN               # Columns 21-24; from Res$Ch1.sds
      All.Results$M.Blue.sdCh1peak <- NaN              
      All.Results$M.Undefined.sdCh1peak <- NaN         
      All.Results$M.Nonfluorescent.sdCh1peak <- NaN
      All.Results$M.Red.meanCh2peak <- NaN               # Columns 25-28; from Res$Ch2.peaks
      All.Results$M.Blue.meanCh2peak <- NaN              
      All.Results$M.Undefined.meanCh2peak <- NaN         
      All.Results$M.Nonfluorescent.meanCh2peak <- NaN  
      All.Results$M.Red.sdCh2peak <- NaN               # Columns 29-32; from Res$Ch2.sds
      All.Results$M.Blue.sdCh2peak <- NaN              
      All.Results$M.Undefined.sdCh2peak <- NaN         
      All.Results$M.Nonfluorescent.sdCh2peak <- NaN  
      
      #Adding columns for cryptophytes
      All.Results$C.Red <- NaN               # Columns 9-15; from Res$counts
      All.Results$C.Blue <- NaN              
      All.Results$C.Undefined <- NaN         
      All.Results$C.Nonfluorescent <- NaN
      All.Results$C.TotRed <- NaN
      All.Results$C.TotBlue <- NaN
      All.Results$TotalCrypto <- NaN          
      All.Results$C.Red.meanCh1peak <- NaN               # Columns 16-19; from Res$Ch1.peaks
      All.Results$C.Blue.meanCh1peak <- NaN              
      All.Results$C.Undefined.meanCh1peak <- NaN         
      All.Results$C.Nonfluorescent.meanCh1peak <- NaN
      All.Results$C.Red.sdCh1peak <- NaN               # Columns 20-23; from Res$Ch1.sds
      All.Results$C.Blue.sdCh1peak <- NaN              
      All.Results$C.Undefined.sdCh1peak <- NaN         
      All.Results$C.Nonfluorescent.sdCh1peak <- NaN
      All.Results$C.Red.meanCh2peak <- NaN               # Columns 24-27; from Res$Ch2.peaks
      All.Results$C.Blue.meanCh2peak <- NaN              
      All.Results$C.Undefined.meanCh2peak <- NaN         
      All.Results$C.Nonfluorescent.meanCh2peak <- NaN  
      All.Results$C.Red.sdCh2peak <- NaN               # Columns 28-31; from Res$Ch2.sds
      All.Results$C.Blue.sdCh2peak <- NaN              
      All.Results$C.Undefined.sdCh2peak <- NaN         
      All.Results$C.Nonfluorescent.sdCh2peak <- NaN  
      
    } else{
      FCDP_prey <- rbind(FCDP_prey,vec2)
      FCDP_meso <- rbind(FCDP_meso,vec)
    }
    
    # Add relevant data for this sample
    All.Results$Flask[i] <- name_flask
    All.Results$Day[i] <- today
    All.Results$Time[i] <- flask_time
    All.Results$Dilution[i] <- flask_dil
    All.Results$Aspirated.vol[i] <- round(Asp.vol,3)
    All.Results$Meso[i] <- Meso_designation
    All.Results$Prey[i] <- prey_designation
    All.Results$Replicate[i] <- expt_rep
    All.Results$Medium[i] <- medium
    
    #Running the partitioning function for Mesodinium

    if(dim(vec)[1] > 0){ # If there are Mesodinium in the dataset
      Res <- Meso.flowPeaks(vec,name_flask,today,create_plot = create_plot_meso,unknown.partition = unk.part.Meso, bluegreen.partition = bg.part.Meso)
      #Assigning partitioned data for Mesodinium
      All.Results[i,10:16] <- Res$counts
      All.Results[i,17:20] <- Res$Ch1.peaks
      All.Results[i,21:24] <- Res$Ch1.peaks.sd
      All.Results[i,25:28] <- Res$Ch2.peaks
      All.Results[i,29:32] <- Res$Ch2.peaks.sd
    }
    
    if(dim(vec2)[1] > 0){ # If there are cryptophytes in the dataset
      #Running flowPeaks for Prey
      Res.crypto <- Meso.flowPeaks(vec2,name_flask,today,create_plot = create_plot_prey,unknown.partition = unk.part.prey, bluegreen.partition = bg.part.prey)
      #Assigning partitioned data for Prey
      All.Results[i,33:39] <- Res.crypto$counts
      All.Results[i,40:43] <- Res.crypto$Ch1.peaks
      All.Results[i,44:47] <- Res.crypto$Ch1.peaks.sd
      All.Results[i,48:51] <- Res.crypto$Ch2.peaks
      All.Results[i,52:55] <- Res.crypto$Ch2.peaks.sd
    }
    
    if(i == length(list.files(current_folder))){
        FCDP_prey <- FCDP_prey %>% mutate(Partition = "Prey")
        FCDP_meso <- FCDP_meso %>% mutate(Partition = "Mesodinium")
        FCDP_all <- rbind(FCDP_meso,FCDP_prey)
      
      
      Res_name <- paste(CSV_folder,"/Summary_",expt.day[dir_idx],".csv",sep = "")
      FCDP_name <- paste(CSV_folder,"/FCDP_all_",expt.day[dir_idx],".csv",sep = "")
      
      write.csv(All.Results,Res_name,row.names = F)
      write.csv(FCDP_all,FCDP_name,row.names = F)
    }
  }
  
  if(dir_idx == 1){
    All.Results.Concat <- All.Results
  } else{
    All.Results.Concat <- rbind(All.Results.Concat, All.Results)
  }
  
  if(dir_idx == length(Folder_list)){
    All_res_name <- paste("All_Summary",".csv",sep='')
    write.csv(All.Results.Concat,All_res_name,row.names = F)
  }
  
}


```

### Calculate population sizes
```{r}
ARC <- All.Results.Concat # Shortening the variable name

# Something strange happened with the first Aspirated Volume measurement that I don't understand. But based on the cryptophyte numbers, the volume should be more similar to the other aspiration volumes than the 0.199 that the datasheet recorded.
ARC$Aspirated.vol[1] <- mean(ARC$Aspirated.vol[2:29])

# Calculating concentrations of cells (in cells per mL), normalizing to the aspirated volume and adjusting for dilution
ARC$M.pmL <- ARC$TotalMeso/ARC$Aspirated.vol*ARC$Dilu
ARC$M.pmL.red <- ARC$M.TotRed/ARC$Aspirated.vol*ARC$Dilu
ARC$M.pmL.blue <- ARC$M.TotBlue/ARC$Aspirated.vol*ARC$Dilu

ARC$C.pmL <- ARC$TotalCrypto/ARC$Aspirated.vol*ARC$Dilu
ARC$C.pmL.red <- ARC$C.TotRed/ARC$Aspirated.vol*ARC$Dilu
ARC$C.pmL.blue <- ARC$C.TotBlue/ARC$Aspirated.vol*ARC$Dilu

# Calculating proportion of blue-green cryptophytes
ARC$C.propblue <- ARC$C.pmL.blue/ARC$C.pmL

# Rounding day to whole number so that we can group by timepoint in downstream calculations
ARC$Day.Numeric <- round(ARC$Time,digits=0)

```

### Plot cryptophyte population dynamics
```{r, fig.height=5, fig.width=5}
par(mar=c(4,4,1,1),mfrow=c(2,2))

# Panel 1: All cryptophytes
plot(jitter(ARC$Day.Numeric,.2),ARC$C.pmL/1000,las=1,xlab='Time (days)',ylab='Cryptophytes (1000s of cells/mL)',pch=21,bg=c(Bothcol.bg,'white')[as.factor(ARC$Meso)],col=Bothcol,cex=1.5)
legend(x='topleft',inset=c(0.03,0.03),legend=c('Control','+ M. rubrum'),pch=21,pt.cex=1.5,pt.bg=c(Bothcol,'white'))

Summ.Prey <- summarySE(data=ARC, 'C.pmL', groupvars=c('Day.Numeric','Meso'))
arrows(Summ.Prey$Day.Numeric,Summ.Prey$C.pmL/1000+Summ.Prey$se/1000,Summ.Prey$Day.Numeric,Summ.Prey$C.pmL/1000-Summ.Prey$se/1000,code=3,angle=90,length=.02)
points(Summ.Prey$Day.Numeric,Summ.Prey$C.pmL/1000,pch=21,cex=1.5,bg=c(Bothcol,'white')[as.factor(Summ.Prey$Meso)])

# Panel 2: Teleaulax
plot(jitter(ARC$Day.Numeric,.2),ARC$C.pmL.red/1000,las=1,xlab='Time (days)',ylab='T. amphioxeia (1000s of cells/mL)',pch=21,bg=c(TAcol.bg,'white')[as.factor(ARC$Meso)],col=TAcol,cex=1.5)
legend(x='topleft',inset=c(0.03,0.03),legend=c('Control','+ M. rubrum'),pch=21,pt.cex=1.5,pt.bg=c(TAcol,'white'))

Summ.Prey <- summarySE(data=ARC, 'C.pmL.red', groupvars=c('Day.Numeric','Meso'))
arrows(Summ.Prey$Day.Numeric,Summ.Prey$C.pmL.red/1000+Summ.Prey$se/1000,Summ.Prey$Day.Numeric,Summ.Prey$C.pmL.red/1000-Summ.Prey$se/1000,code=3,angle=90,length=.02)
points(Summ.Prey$Day.Numeric,Summ.Prey$C.pmL.red/1000,pch=21,cex=1.5,bg=c(TAcol,'white')[as.factor(Summ.Prey$Meso)])

# Panel 3: Hemiselmis
plot(jitter(ARC$Day.Numeric,.2),ARC$C.pmL.blue/1000,las=1,xlab='Time (days)',ylab='H. pacifica (1000s of cells/mL)',pch=21,bg=c(HPcol.bg,'white')[as.factor(ARC$Meso)],col=HPcol,cex=1.5)
legend(x='topleft',inset=c(0.03,0.03),legend=c('Control','+ M. rubrum'),pch=21,pt.cex=1.5,pt.bg=c(HPcol,'white'))

Summ.Prey <- summarySE(data=ARC, 'C.pmL.blue', groupvars=c('Day.Numeric','Meso'))
arrows(Summ.Prey$Day.Numeric,Summ.Prey$C.pmL.blue/1000+Summ.Prey$se/1000,Summ.Prey$Day.Numeric,Summ.Prey$C.pmL.blue/1000-Summ.Prey$se/1000,code=3,angle=90,length=.02)
points(Summ.Prey$Day.Numeric,Summ.Prey$C.pmL.blue/1000,pch=21,cex=1.5,bg=c(HPcol,'white')[as.factor(Summ.Prey$Meso)])


# Panel 4: Proportion Hemiselmis
plot(jitter(ARC$Day.Numeric,.2),ARC$C.propblue,las=1,xlab='Time (days)',ylab='Proportion H. pacifica',pch=21,bg=c(Bothcol.bg,'white')[as.factor(ARC$Meso)],col=Bothcol,cex=1.5)
legend(x='topright',inset=c(0.03,0.03),legend=c('Control','+ M. rubrum'),pch=21,pt.cex=1.5,pt.bg=c(Bothcol,'white'))

Summ.Prey <- summarySE(data=ARC, 'C.propblue', groupvars=c('Day.Numeric','Meso'))
arrows(Summ.Prey$Day.Numeric,Summ.Prey$C.propblue+Summ.Prey$se,Summ.Prey$Day.Numeric,Summ.Prey$C.propblue-Summ.Prey$se,code=3,angle=90,length=.02)
points(Summ.Prey$Day.Numeric,Summ.Prey$C.propblue,pch=21,cex=1.5,bg=c(Bothcol,'white')[as.factor(Summ.Prey$Meso)])

```

### Calculate ingestion rates and test for preferential grazing

We'll follow Jeong & Latz 1994 and calculate ingestion rates based on the growth rates of prey in the absence and presence of predator. To perform this calculation, we'll need estimates of the growth rates for all species in all flasks.

```{r, fig.height=3,fig.width=8}

par(mar=c(4,4,1,1),mfrow=c(1,3))
summ.dat <- as.data.frame(unique(ARC$Flask))
colnames(summ.dat) <- 'Flask'
summ.dat$Meso <- ARC$Meso[match(summ.dat$Flask,ARC$Flask)]
summ.dat$Prey <- ARC$Prey[match(summ.dat$Flask,ARC$Flask)]
summ.dat$Replicate <- ARC$Replicate[match(summ.dat$Flask,ARC$Flask)]
summ.dat$TA.mu <- NaN
summ.dat$HP.mu <- NaN
summ.dat$MR.mu <- NaN

datewindow <- c(1:4)

for(i in 1:dim(summ.dat)[1]){
  FlaskID <- summ.dat$Flask[i]
  subdat <- ARC[ARC$Flask==summ.dat$Flask[i],]
  
  # TA growth curve
  plot(subdat$Time,subdat$C.pmL.red/1000,col=TAcol,pch=21,bg=TAcol.bg,log='y',xlab='Time (days)',ylab=expression(paste(italic('T. amphioxeia'),' (',10^3,' cells m',L^-1,')')),las=1)
  lmTA <- lm(log(subdat$C.pmL.red)[datewindow]~subdat$Time[datewindow])
  summ.dat$TA.mu[i] <- summary(lmTA)$coefficients[2,1]
  xcoords <- seq(from = min(subdat$Time,na.rm = T), to = max(subdat$Time,na.rm = T), length.out=50)
  ycoords <- exp(summary(lmTA)$coefficients[1,1])*exp(summ.dat$TA.mu[i]*xcoords)
  lines(xcoords,ycoords/1000)
  
  # HP growth curve
  plot(subdat$Time,subdat$C.pmL.blue/1000,col=HPcol,pch=21,bg=HPcol.bg,log='y',xlab='Time (days)',ylab=expression(paste(italic('H.pacifica'),' (',10^3,' cells m',L^-1,')')),las=1)
  lmHP <- lm(log(subdat$C.pmL.blue)[datewindow]~subdat$Time[datewindow])
  summ.dat$HP.mu[i] <- summary(lmHP)$coefficients[2,1]
  ycoords <- exp(summary(lmHP)$coefficients[1,1])*exp(summ.dat$HP.mu[i]*xcoords)
  lines(xcoords,ycoords/1000)
  
  # MR growth curve
  if(subdat$Meso[1]=='0000'){
    plot(1,1,type='n',bty='n',xaxt='n',yaxt='n',xlab='',ylab='')
  } else{
  plot(subdat$Time,subdat$M.pmL/1000,col=Bothcol,pch=21,bg=Bothcol.bg,log='y',xlab='Time (days)',ylab=expression(paste(italic('M. rubrum'),' (',10^3,' cells m',L^-1,')')),las=1)
  lmMR <- lm(log(subdat$M.pmL)[datewindow]~subdat$Time[datewindow])
  summ.dat$MR.mu[i] <- summary(lmMR)$coefficients[2,1]
  ycoords <- exp(summary(lmMR)$coefficients[1,1])*exp(summ.dat$MR.mu[i]*xcoords)
  lines(xcoords,ycoords/1000)
  }
  
  
}

```

Now, we'll match the prey control (predator-free) growth rates by replicate:

```{r}
summ.dat.ctrl <- summ.dat[summ.dat$Meso=='0000',]
summ.dat$ctrl.TA.mu <- summ.dat.ctrl$TA.mu[match(summ.dat$Replicate,summ.dat.ctrl$Replicate)]
summ.dat$ctrl.HP.mu <- summ.dat.ctrl$HP.mu[match(summ.dat$Replicate,summ.dat.ctrl$Replicate)]

```

The grazing rate, $g$, is the difference between the growth rate in the absence of the predator and the growth rate in the presence of the predator. It has units of per day: 

```{r}
summ.dat$g.TA <- summ.dat$ctrl.TA.mu-summ.dat$TA.mu
summ.dat$g.HP <- summ.dat$ctrl.HP.mu-summ.dat$HP.mu
```

To determine the ingestion rate, we also need to know the mean population sizes of both predators and prey. To determine this, we first match the population sizes at the start of the experiment.

```{r}
summ.dat$TA.d0 <- ARC[ARC$Day.Numeric==0,]$C.pmL.red
summ.dat$HP.d0 <- ARC[ARC$Day.Numeric==0,]$C.pmL.blue
summ.dat$MR.d0 <- ARC[ARC$Day.Numeric==0,]$M.pmL
```

Next, we assume exponential growth, and solve for the mean population size:

```{r}
summ.dat$TA.pop.72 <- summ.dat$TA.d0*(exp(summ.dat$TA.mu*3)-1) / (3 * summ.dat$TA.mu)
summ.dat$HP.pop.72 <- summ.dat$HP.d0*(exp(summ.dat$HP.mu*3)-1) / (3 * summ.dat$HP.mu)
summ.dat$MR.pop.72 <- summ.dat$MR.d0*(exp(summ.dat$MR.mu*3)-1) / (3 * summ.dat$MR.mu)
```

Finally, we can compute the ingestion rate: the number of cryptophytes consumed per Mesodinium per day:

```{r}
summ.dat$i.TA <- summ.dat$g.TA*summ.dat$TA.pop.72/summ.dat$MR.pop.72
summ.dat$i.HP <- summ.dat$g.HP*summ.dat$HP.pop.72/summ.dat$MR.pop.72
```

And the attack rate: the volume of water (in uL) filtered per each M. rubrum cell per day

```{r}
summ.dat$a.TA <- summ.dat$g.TA/summ.dat$MR.pop.72*1000
summ.dat$a.HP <- summ.dat$g.HP/summ.dat$MR.pop.72*1000
```

We can perform a statistical test to see whether the attack rates differ by prey type:

```{r}
t.test(summ.dat[summ.dat$Meso=='MRTA',]$a.TA,summ.dat[summ.dat$Meso=='MRTA',]$a.HP)
```
The p-value is 0.9292, which is much greater than 0.05. This means that, according to our experimental results and within the limits of statistical power set by our design, the attack rates are not significantly different from one another.

### Manuscript figure:
Top row: timeseries of population sizes and ratio
Bottom row: barplots of growth rate, mean population size, ingestion rate, and attack rate

```{r}
t.test(summ.dat[summ.dat$Meso=='0000',]$TA.mu,summ.dat[summ.dat$Meso=='0000',]$HP.mu) # p = 0.3728
t.test(summ.dat[summ.dat$Meso=='MRTA',]$TA.pop.72,summ.dat[summ.dat$Meso=='MRTA',]$HP.pop.72) # p = 0.003637
t.test(summ.dat[summ.dat$Meso=='MRTA',]$i.TA,summ.dat[summ.dat$Meso=='MRTA',]$i.HP) # p = 0.05589
t.test(summ.dat[summ.dat$Meso=='MRTA',]$a.TA,summ.dat[summ.dat$Meso=='MRTA',]$a.HP) # p = 0.9292
```

```{r,fig.height=6*.8,fig.width=8.5*.8}

pointcolor <- 'gray50'
pointcolor.bg <- 'gray80'

layout(matrix(data=c(1,1,2,2,3,4,5,6),nrow=2,ncol=4,byrow=T))
par(mar=c(4,4.5,1,1))

# Panel 1: Population dynamics
axlabcex <- 0.7
plot(jitter(ARC$Day.Numeric,.2),ARC$C.pmL.red/1000,las=1,xlab='',ylab='',pch=21,bg=c('white',pointcolor.bg)[as.factor(ARC$Meso)],col=pointcolor.bg,cex=1.5,log='y',ylim=c(1,50)) # ,type='n'
points(jitter(ARC$Day.Numeric,.2),ARC$C.pmL.blue/1000,pch=22,bg=c('white',pointcolor.bg)[as.factor(ARC$Meso)],col=pointcolor.bg,cex=1.5)
text(0,45,'(A)')
legend(x='topleft',inset=c(0.01,0.08),legend=c(expression(paste(italic('H. pac.'),' + ',italic('M. rubrum'))),expression(paste(italic('T. amph.'),' + ',italic('M. rubrum'))),expression(paste(italic('H. pac.'),' control')),expression(paste(italic('T. amph.'),' control'))),pch=c(22,21,22,21),pt.cex=1.5,pt.bg=c('black','black','white','white'),bty='n')
mtext(expression(paste('Cryptophyte population size')),side=2,line=3.4,cex=axlabcex)
mtext(expression(paste('(',10^3,' cells  ',mL^-1,')')),side=2,line=2,cex=axlabcex)
mtext('Time (d)',side=1,cex=axlabcex,line=2.3)

# Add Teleaulax points
Summ.Prey <- summarySE(data=ARC, 'C.pmL.red', groupvars=c('Day.Numeric','Meso'))
arrows(Summ.Prey$Day.Numeric,Summ.Prey$C.pmL.red/1000+Summ.Prey$se/1000,Summ.Prey$Day.Numeric,Summ.Prey$C.pmL.red/1000-Summ.Prey$se/1000,code=3,angle=90,length=.02)
lines(Summ.Prey[Summ.Prey$Meso=='0000',]$Day.Numeric,Summ.Prey[Summ.Prey$Meso=='0000',]$C.pmL.red/1000,lty=2)
lines(Summ.Prey[Summ.Prey$Meso=='MRTA',]$Day.Numeric,Summ.Prey[Summ.Prey$Meso=='MRTA',]$C.pmL.red/1000,lty=1)
points(Summ.Prey$Day.Numeric,Summ.Prey$C.pmL.red/1000,pch=21,cex=1.5,bg=c('white','black')[as.factor(Summ.Prey$Meso)])

# Add Hemiselmis points
Summ.Prey <- summarySE(data=ARC, 'C.pmL.blue', groupvars=c('Day.Numeric','Meso'))
arrows(Summ.Prey$Day.Numeric,Summ.Prey$C.pmL.blue/1000+Summ.Prey$se/1000,Summ.Prey$Day.Numeric,Summ.Prey$C.pmL.blue/1000-Summ.Prey$se/1000,code=3,angle=90,length=.02)
lines(Summ.Prey[Summ.Prey$Meso=='0000',]$Day.Numeric,Summ.Prey[Summ.Prey$Meso=='0000',]$C.pmL.blue/1000,lty=2)
lines(Summ.Prey[Summ.Prey$Meso=='MRTA',]$Day.Numeric,Summ.Prey[Summ.Prey$Meso=='MRTA',]$C.pmL.blue/1000,lty=1)
points(Summ.Prey$Day.Numeric,Summ.Prey$C.pmL.blue/1000,pch=22,cex=1.5,bg=c('white','black')[as.factor(Summ.Prey$Meso)])


# Panel 2: Ratio
plot(jitter(ARC$Day.Numeric,.2),ARC$C.propblue,las=1,xlab='',ylab=expression(paste('Proportion ',italic('H. pacifica'))),pch=21,bg=c('white',pointcolor.bg)[as.factor(ARC$Meso)],col=pointcolor.bg,cex=1.5,ylim=c(0.2,0.4))
legend(x='topright',inset=c(0.03,0.03),legend=c(expression(paste('+ ',italic('M. rubrum'))),'Control'),pch=21,pt.cex=1.5,pt.bg=c('black','white'),bty='n')
mtext('Time (d)',side=1,cex=axlabcex,line=2.3)
text(0,.395,'(B)')

Summ.Prey <- summarySE(data=ARC, 'C.propblue', groupvars=c('Day.Numeric','Meso'))
arrows(Summ.Prey$Day.Numeric,Summ.Prey$C.propblue+Summ.Prey$se,Summ.Prey$Day.Numeric,Summ.Prey$C.propblue-Summ.Prey$se,code=3,angle=90,length=.02)
lines(Summ.Prey[Summ.Prey$Meso=='0000',]$Day.Numeric,Summ.Prey[Summ.Prey$Meso=='0000',]$C.propblue,lty=2)
lines(Summ.Prey[Summ.Prey$Meso=='MRTA',]$Day.Numeric,Summ.Prey[Summ.Prey$Meso=='MRTA',]$C.propblue,lty=1)
points(Summ.Prey$Day.Numeric,Summ.Prey$C.propblue,pch=21,cex=1.5,bg=c('white','black')[as.factor(Summ.Prey$Meso)])




# Row 2: barplots
names2use <- c(expression(paste(italic('H. pac.'))),expression(paste(italic('T. amph.'))))
par(mar=c(6,4,1,1))
HPcol.bg <- 'gray70'
TAcol.bg <- 'white'

# Plot 1: Growth rates
growths <- as.data.frame(cbind(rep(c('TA','HP'),each=3),c(summ.dat[summ.dat$Meso=='0000',]$TA.mu,summ.dat[summ.dat$Meso=='0000',]$HP.mu)))
colnames(growths) <- c('Cryptophyte','GrowthRate')
growths$GrowthRate <- as.numeric(as.character(growths$GrowthRate))
bargraph.CI(Cryptophyte,GrowthRate,data=growths,las=1,xlab='',names=names2use,ylab='',col=c(HPcol.bg,TAcol.bg),space=0.1,ylim=c(0,.825))
mtext(expression(paste('Cryptophyte growth rate (',d^-1,')')),side=2,line=2.5,cex=axlabcex)
text(0.25,.795,'(C)')

# Plot 2: Population sizes
sizes <- as.data.frame(cbind(rep(c('TA','HP'),each=3),c(summ.dat[summ.dat$Meso=='MRTA',]$TA.pop.72,summ.dat[summ.dat$Meso=='MRTA',]$HP.pop.72)))
colnames(sizes) <- c('Cryptophyte','PopSize')
sizes$PopSize <- as.numeric(as.character(sizes$PopSize))
bargraph.CI(Cryptophyte,PopSize,data=sizes,las=1,xlab='',names=names2use,ylab='',col=c(HPcol.bg,TAcol.bg),space=.1,ylim=c(0,4500))
text(1.15,4400,'**',cex=1.5)
mtext('Cryptophyte prey species',side=1,line=2.3,cex = axlabcex,at=3)
mtext(expression(paste('Mean popn. size (cells  ',mL^-1,')')),side=2,line=3,cex=axlabcex)
text(0.25,4300,'(D)')

# Plot 3: Ingestion rates
ingests <- as.data.frame(cbind(rep(c('TA','HP'),each=3),c(summ.dat[summ.dat$Meso=='MRTA',]$i.TA,summ.dat[summ.dat$Meso=='MRTA',]$i.HP)))
colnames(ingests) <- c('Cryptophyte','IngestRate')
ingests$IngestRate <- as.numeric(as.character(ingests$IngestRate))
bargraph.CI(Cryptophyte,IngestRate,data=ingests,las=1,xlab='',names=names2use,ylab='',col=c(HPcol.bg,TAcol.bg),space=.1,ylim=c(0,1.75))
mtext(expression(paste('Ingestion (prey  ',italic('M. rub.')^-1,'  ',d^-1,')')),side=2,line=2.5,cex=axlabcex)
text(0.25,1.66,'(E)')

# Plot 4: Attack rates
attacks <- as.data.frame(cbind(rep(c('TA','HP'),each=3),c(summ.dat[summ.dat$Meso=='MRTA',]$a.TA,summ.dat[summ.dat$Meso=='MRTA',]$a.HP)))
colnames(attacks) <- c('Cryptophyte','AttackRate')
attacks$AttackRate <- as.numeric(as.character(attacks$AttackRate))
bargraph.CI(Cryptophyte,AttackRate,data=attacks,las=1,xlab='',names=names2use,ylab='',col=c(HPcol.bg,TAcol.bg),space=.1,ylim=c(0,.45))
mtext(expression(paste('Clearance rate (L  ',italic('M. rub.')^-1,'  ',d^-1,')')),side=2,line=2.5,cex=axlabcex)
text(0.2,.43,'(F)')
```



# Experiment 3: Long-term feeding

### FlowCam data analysis
```{r}
#Enter the location of your main folder for the current experiment.
#Alter this line to refer to the file location where the excel sheet is.
root_folder <- "/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/LongTermExpt/FlowCam/DataFiles"

#In the main folder create a folder name CSV_files, if named other wise change "/CSV_files" accordingly
CSV_folder <- paste(root_folder,"/CSV_files",sep = "")

#List the sub-folders of the current experiment, this would usually be one folder for each sampling day.
Folder_list <- c("D0","D1","D2","D3","D5","D7","D10","D12","D14","D16","D18","D20","D22")
#Folder_list <- c("D7")

expt.day <- Folder_list

knitr::opts_knit$set(root.dir = root_folder)

#A .csv file should be created with extra meta-data, such as data for sampling time and dilution. If other data is acquired, such as pigment extractions, include these in the this file as well.
expt.meta <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/LongTermExpt/FlowCam/Mrubrum_fedHP_FunctionalResponseCurves - LT_DilTime.csv")
```

```{r,fig.height=8,fig.width=8}
#Using the previously defined Folder_list, a for loop is created to access each folder one at a time, and within those folder each sample is then accessed one at a time.
#Each data set is being processed using the MRMC.partitioning function, which distinguished Red Chloroplast MC from blue-green Chloroplast MC. By using the meta-data stored in the file-name a new data-sheet is created with the desired data where each row is from a single sample from a single day.

create_plot_meso = F #If TRUE, the partitioning will output partitioned Ch1 vs Ch2 plots -- MESODINIUM VERSION
create_plot_prey = F #If TRUE, the partitioning will output partitioned Ch1 vs Ch2 plots -- PREY VERSION

unk.part.Meso = 5.5 # unknown partition for Mesodinium
bg.part.Meso = 4.5 # blue-green partition for Mesodinium
unk.part.prey = 0 # unknown partition for cryptophytes
bg.part.prey = 4.5 # blue-green partition for cryptophytes

#The first for-loop is created to open the folder of the individual sampling day in the order as they were defined (usually chronologically)
for(dir_idx in 1:length(Folder_list)){
  
  #The working directory is set to the folder containing one days worth of data.
  current_folder <- paste(root_folder,"/",Folder_list[dir_idx],sep = "")
  
  #Recording the current experimental day
  today <- expt.day[dir_idx]
  
  #here the columns to retrieve timestamp and dilution is defined.
  dil_name <- paste("Dil.",today,sep = "")
  time_name <- paste("TS.",today,sep = "")
  
  #The function list.files(current_folder), will create a list of files that are located in the folder, and by using this list of files, a new for-loop is created accessing each file consecutively.
  for(i in 1:length(list.files(current_folder))){
    
    #extracting meta data from the file name
    #Characters 1 to 7 is the Flask index
    name_flask <- substring(list.files(current_folder)[i],
                            first = 1,
                            last = 7)
    
    #assigning flask index as a number
    num_flask <- as.integer(substring(list.files(current_folder)[i],
                                      first = 6,
                                      last = 7))
    
    #Characters 9 to 12 is the Mesodinium pre-experiment plastid type
    Meso_designation <- substring(list.files(current_folder)[i],
                                  first = 9,
                                  last = 12)
    
    #Characters 14 through 18 indicate the prey being fed during the experiment
    prey_designation <- substring(list.files(current_folder)[i],
                                  first = 14,
                                  last = 15)
    
    #Character 20 is the replicate indicator
    expt_rep <- substring(list.files(current_folder)[i],
                          first = 20,
                          last = 20)
    
    #The dilution factor is extracted from the meta-data data-sheet in the root-folder
    flask_dil <- expt.meta[expt.meta$Flask == num_flask,
                           names(expt.meta) == dil_name]
    
    #Relative time from beginning of experiment is extracted
    flask_time <- expt.meta[expt.meta$Flask == num_flask,
                           names(expt.meta) == time_name]
    
    medium <- expt.meta[expt.meta$Flask == num_flask,"Medium"]
    
    #The .csv file is loaded here, and extra columns are added with the additional meta-data required for the data-processing
    file.name <- paste(current_folder,"/",list.files(current_folder)[i],sep = "")
    
    vec <- read.csv(file.name) %>% 
      mutate(Flask = name_flask,
             replicate = expt_rep,
             Meso = Meso_designation,
             Prey = prey_designation,
             Day = as.numeric(substring(expt.day[dir_idx],2)))
    
    #Because the flow-cam keeps counting the seconds when resetting the pump, a constant is multiplied to the Elapsed time to get the correct volume aspirated. This constant however was calculated from using the 0.5 ml pump, so a new value is probably needed for the 1 ml pump.
    Asp.vol <- (max(vec$Elapsed.Time*0.967)/60)*0.150
    
    #R-vector containing the raw data-set with both Mesodinium and Crypotphyte data
    vec.raw <- vec
    
    Meso_filter <- vec.raw$Class == "Mesodinium"
    
    #Creating an R-vector that only contains the data classified as Mesodinium
    vec <- vec.raw[Meso_filter,]
    
    #Creating an R-vector that only contains the data classified as Cryptophyte (or rather it only contains data that has not been classified as Meosdinium)
    vec2 <- vec.raw[!Meso_filter,]
    
    #On the first sample of each experimental day, an empty spreadsheet is created for both Prey and Mesodinium. This will be populated as the for-loop iterates through each sample.
    if(i == 1){
      FCDP_meso <- vec
      FCDP_prey <- vec2
      
      #Creating data-frame for partitioned data results
      All.Results <- as.data.frame(1:length(list.files(current_folder)))
      
      colnames(All.Results) <- c("Flask")     # Columns 1-8: Metadata
      All.Results$Day <- NaN
      All.Results$Time <- NaN                 
      All.Results$Dilution <- NaN             
      All.Results$Aspirated.vol <- NaN        
      All.Results$Meso <- NaN                 
      All.Results$Prey <- NaN                 
      All.Results$Replicate <- NaN            
      All.Results$Medium <- NaN               
      All.Results$M.Red <- NaN               # Columns 10-16; from Res$counts
      All.Results$M.Blue <- NaN              
      All.Results$M.Undefined <- NaN         
      All.Results$M.Nonfluorescent <- NaN
      All.Results$M.TotRed <- NaN
      All.Results$M.TotBlue <- NaN
      All.Results$TotalMeso <- NaN          
      All.Results$M.Red.meanCh1peak <- NaN               # Columns 17-20; from Res$Ch1.peaks
      All.Results$M.Blue.meanCh1peak <- NaN              
      All.Results$M.Undefined.meanCh1peak <- NaN         
      All.Results$M.Nonfluorescent.meanCh1peak <- NaN
      All.Results$M.Red.sdCh1peak <- NaN               # Columns 21-24; from Res$Ch1.sds
      All.Results$M.Blue.sdCh1peak <- NaN              
      All.Results$M.Undefined.sdCh1peak <- NaN         
      All.Results$M.Nonfluorescent.sdCh1peak <- NaN
      All.Results$M.Red.meanCh2peak <- NaN               # Columns 25-28; from Res$Ch2.peaks
      All.Results$M.Blue.meanCh2peak <- NaN              
      All.Results$M.Undefined.meanCh2peak <- NaN         
      All.Results$M.Nonfluorescent.meanCh2peak <- NaN  
      All.Results$M.Red.sdCh2peak <- NaN               # Columns 29-32; from Res$Ch2.sds
      All.Results$M.Blue.sdCh2peak <- NaN              
      All.Results$M.Undefined.sdCh2peak <- NaN         
      All.Results$M.Nonfluorescent.sdCh2peak <- NaN  
      
      #Adding columns for cryptophytes
      All.Results$C.Red <- NaN               # Columns 9-15; from Res$counts
      All.Results$C.Blue <- NaN              
      All.Results$C.Undefined <- NaN         
      All.Results$C.Nonfluorescent <- NaN
      All.Results$C.TotRed <- NaN
      All.Results$C.TotBlue <- NaN
      All.Results$TotalCrypto <- NaN          
      All.Results$C.Red.meanCh1peak <- NaN               # Columns 16-19; from Res$Ch1.peaks
      All.Results$C.Blue.meanCh1peak <- NaN              
      All.Results$C.Undefined.meanCh1peak <- NaN         
      All.Results$C.Nonfluorescent.meanCh1peak <- NaN
      All.Results$C.Red.sdCh1peak <- NaN               # Columns 20-23; from Res$Ch1.sds
      All.Results$C.Blue.sdCh1peak <- NaN              
      All.Results$C.Undefined.sdCh1peak <- NaN         
      All.Results$C.Nonfluorescent.sdCh1peak <- NaN
      All.Results$C.Red.meanCh2peak <- NaN               # Columns 24-27; from Res$Ch2.peaks
      All.Results$C.Blue.meanCh2peak <- NaN              
      All.Results$C.Undefined.meanCh2peak <- NaN         
      All.Results$C.Nonfluorescent.meanCh2peak <- NaN  
      All.Results$C.Red.sdCh2peak <- NaN               # Columns 28-31; from Res$Ch2.sds
      All.Results$C.Blue.sdCh2peak <- NaN              
      All.Results$C.Undefined.sdCh2peak <- NaN         
      All.Results$C.Nonfluorescent.sdCh2peak <- NaN  
      
    } else{
      FCDP_prey <- rbind(FCDP_prey,vec2)
      FCDP_meso <- rbind(FCDP_meso,vec)
    }
    
    # Add relevant data for this sample
    All.Results$Flask[i] <- name_flask
    All.Results$Day[i] <- today
    All.Results$Time[i] <- flask_time
    All.Results$Dilution[i] <- flask_dil
    All.Results$Aspirated.vol[i] <- round(Asp.vol,3)
    All.Results$Meso[i] <- Meso_designation
    All.Results$Prey[i] <- prey_designation
    All.Results$Replicate[i] <- expt_rep
    All.Results$Medium[i] <- medium
    
    #Running the partitioning function for Mesodinium

    if(dim(vec)[1] > 0){ # If there are Mesodinium in the dataset
      Res <- Meso.flowPeaks(vec,name_flask,today,create_plot = create_plot_meso,unknown.partition = unk.part.Meso, bluegreen.partition = bg.part.Meso)
      #Assigning partitioned data for Mesodinium
      All.Results[i,10:16] <- Res$counts
      All.Results[i,17:20] <- Res$Ch1.peaks
      All.Results[i,21:24] <- Res$Ch1.peaks.sd
      All.Results[i,25:28] <- Res$Ch2.peaks
      All.Results[i,29:32] <- Res$Ch2.peaks.sd
    }
    
    if(dim(vec2)[1] > 0){ # If there are cryptophytes in the dataset
      #Running flowPeaks for Prey
      Res.crypto <- Meso.flowPeaks(vec2,name_flask,today,create_plot = create_plot_prey,unknown.partition = unk.part.prey, bluegreen.partition = bg.part.prey)
      #Assigning partitioned data for Prey
      All.Results[i,33:39] <- Res.crypto$counts
      All.Results[i,40:43] <- Res.crypto$Ch1.peaks
      All.Results[i,44:47] <- Res.crypto$Ch1.peaks.sd
      All.Results[i,48:51] <- Res.crypto$Ch2.peaks
      All.Results[i,52:55] <- Res.crypto$Ch2.peaks.sd
    }
    
    if(i == length(list.files(current_folder))){
        FCDP_prey <- FCDP_prey %>% mutate(Partition = "Prey")
        FCDP_meso <- FCDP_meso %>% mutate(Partition = "Mesodinium")
        FCDP_all <- rbind(FCDP_meso,FCDP_prey)
      
      
      Res_name <- paste(CSV_folder,"/Summary_",expt.day[dir_idx],".csv",sep = "")
      FCDP_name <- paste(CSV_folder,"/FCDP_all_",expt.day[dir_idx],".csv",sep = "")
      
      write.csv(All.Results,Res_name,row.names = F)
      write.csv(FCDP_all,FCDP_name,row.names = F)
    }
  }
  
  if(dir_idx == 1){
    All.Results.Concat <- All.Results
  } else{
    All.Results.Concat <- rbind(All.Results.Concat, All.Results)
  }
  
  if(dir_idx == length(Folder_list)){
    All_res_name <- paste("All_Summary",".csv",sep='')
    write.csv(All.Results.Concat,All_res_name,row.names = F)
  }
  
}


```

```{r}
ARC <- All.Results.Concat[All.Results.Concat$Meso=="MRTA",] # Shortening the variable name
Preyref <- All.Results.Concat[All.Results.Concat$Meso=="0000",]

# Calculating concentrations of cells (in cells per mL), normalizing to the aspirated volume and adjusting for dilution
ARC$M.pmL <- ARC$TotalMeso/ARC$Aspirated.vol*ARC$Dilu
ARC$M.pmL.red <- ARC$M.TotRed/ARC$Aspirated.vol*ARC$Dilu
ARC$M.pmL.blue <- ARC$M.TotBlue/ARC$Aspirated.vol*ARC$Dilu

ARC$C.pmL <- ARC$TotalCrypto/ARC$Aspirated.vol*ARC$Dilu
ARC$C.pmL.red <- ARC$C.TotRed/ARC$Aspirated.vol*ARC$Dilu
ARC$C.pmL.blue <- ARC$C.TotBlue/ARC$Aspirated.vol*ARC$Dilu

# Calculating proportion of blue-green cryptophytes
ARC$C.propblue <- ARC$C.pmL.blue/ARC$C.pmL

# Rounding day to whole number so that we can group by timepoint in downstream calculations
ARC$Day.Numeric <- round(ARC$Time,digits=0)

```

### Fluorescence/plastid dynamics
#### Scatterplot of pigmentation
Use a subset of datapoints
```{r}
numcells2use <- 200

# Concatenate data
FCDP_name <- paste(CSV_folder,"/FCDP_all_",expt.day[1],".csv",sep = "")
FCDP <- read.csv(FCDP_name)
FCDP.Meso.00 <- FCDP[FCDP$Class=='Mesodinium' & FCDP$Prey=='00',]
if(dim(FCDP.Meso.00)[1] > numcells2use){
  rows2use <- sample(c(1:dim(FCDP.Meso.00)[1]),numcells2use)
  FCDP.Meso.00 <- FCDP.Meso.00[rows2use,]
}
FCDP.Meso.HP <- FCDP[FCDP$Class=='Mesodinium' & FCDP$Prey=='HP',]
if(dim(FCDP.Meso.HP)[1] > numcells2use){
  rows2use <- sample(c(1:dim(FCDP.Meso.HP)[1]),numcells2use)
  FCDP.Meso.HP <- FCDP.Meso.HP[rows2use,]
}

for(i in 2:length(expt.day)){
  FCDP_name <- paste(CSV_folder,"/FCDP_all_",expt.day[i],".csv",sep = "")
  FCDP <- read.csv(FCDP_name)
  FCDP.Meso.00.hold <- FCDP[FCDP$Class=='Mesodinium' & FCDP$Prey=='00',]
  if(dim(FCDP.Meso.00.hold)[1] > numcells2use){
    rows2use <- sample(c(1:dim(FCDP.Meso.00.hold)[1]),numcells2use)
    FCDP.Meso.00.hold <- FCDP.Meso.00.hold[rows2use,]
  }
  FCDP.Meso.HP.hold <- FCDP[FCDP$Class=='Mesodinium' & FCDP$Prey=='HP',]    
  if(dim(FCDP.Meso.HP.hold)[1] > numcells2use){
    rows2use <- sample(c(1:dim(FCDP.Meso.HP.hold)[1]),numcells2use)
    FCDP.Meso.HP.hold <- FCDP.Meso.HP.hold[rows2use,]
  }
  FCDP.Meso.00 <- rbind(FCDP.Meso.00,FCDP.Meso.00.hold)
  FCDP.Meso.HP <- rbind(FCDP.Meso.HP,FCDP.Meso.HP.hold)
}


```

Extract the fluorescent particles -- HP-fed
```{r}
# Step 1: Partition dataset to just fluorescent particles
dataset.fluo <- FCDP.Meso.HP[FCDP.Meso.HP$Ch1.Peak>0,]
dataset.fluo <- dataset.fluo[dataset.fluo$Ch2.Peak>0,]
  
# Step 2: Use flowPeaks package to fit and visualize the number of clusters of points
invisible(capture.output(fp <- suppressMessages(flowPeaks(dataset.fluo[,c("Ch1.Peak",'Ch2.Peak')],tol=.1,h0=.4))))
      # The "capture.output" function captures the printed output of the flowPeaks function
      # The "invisible" function suppresses that output so it doesn't automatically print.
      # The "suppressMessages" function suppresses the messages output of flowPeaks

# Step 3: Extract cluster assignments
dataset.fluo$peak <- fp$peaks.cluster

# Step 4: Assign clusters to colors (or unknown)
fp.data <- as.data.frame(summary(fp))
fp.data$plastid.color <- 'red' # Presume plastids are red in color
for(i in 1:dim(fp.data)[1]){
  if(fp.data$Ch1.Peak.center[i] < unk.part.Meso){ # If they fall below the unknown threshold, assign them "black" color for unknown
    fp.data$plastid.color[i] <- 'black'
  } else{ #If not unknown, then assign them "blue" color for bluegreen plastid type
  if(fp.data$Ch2.Peak.center[i] < bg.part.Meso){
    fp.data$plastid.color[i] <- 'blue'
  }
}}
dataset.fluo$peak.Ch1 <- fp.data$Ch1.Peak.center[match(dataset.fluo$peak,fp.data$cluster.id)]
dataset.fluo$peak.Ch2 <- fp.data$Ch2.Peak.center[match(dataset.fluo$peak,fp.data$cluster.id)]
dataset.fluo$plastidcolor <- fp.data$plastid.color[match(dataset.fluo$peak,fp.data$cluster.id)]
  
# Step 5: Map fluorescent data back onto the dataset for export.
dataset.analyzed <- FCDP.Meso.HP
dataset.analyzed$plastidcolor <- dataset.fluo$plastidcolor[match(dataset.analyzed$Capture.ID,dataset.fluo$Capture.ID)]
if(dim(dataset.analyzed[is.na(dataset.analyzed$plastidcolor),])[1]>0){
dataset.analyzed[is.na(dataset.analyzed$plastidcolor),]$plastidcolor <- 'nonfluorescent'}
dataset.analyzed$plastidcolor <- factor(dataset.analyzed$plastidcolor,levels=c('red','blue','black','nonfluorescent'))
  
# 1. Baseline plot of all data
    par(mfrow=c(2,2))
    par(mar=c(2,4,2.5,0.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,ylab='Channel 2 peak (phycoerythrin)')
    
    # 2. Plot of flowpeaks package partitions
    par(mar=c(2,2,2.5,2.5))
    plot(fp)
    
    # 3. Plot of data with cluster assignments
    par(mar=c(4,4,.5,.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,col=c('red','blue','cyan','green')[as.factor(dataset.fluo$peak)],xlab='Channel 1 peak (chlorophyll)',ylab='Channel 2 peak (phycoerythrin)')
    
    # 4. Plot of data assigned by plastid type
    par(mar=c(4,2,.5,2.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,col=dataset.fluo$plastidcolor,xlab='Channel 1 peak (chlorophyll)')

FCDP.Meso.HP.hasplastid <- dataset.fluo[dataset.fluo$plastidcolor!='black',]
```

Extract the fluorescent particles -- starved
```{r}
# Step 1: Partition dataset to just fluorescent particles
dataset.fluo <- FCDP.Meso.00[FCDP.Meso.00$Ch1.Peak>0,]
dataset.fluo <- dataset.fluo[dataset.fluo$Ch2.Peak>0,]
  
# Step 2: Use flowPeaks package to fit and visualize the number of clusters of points
invisible(capture.output(fp <- suppressMessages(flowPeaks(dataset.fluo[,c("Ch1.Peak",'Ch2.Peak')],tol=.1,h0=.4))))
      # The "capture.output" function captures the printed output of the flowPeaks function
      # The "invisible" function suppresses that output so it doesn't automatically print.
      # The "suppressMessages" function suppresses the messages output of flowPeaks

# Step 3: Extract cluster assignments
dataset.fluo$peak <- fp$peaks.cluster

# Step 4: Assign clusters to colors (or unknown)
fp.data <- as.data.frame(summary(fp))
fp.data$plastid.color <- 'red' # Presume plastids are red in color
for(i in 1:dim(fp.data)[1]){
  if(fp.data$Ch1.Peak.center[i] < unk.part.Meso){ # If they fall below the unknown threshold, assign them "black" color for unknown
    fp.data$plastid.color[i] <- 'black'
  } else{ #If not unknown, then assign them "blue" color for bluegreen plastid type
  if(fp.data$Ch2.Peak.center[i] < bg.part.Meso){
    fp.data$plastid.color[i] <- 'blue'
  }
}}
dataset.fluo$peak.Ch1 <- fp.data$Ch1.Peak.center[match(dataset.fluo$peak,fp.data$cluster.id)]
dataset.fluo$peak.Ch2 <- fp.data$Ch2.Peak.center[match(dataset.fluo$peak,fp.data$cluster.id)]
dataset.fluo$plastidcolor <- fp.data$plastid.color[match(dataset.fluo$peak,fp.data$cluster.id)]
  
# Step 5: Map fluorescent data back onto the dataset for export.
dataset.analyzed <- FCDP.Meso.00
dataset.analyzed$plastidcolor <- dataset.fluo$plastidcolor[match(dataset.analyzed$Capture.ID,dataset.fluo$Capture.ID)]
if(dim(dataset.analyzed[is.na(dataset.analyzed$plastidcolor),])[1]>0){
dataset.analyzed[is.na(dataset.analyzed$plastidcolor),]$plastidcolor <- 'nonfluorescent'}
dataset.analyzed$plastidcolor <- factor(dataset.analyzed$plastidcolor,levels=c('red','blue','black','nonfluorescent'))
  
# 1. Baseline plot of all data
    par(mfrow=c(2,2))
    par(mar=c(2,4,2.5,0.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,ylab='Channel 2 peak (phycoerythrin)')
    
    # 2. Plot of flowpeaks package partitions
    par(mar=c(2,2,2.5,2.5))
    plot(fp)
    
    # 3. Plot of data with cluster assignments
    par(mar=c(4,4,.5,.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,col=c('red','blue','cyan','green')[as.factor(dataset.fluo$peak)],xlab='Channel 1 peak (chlorophyll)',ylab='Channel 2 peak (phycoerythrin)')
    
    # 4. Plot of data assigned by plastid type
    par(mar=c(4,2,.5,2.5))
    plot(dataset.fluo$Ch1.Peak,dataset.fluo$Ch2.Peak,col=dataset.fluo$plastidcolor,xlab='Channel 1 peak (chlorophyll)')

FCDP.Meso.00.hasplastid <- dataset.fluo[dataset.fluo$plastidcolor!='black',]
```


```{r SFIG fluorescence scatterplot, fig.height=4, fig.width=9.5,warning=F}

xlimits <- c(5.3,6.5)
ylimits <- c(3.5,6.75)

TAto00cols2 <- colorRampPalette(c('indianred3','gray90'))
TAto00cols2 <- colorRampPalette(c(TAcol,'gray80'))
TAto00colset2 <- addalpha(TAto00cols2(length(expt.day)),.5)

TAtoHPcols2 <- colorRampPalette(c('indianred3','gray90','paleturquoise4'))
TAtoHPcols2 <- colorRampPalette(c(TAcol,'gray90',HPcol))
TAtoHPcolset2 <- addalpha(TAtoHPcols2(length(expt.day)),.5)

p1 <- FCDP.Meso.00.hasplastid %>%
  ggplot(aes(x=Ch1.Peak, y = Ch2.Peak, color=as.factor(Day)))+
  geom_point() +
  theme(legend.position='left', 
        panel.background = element_rect(color='gray20',size=1,fill='white'),
        panel.grid.major=element_line(colour="gray80"),
        panel.grid.minor=element_line(colour="gray80")) +
  scale_color_manual(values=TAto00colset2,name = "Day") +
  xlab('Channel 1 peak (chlorophyll fluorescence)') +
  ylab('Channel 2 peak (phycoerythrin fluorescence)') +
  scale_x_continuous(limits = xlimits) +
  scale_y_continuous(limits = ylimits) + 
  annotate("text", x=5.5, y=6.65, label= expression(paste('(A) Starved')), cex = 5) 
  #annotate("text", x=6.37, y=3.6, label= expression(paste('(A) Starved')), cex = 5) 
p2 <- ggMarginal(p1,type='histogram',groupColour=TRUE,groupFill=TRUE)
p5 <- ggMarginal(p1,groupColour=TRUE)#,groupFill=TRUE)


p3 <- FCDP.Meso.HP.hasplastid %>%
  ggplot(aes(x=Ch1.Peak, y = Ch2.Peak, color=as.factor(Day)))+
  geom_point() +
  theme(legend.position='left', 
        panel.background = element_rect(color='gray20',size=1,fill='white'),
        panel.grid.major=element_line(colour="gray80"),
        panel.grid.minor=element_line(colour="gray80")) +
  scale_color_manual(values=TAtoHPcolset2,name = "Day") +
  xlab('Channel 1 peak (chlorophyll fluorescence)') +
  ylab('Channel 2 peak (phycoerythrin fluorescence)') +
  scale_x_continuous(limits = xlimits) +
  scale_y_continuous(limits = ylimits) + 
  annotate("text", x=5.63, y=6.65, label= expression(paste('(B) Fed ',italic('H. pacifica'))), cex = 5) 
p6 <- ggMarginal(p3,type='histogram',groupColour=TRUE,groupFill=TRUE)
p7 <- ggMarginal(p3,groupColour=TRUE)#,groupFill=TRUE)

plot_grid(p5,p7)

```

#### Cell size

```{r SFIG cell size,fig.height=3,fig.width=4}
FCDP.Meso.00.hasplastid$Volscale <- FCDP.Meso.00.hasplastid$Volume..ABD./1000
FCDP.Meso.HP.hasplastid$Volscale <- FCDP.Meso.HP.hasplastid$Volume..ABD./1000
cellVol.00 <- summarySE(data=FCDP.Meso.00.hasplastid,'Volscale','Day',na.rm=T)
cellVol.HP <- summarySE(data=FCDP.Meso.HP.hasplastid,'Volscale','Day',na.rm=T)

par(mar=c(4,4,1,1))
plot(cellVol.00$Day,cellVol.00$Volscale,type='n',xlab='',ylab='',ylim=c(7,10.500),las=1)
mtext('Experimental Day',side=1,line=2.3)
mtext('Estimated cell volume',side=2,line=2.8)
arrows(cellVol.HP$Day,cellVol.HP$Volscale+cellVol.HP$se,cellVol.HP$Day,cellVol.HP$Volscale-cellVol.HP$se,code=3,angle=90,length=0.01,col='black')
arrows(cellVol.00$Day,cellVol.00$Volscale+cellVol.00$se,cellVol.00$Day,cellVol.00$Volscale-cellVol.00$se,code=3,angle=90,length=0.01,col='black')
lines(cellVol.00$Day,cellVol.00$Volscale)
lines(cellVol.HP$Day,cellVol.HP$Volscale)
points(cellVol.HP$Day,cellVol.HP$Volscale,pch=21,col='black',bg='black',cex=1.5)
points(cellVol.00$Day,cellVol.00$Volscale,pch=21,col='black',bg='white',cex=1.5)
legend(x='topleft',inset=c(0,0),legend=c('Starved',expression(paste('Fed ',italic('H. pacifica')))),bty='n',pch=21,pt.bg=c('white','black'),pt.cex=1.5)

```

With additional cell properties


```{r SFIG cell properties,fig.height=5,fig.width=3}

par(mar=c(0,4,4,1),mfrow=c(3,1))

FCDP.Meso.00.hasplastid$Volscale <- FCDP.Meso.00.hasplastid$Volume..ABD./1000
FCDP.Meso.HP.hasplastid$Volscale <- FCDP.Meso.HP.hasplastid$Volume..ABD./1000
cellVol.00 <- summarySE(data=FCDP.Meso.00.hasplastid,'Volscale','Day',na.rm=T)
cellVol.HP <- summarySE(data=FCDP.Meso.HP.hasplastid,'Volscale','Day',na.rm=T)

plot(cellVol.00$Day,cellVol.00$Volscale,type='n',xlab='',ylab='',ylim=c(6.5,11),las=1,xaxt='n'); axis(side=1,labels=F)
#mtext('Experimental Day',side=1,line=2.3)
mtext('Estimated cell volume',side=2,line=2.8,cex=.7)
arrows(cellVol.HP$Day,cellVol.HP$Volscale+cellVol.HP$se,cellVol.HP$Day,cellVol.HP$Volscale-cellVol.HP$se,code=3,angle=90,length=0.01,col='black')
arrows(cellVol.00$Day,cellVol.00$Volscale+cellVol.00$se,cellVol.00$Day,cellVol.00$Volscale-cellVol.00$se,code=3,angle=90,length=0.01,col='black')
lines(cellVol.00$Day,cellVol.00$Volscale)
lines(cellVol.HP$Day,cellVol.HP$Volscale)
points(cellVol.HP$Day,cellVol.HP$Volscale,pch=21,col='black',bg='black',cex=1.5)
points(cellVol.00$Day,cellVol.00$Volscale,pch=21,col='black',bg='white',cex=1.5)
legend(x='topleft',legend=c(''),title='(a)',bty='n',cex=1.1)

# Cell perimeter
FCDP.Meso.00.hasplastid$Volscale <- FCDP.Meso.00.hasplastid$Perimeter 
FCDP.Meso.HP.hasplastid$Volscale <- FCDP.Meso.HP.hasplastid$Perimeter

cellVol.00 <- summarySE(data=FCDP.Meso.00.hasplastid,'Volscale','Day',na.rm=T)
cellVol.HP <- summarySE(data=FCDP.Meso.HP.hasplastid,'Volscale','Day',na.rm=T)

par(mar=c(2,4,2,1))
plot(cellVol.00$Day,cellVol.00$Volscale,type='n',xlab='',ylab='',las=1,xaxt='n',ylim=c(103,122)); axis(side=1,labels=F)
mtext('Cell perimeter',side=2,line=2.8,cex=.7)
#mtext('Experimental Day',side=1,line=2.3)
arrows(cellVol.HP$Day,cellVol.HP$Volscale+cellVol.HP$se,cellVol.HP$Day,cellVol.HP$Volscale-cellVol.HP$se,code=3,angle=90,length=0.01,col='black')
arrows(cellVol.00$Day,cellVol.00$Volscale+cellVol.00$se,cellVol.00$Day,cellVol.00$Volscale-cellVol.00$se,code=3,angle=90,length=0.01,col='black')
lines(cellVol.00$Day,cellVol.00$Volscale)
lines(cellVol.HP$Day,cellVol.HP$Volscale)
points(cellVol.HP$Day,cellVol.HP$Volscale,pch=21,col='black',bg='black',cex=1.5)
points(cellVol.00$Day,cellVol.00$Volscale,pch=21,col='black',bg='white',cex=1.5)
legend(x='topleft',legend=c(''),title='(b)',bty='n',cex=1.1)

# Length:width ratio
FCDP.Meso.00.hasplastid$Volscale <- FCDP.Meso.00.hasplastid$Length/FCDP.Meso.00.hasplastid$Width 
FCDP.Meso.HP.hasplastid$Volscale <- FCDP.Meso.HP.hasplastid$Length/FCDP.Meso.HP.hasplastid$Width

cellVol.00 <- summarySE(data=FCDP.Meso.00.hasplastid,'Volscale','Day',na.rm=T)
cellVol.HP <- summarySE(data=FCDP.Meso.HP.hasplastid,'Volscale','Day',na.rm=T)

par(mar=c(4,4,0,1))
plot(cellVol.00$Day,cellVol.00$Volscale,type='n',xlab='',ylab='',las=1,ylim=c(1.21,1.35))
mtext('Experimental Day',side=1,line=2.3,cex=.7)
mtext('Cell length : width ratio',side=2,line=2.8,cex=.7)
arrows(cellVol.HP$Day,cellVol.HP$Volscale+cellVol.HP$se,cellVol.HP$Day,cellVol.HP$Volscale-cellVol.HP$se,code=3,angle=90,length=0.01,col='black')
arrows(cellVol.00$Day,cellVol.00$Volscale+cellVol.00$se,cellVol.00$Day,cellVol.00$Volscale-cellVol.00$se,code=3,angle=90,length=0.01,col='black')
lines(cellVol.00$Day,cellVol.00$Volscale)
lines(cellVol.HP$Day,cellVol.HP$Volscale)
points(cellVol.HP$Day,cellVol.HP$Volscale,pch=21,col='black',bg='black',cex=1.5)
points(cellVol.00$Day,cellVol.00$Volscale,pch=21,col='black',bg='white',cex=1.5)
legend(x='bottomright',inset=c(0,0),legend=c('Starved',expression(paste('Fed ',italic('H. pacifica')))),bty='n',pch=21,pt.bg=c('white','black'),pt.cex=1.5)
legend(x='topleft',legend=c(''),title='(c)',bty='n',cex=1.1)


```



#### Line plots of plastid content
Find composite fluorescence values
```{r}
ARC$M.meanch1peak <- (ARC$M.pmL.red*ARC$M.Red.meanCh1peak+ARC$M.pmL.blue*ARC$M.Blue.meanCh1peak)/ARC$M.pmL
ARC$M.meanch2peak <- (ARC$M.pmL.red*ARC$M.Red.meanCh2peak+ARC$M.pmL.blue*ARC$M.Blue.meanCh2peak)/ARC$M.pmL
for(i in 1:dim(ARC)[1]){
  if(is.na(ARC$M.meanch1peak[i])){
    if(is.na(ARC$M.Blue.meanCh1peak[i])){ 
      ARC$M.meanch1peak[i] <- ARC$M.Red.meanCh1peak[i]
    }
  }
  if(is.na(ARC$M.meanch2peak[i])){
    if(is.na(ARC$M.Blue.meanCh2peak[i])){
      ARC$M.meanch2peak[i] <- ARC$M.Red.meanCh2peak[i]
    }
  }
  if(is.na(ARC$M.meanch1peak[i])){
    if(is.na(ARC$M.Red.meanCh1peak[i])){
      ARC$M.meanch1peak[i] <- ARC$M.Blue.meanCh1peak[i]
    }
  }
  if(is.na(ARC$M.meanch2peak[i])){
    if(is.na(ARC$M.Red.meanCh2peak[i])){
      ARC$M.meanch2peak[i] <- ARC$M.Blue.meanCh2peak[i]
    }
  }
}

```

Using calibration to turn into prop cell volume with PC and PE plastids
```{r}
ARC$prop.PE.predict <- ((ARC$M.meanch2peak-sqrt.PE.b)/sqrt.PE.a)^2
ARC$prop.PC.predict <- (ARC$M.meanch1peak-lm.Chl.a-lm.Chl.c*ARC$prop.PE.predict)/lm.Chl.b
for(i in 1:dim(ARC)[1]){
  ARC$prop.PC.predict[i] <- max(0,ARC$prop.PC.predict[i])
}
ARC$prop.plastid.predict <- ARC$prop.PE.predict+ARC$prop.PC.predict
```

```{r FIG4 Long Term Plastid Dynamics, fig.height=2.5, fig.width=7.5,warning=F}
par(mar=c(4,4,1,1),mfrow=c(1,3))

pointcolor <- 'black'
pointcolor.bg <- 'gray80'


plot(jitter(ARC$Day.Numeric,.4),ARC$prop.PE.predict,las=1,xlab='Time (days)',ylab=expression(paste('Prop. cell volume ',italic('T. amphioxeia'),' plastids')),pch=21,bg=c('white',pointcolor.bg)[as.factor(ARC$Prey)],col=pointcolor.bg,cex=1.5)

Summ.Prey <- summarySE(data=ARC, 'prop.PE.predict', groupvars=c('Day.Numeric','Prey'))
arrows(Summ.Prey$Day.Numeric,Summ.Prey$prop.PE.predict+Summ.Prey$se,Summ.Prey$Day.Numeric,Summ.Prey$prop.PE.predict-Summ.Prey$se,code=3,angle=90,length=.02)
for(i in 1:length(unique(Summ.Prey$Prey))){
  subdat <- Summ.Prey[Summ.Prey$Prey==unique(Summ.Prey$Prey)[i],]
  lines(subdat$Day.Numeric,subdat$prop.PE.predict)
}
points(Summ.Prey$Day.Numeric,Summ.Prey$prop.PE.predict,pch=21,cex=1.5,bg=c('white',pointcolor)[as.factor(Summ.Prey$Prey)])

legend(x='bottomleft',inset=c(0.03,0.03),legend=c('Starved',expression(paste('Fed ',italic('H. pacifica')))),pch=21,col='black',pt.bg=c('white',pointcolor),pt.cex=1.5,cex=.8)
text(x=0.5,y=0.6,'(A)')


# Panel B: Phycocyanin plastids
plot(jitter(ARC$Day.Numeric,.4),ARC$prop.PC.predict,las=1,xlab='Time (days)',ylab=expression(paste('Prop. cell volume ',italic('H. pacifica'),' plastids')),pch=21,bg=c('white',pointcolor.bg)[as.factor(ARC$Prey)],col=pointcolor.bg,cex=1.5)

Summ.Prey <- summarySE(data=ARC, 'prop.PC.predict', groupvars=c('Day.Numeric','Prey'))
arrows(Summ.Prey$Day.Numeric,Summ.Prey$prop.PC.predict+Summ.Prey$se,Summ.Prey$Day.Numeric,Summ.Prey$prop.PC.predict-Summ.Prey$se,code=3,angle=90,length=.02)
for(i in 1:length(unique(Summ.Prey$Prey))){
  subdat <- Summ.Prey[Summ.Prey$Prey==unique(Summ.Prey$Prey)[i],]
  lines(subdat$Day.Numeric,subdat$prop.PC.predict)
}
points(Summ.Prey$Day.Numeric,Summ.Prey$prop.PC.predict,pch=21,cex=1.5,bg=c('white',pointcolor)[as.factor(Summ.Prey$Prey)])
text(x=0.5,y=0.207,'(B)')

# Panel C: All Plastids
plot(jitter(ARC$Day.Numeric,.4),ARC$prop.plastid.predict,las=1,xlab='Time (days)',ylab='Prop. cell volume containing plastids',pch=21,bg=c('white',pointcolor.bg)[as.factor(ARC$Prey)],col=pointcolor.bg,cex=1.5,ylim=c(0,0.61))

Summ.Prey <- summarySE(data=ARC, 'prop.plastid.predict', groupvars=c('Day.Numeric','Prey'))
arrows(Summ.Prey$Day.Numeric,Summ.Prey$prop.plastid.predict+Summ.Prey$se,Summ.Prey$Day.Numeric,Summ.Prey$prop.plastid.predict-Summ.Prey$se,code=3,angle=90,length=.02)
for(i in 1:length(unique(Summ.Prey$Prey))){
  subdat <- Summ.Prey[Summ.Prey$Prey==unique(Summ.Prey$Prey)[i],]
  lines(subdat$Day.Numeric,subdat$prop.plastid.predict)
}
points(Summ.Prey$Day.Numeric,Summ.Prey$prop.plastid.predict,pch=21,cex=1.5,bg=c('white',pointcolor)[as.factor(Summ.Prey$Prey)])
text(x=0.5,y=0.6,'(C)')
```


### Population dynamics
```{r}
# Read in cell count data
dat <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/LongTermExpt/Mrubrum_fedHP_FunctionalResponseCurves - LTExp_16Dec2023.csv")

# Read in photophysiology data
dat <- dat[!is.na(dat$Flask),]
fire <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/LongTermExpt/Mrubrum_fedHP_FunctionalResponseCurves - LTExp_PECurves.csv")
fire <- fire[fire$Exp=='LT',]

MRcolumns <- which(substr(colnames(dat),1,6)=='corMR.')
scaleMRcolumns <- which(substr(colnames(dat),1,9)=='altcorMR.')
HPcolumns <- which(substr(colnames(dat),1,3)=='HP.')
Ratiocolumns <- which(substr(colnames(dat),1,6)=='Ratio.')
Chlcolumns <- which(substr(colnames(dat),1,4)=='Chl.')
TotChlcolumns <- which(substr(colnames(dat),1,7)=='TotChl.')
days <- as.numeric(as.character(str_extract(colnames(dat[,MRcolumns]),  "\\d+$")))
days[10] <- 8.2
days.chl <- as.numeric(as.character(str_extract(colnames(dat[,Chlcolumns]),  "\\d+$")))

treats <- unique(dat$Treat)
flasks <- unique(dat$Flask)

feedpts <- c(2.3,3.3,5.3,7.1,11.1,13.1,14.3,16.3,18.4)
feedvols <- c(0.4,1,2,3,1,3,2,1,1)

dilupts <- c(8)

# Special parameters, etc
Cfix.mult <- 0.01728178 # The multiplier 0.01728178 converts from electrons per chlorophyll molecule per second into pg C per pg chlorophyll-a per hour
```

```{r SFIG long term population dynamics,fig.height=2.5,fig.width=7.5,warning=F}

par(mar=c(4,4,1,.5),mfrow=c(1,3))

ax.lab.cex <- 0.7

# M. rubrum data
plot(jitter(days,.4),dat[1,MRcolumns],las=1,xlab='',ylab='', type='n',ylim=c(min(dat[,MRcolumns],na.rm=T),max(dat[,MRcolumns],na.rm = T))/1000, xlim=c(min(days)-.1,max(days)+.1),log='y')
abline(v=dilupts,lty=3)
mtext(expression(paste(italic('M. rubrum'),' (',10^3,' cells ',mL^-1,')')),side=2,line=2.2,cex=ax.lab.cex)
mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
for(i in 1:length(treats)){
  subdat <- dat[dat$Treat==treats[i],]
  for(j in 1:dim(dat)[1]){
    points(jitter(days,0.4),subdat[j,MRcolumns]/1000,pch=21,bg=TAcols.bg[i],col=TAcol.bg,cex=1.5)
  }
  lines(days,colMeans(subdat[,MRcolumns],na.rm=T)/1000)
}
for(i in 1:length(days)){
  for(j in 1:length(treats)){
    subdat <- dat[dat$Treat==treats[j],]
    arrows(days[i],mean(subdat[,MRcolumns[i]],na.rm=T)/1000+se(subdat[,MRcolumns[i]])/1000,days[i],mean(subdat[,MRcolumns[i]],na.rm=T)/1000-se(subdat[,MRcolumns[i]])/1000, angle=90, code = 3, length=0.03)
    points(days[i],mean(subdat[,MRcolumns[i]],na.rm=T)/1000,pch=21,cex=1.5,col='black',bg=TAcols[j])
  }
}
text(dilupts-1.5,.95*rep(min(dat[,MRcolumns]/1000,na.rm=T),length(dilupts)),rep('Dilution',length(dilupts)),pos=4,srt=90)

# H. pacifica data
subdat <- dat[dat$Treat==2,]
plot(jitter(days,.4),subdat[1,HPcolumns],las=1,xlab='',ylab='', type='n',ylim=c(min(subdat[,HPcolumns],na.rm=T),max(subdat[,HPcolumns],na.rm = T))/1000,xlim=c(min(days)-.1,max(days)+.1),log='y')
abline(v=feedpts,lty=2)
abline(v=dilupts,lty=3)
mtext(expression(paste('Cryptophytes (',10^3,' cells ',mL^-1,')')),side=2,line=2,cex=ax.lab.cex)
mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
for(j in 1:dim(subdat)[1]){
    points(jitter(days,0.4),subdat[j,HPcolumns]/1000,pch=21,bg=HPcols.bg[2],col=HPcol.bg,cex=1.5)
}
lines(days,colMeans(subdat[,HPcolumns],na.rm=T)/1000)
for(i in 1:length(days)){
  arrows(days[i],mean(subdat[,HPcolumns[i]],na.rm=T)/1000+se(subdat[,HPcolumns[i]])/1000,days[i],mean(subdat[,HPcolumns[i]],na.rm=T)/1000-se(subdat[,HPcolumns[i]])/1000, angle=90, code = 3, length=0.03)
  points(days[i],mean(subdat[,HPcolumns[i]],na.rm=T)/1000,pch=21,cex=1.5,col='black',bg=HPcols[2])
}
text(feedpts+.3,rep(max(subdat[,HPcolumns]/1000)*1.03,length(feedpts)),rep('Pulse fed',length(feedpts)),pos=2,srt=90)
text(dilupts+.0,.93*rep(min(subdat[,HPcolumns]/1000,na.rm=T),length(dilupts)),rep('Dilution',length(dilupts)),pos=4,srt=90)

# Ratio
subdat <- dat[dat$Treat==2,]
plot(jitter(days,.4),subdat[1,Ratiocolumns],las=1,xlab='',ylab='', type='n',ylim=c(min(subdat[,Ratiocolumns],na.rm=T), max(subdat[,Ratiocolumns],na.rm = T)),xlim=c(min(days)-.1,max(days)+.1))
abline(v=feedpts,lty=2)
abline(v=dilupts,lty=3)
mtext(expression(paste('Cryptophytes : ',italic('M. rubrum'))),side=2,line=2.3,cex=ax.lab.cex)
mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
for(j in 1:dim(subdat)[1]){
    points(jitter(days,0.4),subdat[j,Ratiocolumns],pch=21,bg='gray80',col='gray60',cex=1.5)
}
lines(days,colMeans(subdat[,Ratiocolumns],na.rm=T))
for(i in 1:length(days)){
  arrows(days[i],mean(subdat[,Ratiocolumns[i]],na.rm=T)+se(subdat[,Ratiocolumns[i]]),days[i],mean(subdat[,Ratiocolumns[i]],na.rm=T)-se(subdat[,Ratiocolumns[i]]), angle=90, code = 3, length=0.03)
  points(days[i],mean(subdat[,Ratiocolumns[i]],na.rm=T),pch=21,cex=1.5,col='black',bg='gray30')
}
text(feedpts+.3,rep(max(subdat[,Ratiocolumns]*1.02,na.rm = T),length(feedpts)),rep('Pulse fed',length(feedpts)),pos=2,srt=90)
text(dilupts+.0,-.3,rep('Dilution',length(dilupts)),pos=4,srt=90)

```

### M. rubrum growth rate

```{r}
grwindow <- 4 # number of datapoints required for a growth rate calculation

numcalcs <- length(days) - grwindow + 1

gr.data <- as.data.frame(rep(flasks,each=numcalcs))
colnames(gr.data) <- 'Flask'
gr.data$Treat <- dat$Treat[match(gr.data$Flask,dat$Flask)]
gr.data$MeanDay <- NaN
gr.data$GrowthRate <- NaN
gr.data$GrowthRateErr <- NaN


for(i in 1:6){
  for(j in 1:numcalcs){
    if(sum(days[j:(j+grwindow-1)]%in%c(8,8.2))!=2){ # if the dilution point is not in the string of numbers
    gr.data$MeanDay[(i-1)*numcalcs + j] <- mean(days[j:(j+grwindow-1)])
    lm1 <- lm(t(log(dat[dat$Flask==flasks[i],MRcolumns[j:(j+grwindow-1)]]))~days[j:(j+grwindow-1)])
    gr.data$GrowthRate[(i-1)*numcalcs + j] <- summary(lm1)$coefficients[2,1]
    gr.data$GrowthRateErr[(i-1)*numcalcs + j] <- summary(lm1)$coefficients[2,2]
  }}}


```

```{r FIG M rubrum long term growth,fig.height=4,fig.width=8}

gr.data <- gr.data[!is.na(gr.data$GrowthRate),]

monochromecols <- c('white','black')
monochromecols.bg <- c('white','gray80')

par(mar=c(4,4,1,1),mfrow=c(1,2))

# M. rubrum data
plot(jitter(days,.4),dat[1,scaleMRcolumns],las=1,xlab='Experimental day',ylab='', type='n',ylim=c(min(dat[,scaleMRcolumns],na.rm=T),max(dat[,scaleMRcolumns],na.rm = T))/1000, xlim=c(min(days)-.1,max(days)+.1),log='y')
#abline(v=dilupts,lty=3)
mtext(expression(paste('Scaled ',italic('M. rubrum'),' popn. (',10^3,' cells ',mL^-1,')')),side=2,line=2,cex=1)
#mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
for(i in 1:length(treats)){
  subdat <- dat[dat$Treat==treats[i],]
  for(j in 1:dim(dat)[1]){
    points(jitter(days,0.4),subdat[j,scaleMRcolumns]/1000,pch=21,bg=monochromecols.bg[i],col=monochromecols.bg,cex=1.5)
  }
  lines(days,colMeans(subdat[,scaleMRcolumns],na.rm=T)/1000)
}
for(i in 1:length(days)){
  for(j in 1:length(treats)){
    subdat <- dat[dat$Treat==treats[j],]
    arrows(days[i],mean(subdat[,scaleMRcolumns[i]],na.rm=T)/1000+se(subdat[,scaleMRcolumns[i]])/1000,days[i],mean(subdat[,scaleMRcolumns[i]],na.rm=T)/1000-se(subdat[,scaleMRcolumns[i]])/1000, angle=90, code = 3, length=0.03)
    points(days[i],mean(subdat[,scaleMRcolumns[i]],na.rm=T)/1000,pch=21,cex=1.5,col='black',bg=monochromecols[j])
  }
}
text(0.25,37,'(A)')

# Growth rates
grwindow <- 7 # number of datapoints required for a growth rate calculation
numcalcs <- length(days) - grwindow + 1
gr.data <- as.data.frame(rep(flasks[1:6],each=numcalcs))
colnames(gr.data) <- 'Flask'
gr.data$Treat <- dat$Treat[match(gr.data$Flask,dat$Flask)]
gr.data$MeanDay <- NaN
gr.data$GrowthRate <- NaN
gr.data$GrowthRateErr <- NaN

for(i in 1:6){
  for(j in 1:numcalcs){
    gr.data$MeanDay[(i-1)*numcalcs + j] <- mean(days[j:(j+grwindow-1)])
    lm1 <- lm(t(log(dat[dat$Flask==flasks[i],scaleMRcolumns[j:(j+grwindow-1)]]))~days[j:(j+grwindow-1)])
    gr.data$GrowthRate[(i-1)*numcalcs + j] <- summary(lm1)$coefficients[2,1]
    gr.data$GrowthRateErr[(i-1)*numcalcs + j] <- summary(lm1)$coefficients[2,2]
}}

plot(jitter(gr.data$MeanDay,.5),gr.data$GrowthRate,las=1,xlab='Experimental day',ylab=expression(paste(italic('M. rubrum'),' growth rate (',d^-1,')')),pch=21,cex=1.5,bg=monochromecols.bg[as.factor(gr.data$Treat)],col='gray80')
growth.summ <- summarySE(data=gr.data,measurevar='GrowthRate',groupvars=c('MeanDay','Treat'))
#abline(v=dilupts,lty=3)
for(i in 1:length(treats)){
  subdat <- growth.summ[growth.summ$Treat==treats[i],]
  lines(subdat$MeanDay,subdat$GrowthRate)
  arrows(subdat$MeanDay,subdat$GrowthRate + subdat$se, subdat$MeanDay, subdat$GrowthRate - subdat$se, code=3, angle = 90, length = 0.03)
  points(subdat$MeanDay,subdat$GrowthRate,pch=21, cex= 1.5, col='black', bg = monochromecols[i])
}

legend(x='bottomleft',inset=c(-0.0,-0.02),legend=c('Starved',expression(paste('Fed ',italic('H. pacifica')))),pch=21,pt.cex=1.5,col='black',pt.bg=monochromecols,bty='n')

text(3.25,0.28,'(B)')
```

Stacked vertically
```{r FIG vertical M rubrum long term growth,fig.height=7,fig.width=4}

gr.data <- gr.data[!is.na(gr.data$GrowthRate),]

monochromecols <- c('white','black')
monochromecols.bg <- c('white','gray80')

par(mar=c(1,4,3,1),mfrow=c(2,1))

# M. rubrum data
plot(jitter(days,.4),dat[1,scaleMRcolumns],las=1,xlab='Experimental day',ylab='', type='n',ylim=c(min(dat[,scaleMRcolumns],na.rm=T),max(dat[,scaleMRcolumns],na.rm = T))/1000, xlim=c(min(days)-.1,max(days)+.1),log='y',xaxt='n')
axis(side=1,labels=F)
#abline(v=dilupts,lty=3)
mtext(expression(paste('Scaled ',italic('M. rubrum'),' popn. (',10^3,' cells ',mL^-1,')')),side=2,line=2,cex=1)
#mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
for(i in 1:length(treats)){
  subdat <- dat[dat$Treat==treats[i],]
  for(j in 1:dim(dat)[1]){
    points(jitter(days,0.4),subdat[j,scaleMRcolumns]/1000,pch=21,bg=monochromecols.bg[i],col=monochromecols.bg,cex=1.5)
  }
  lines(days,colMeans(subdat[,scaleMRcolumns],na.rm=T)/1000)
}
for(i in 1:length(days)){
  for(j in 1:length(treats)){
    subdat <- dat[dat$Treat==treats[j],]
    arrows(days[i],mean(subdat[,scaleMRcolumns[i]],na.rm=T)/1000+se(subdat[,scaleMRcolumns[i]])/1000,days[i],mean(subdat[,scaleMRcolumns[i]],na.rm=T)/1000-se(subdat[,scaleMRcolumns[i]])/1000, angle=90, code = 3, length=0.03)
    points(days[i],mean(subdat[,scaleMRcolumns[i]],na.rm=T)/1000,pch=21,cex=1.5,col='black',bg=monochromecols[j])
  }
}
text(0.25,37,'(A)')

par(mar=c(4,4,0,1))
# Growth rates
grwindow <- 7 # number of datapoints required for a growth rate calculation
numcalcs <- length(days) - grwindow + 1
gr.data <- as.data.frame(rep(flasks[1:6],each=numcalcs))
colnames(gr.data) <- 'Flask'
gr.data$Treat <- dat$Treat[match(gr.data$Flask,dat$Flask)]
gr.data$MeanDay <- NaN
gr.data$GrowthRate <- NaN
gr.data$GrowthRateErr <- NaN

for(i in 1:6){
  for(j in 1:numcalcs){
    gr.data$MeanDay[(i-1)*numcalcs + j] <- mean(days[j:(j+grwindow-1)])
    lm1 <- lm(t(log(dat[dat$Flask==flasks[i],scaleMRcolumns[j:(j+grwindow-1)]]))~days[j:(j+grwindow-1)])
    gr.data$GrowthRate[(i-1)*numcalcs + j] <- summary(lm1)$coefficients[2,1]
    gr.data$GrowthRateErr[(i-1)*numcalcs + j] <- summary(lm1)$coefficients[2,2]
}}

plot(jitter(gr.data$MeanDay,.5),gr.data$GrowthRate,las=1,xlab='',ylab=expression(paste(italic('M. rubrum'),' growth rate (',d^-1,')')),pch=21,cex=1.5,bg=monochromecols.bg[as.factor(gr.data$Treat)],col='gray80')
mtext('Experimental day',side=1,line=2.3)
growth.summ <- summarySE(data=gr.data,measurevar='GrowthRate',groupvars=c('MeanDay','Treat'))
#abline(v=dilupts,lty=3)
for(i in 1:length(treats)){
  subdat <- growth.summ[growth.summ$Treat==treats[i],]
  lines(subdat$MeanDay,subdat$GrowthRate)
  arrows(subdat$MeanDay,subdat$GrowthRate + subdat$se, subdat$MeanDay, subdat$GrowthRate - subdat$se, code=3, angle = 90, length = 0.03)
  points(subdat$MeanDay,subdat$GrowthRate,pch=21, cex= 1.5, col='black', bg = monochromecols[i])
}

legend(x='bottomleft',inset=c(-0.0,-0.02),legend=c('Starved',expression(paste('Fed ',italic('H. pacifica')))),pch=21,pt.cex=1.5,col='black',pt.bg=monochromecols,bty='n')

text(3.25,0.28,'(B)')
```

### Photophysiology
Fit PE curves to all data
```{r fit PE curves}
flasks <- unique(fire$Flask)
days.fire <- unique(fire$ExpDay)
fire$Flask.Day <- paste(fire$Flask,fire$ExpDay,sep='.')

# Create PE dataframe
PEres <- as.data.frame(cbind(rep(flasks,length(days.fire)),rep(days.fire,each=length(flasks))))
colnames(PEres) <- c('Flask','ExpDay')
PEres$Flask.Day <- paste(PEres$Flask,PEres$ExpDay,sep='.')
PEres$Treatment <- fire$Treatment[match(PEres$Flask,fire$Flask)]
PEres$Prey <- fire$Prey[match(PEres$Flask,fire$Flask)]
PEres$Rep <- fire$Rep[match(PEres$Flask,fire$Flask)]
PEres$TargetHP <- fire$TargetHP[match(PEres$Flask,fire$Flask)]


PEres$FvFm <- fire[fire$PAR==0,]$Fv.Fm[match(PEres$Flask.Day,fire[fire$PAR==0,]$Flask.Day)]
PEres$P.est <- NA
PEres$a.est <- NA
PEres$Pmax <- NA
PEres$Pmax.err <- NA
PEres$Pmax.p <- NA
PEres$a <- NA
PEres$a.err <- NA
PEres$a.p <- NA
PEres$Ek <- NA
PEres$P_I <- NA
PEres$P_I.C <- NA
PEres$P.interp <- NA

PARset <- seq(from =0, to = max(fire$PAR,na.rm=T), length.out = 100)  # Create a holding vector of light levels to use for plotting later

# Fit curves
for(i in 1:(dim(PEres)[1])){
	if((i-1)%%30 == 0){   # plot results in 30-panel figures
		par(mar=c(1,1,1,1),mfrow=c(5,6))
	}
	
	subdat <- fire[fire$Flask.Day==PEres$Flask.Day[i],]   # Subset the data
	
	if(!is.na(subdat$PAR[1])){
	
	plot(subdat$PAR, subdat$ETR,xlim=c(0,300),ylim=c(0,300)); text(max(PARset)*0.5,5,PEres$Flask.Day[i])  # Plot the raw data
	
	PEres$FvFm[i] <- subdat[subdat$PAR==0,]$Fv.Fm # Save FvFm
	
	for(j in 1:dim(subdat)[1]){if(subdat$ETR[j]<0){subdat$ETR[j]<- NaN}} #  Remove negative values for ETR
  # note: usually points with negative qpcoef are those that are difficult to fit. in some cases, you can comment the following line of code to include those points
  for(j in 1:dim(subdat)[1]){if(subdat$qp.coeff[j]<0){subdat$ETR[j]<- NaN}} #  Remove negative values for qp coef
  
	#for(j in 5:dim(subdat[1])){if(!is.nan(subdat$ETR[j-1])){if(!is.nan(subdat$ETR[j])){
	#  if(subdat$ETR[j] > 1.3*subdat$ETR[j-1]){subdat$ETR[j]<-NaN}}}

	
	P.est <- max(subdat$ETR,na.rm=TRUE)
	PEres$P.est[i] <- P.est
	a.est <- lm(subdat$ETR[1:3]~subdat$PAR[1:3])$coef[2]
  PEres$a.est[i] <- a.est
	
	points(subdat$PAR,subdat$ETR,col='red')
	
	rm(nls.summ)
	try({
	  nls.summ <- summary(nls(ETR ~ P * tanh(a * PAR / P), data= subdat, start = list(P = P.est, a = a.est),nls.control(tol=1e-7))) })  # Do curve fit; 'try' wrapper prevents an error from causing the program to crash
	
	if(exists("nls.summ")){ # Only save these data if the curve fit was successful
	PEres$Pmax[i] <- nls.summ$p[1,1]   # Save various statistical parameters
	PEres$Pmax.err[i] <- nls.summ$p[1,2]
	PEres$Pmax.p[i] <- nls.summ$p[1,4]
	PEres$a[i] <- nls.summ$p[2,1]
	PEres$a.err[i] <- nls.summ$p[2,2]
	PEres$a.p[i] <- nls.summ$p[2,4]
	PEres$P.interp[i] <- interp1(subdat$PAR,subdat$ETR,xi=20)
	
	predictset <- PEres$Pmax[i]*tanh(PEres$a[i]*PARset/PEres$Pmax[i])  
	lines(PARset,predictset, col='royalblue3')  # Overlay the curve fit
	predictset2 <- P.est*tanh(a.est*PARset/P.est)  
	lines(PARset,predictset2, col='green')  # Overlay the curve fit
  }}}

PEres$Ek <- PEres$Pmax / PEres$a
PEres$P_I <- PEres$Pmax * tanh(PEres$a * 20 / PEres$Pmax)
PEres$P_I.C <- PEres$P_I* Cfix.mult
PEres$P.interp.C <- PEres$P.interp* Cfix.mult

# Export data

# # # write.csv(PEres,'/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/LongTermExpt/PEres.csv')
```
We'll incorporate data from reference cryptophyte PE curves as well
```{r import reference prey PE curves}
HP.ref <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/Mrubrum_fedHP_FunctionalResponseCurves - Exp2_PECurves.csv")
HP.ref <- HP.ref[HP.ref$TargetMR==0&HP.ref$Treatment%in%c(3,5),]
HP.ref <- read.csv("/Users/hollyvm/GoogleSync/Mesodinium/Mrubrum_fedHP/LongTermExpt/Mrubrum_fedHP_FunctionalResponseCurves - LTExp_PECurves.csv")
TA.ref <- HP.ref[HP.ref$Treatment=='TA',]
HP.ref <- HP.ref[HP.ref$Treatment=='HP',]

```

```{r SFIG PE curve transition,fig.height=4, fig.width=8}
# Color spectrum for experimental days
TAto00cols2 <- colorRampPalette(c(TAcol,'gray80'))
TAto00colset2 <- addalpha(TAto00cols2(length(days.fire)),.5)
TAto00colset <- TAto00cols2(length(days.fire))

TAtoHPcols2 <- colorRampPalette(c(TAcol,'gray90',HPcol))
TAtoHPcolset2 <- addalpha(TAtoHPcols2(length(expt.day)),.5)
TAtoHPcolset <- TAtoHPcols2(length(expt.day))

PARset2 <- seq(from = 0, to = 340, length.out=200)

par(mar=c(4,3.5,1,0),mfrow=c(1,2))
# Panel 1: Treatment 1
subdat <- PEres[PEres$Treatment==1,]
subdat.fire <- fire[fire$Treatment==1,]
plot(subdat.fire$PAR,subdat.fire$ETR,xlim=c(0,333),ylim=c(0,295),type='n',xlab='',ylab='',las=1)
mtext(expression(paste('Electron transport rate (e- chl-',italic(a)^-1,' ',s^-1,')')),side=2,line=2.5)
for(i in 1:length(days.fire)){
  subdat.fire <- fire[fire$Treatment==1 & fire$ExpDay==days.fire[i],]
  points(subdat.fire$PAR,subdat.fire$ETR,pch=21,bg=TAto00colset2[i],col=TAto00colset2[i])
  nls.summ <- summary(nls(ETR ~ P * tanh(a * PAR / P), data= subdat.fire, start = list(P = P.est, a = a.est),nls.control(tol=1e-7)))
  Pmax.fit <- nls.summ$p[1,1]   # Save various statistical parameters
	a.fit <- nls.summ$p[2,1]
	predictset <- Pmax.fit*tanh(a.fit*PARset/Pmax.fit)  
	lines(PARset,predictset, col=TAto00colset[i],lwd=2)  # Overlay the curve fit
}
text(x=-10,y=285,'(A) Starved',pos=4)
text(x=293,y=265,'Day 0',pos=4,cex=.7)
text(x=293,y=193,'Day 10',pos=4,cex=.7,col=TAto00colset[7])
text(x=293,y=93,'Day 22',pos=4,cex=.7,col=TAto00colset[length(days.fire)])

# Add reference line from HP data
#points(HP.ref$PAR,HP.ref$ETR,col=addalpha(HPcol.bg,.2),bg=addalpha(HPcol.bg,.2),pch=21)
nls.summ <- summary(nls(ETR ~ P * tanh(a * PAR / P), data= HP.ref, start = list(P = P.est, a = a.est),nls.control(tol=1e-7)))
Pmax.fit <- nls.summ$p[1,1]   # Save various statistical parameters
a.fit <- nls.summ$p[2,1]
predictset <- Pmax.fit*tanh(a.fit*PARset2/Pmax.fit)  
lines(PARset2,predictset, col='gray30',lwd=2,lty=3)
text(335,Pmax.fit*.88,expression(paste('Free-living ',italic('H. pacifica'))),pos=2,cex=.7,col='black')

# Add reference line from TA data
#points(TA.ref$PAR,TA.ref$ETR,col=addalpha(TAcol.bg,.2),bg=addalpha(TAcol.bg,.2),pch=21)
nls.summ <- summary(nls(ETR ~ P * tanh(a * PAR / P), data= TA.ref, start = list(P = P.est, a = a.est),nls.control(tol=1e-7)))
Pmax.fit <- nls.summ$p[1,1]   # Save various statistical parameters
a.fit <- nls.summ$p[2,1]
predictset <- Pmax.fit*tanh(a.fit*PARset2/Pmax.fit)  
lines(PARset2,predictset, col='gray30',lwd=2,lty=2)
text(335,Pmax.fit*.96,expression(paste('Free-living ',italic('T. amphioxeia'))),pos=2,cex=.7,col='black')


# Panel 1: Treatment 1
par(mar=c(4,1,1,2.5))
subdat.fire <- fire[fire$Treatment==2,]
plot(subdat.fire$PAR,subdat.fire$ETR,xlim=c(0,333),ylim=c(0,295),type='n',xlab='',ylab='',las=1,yaxt='n')
axis(side=2,labels=F)
mtext(expression(paste('Light level (mol quanta ',m^-2,' ',s^-1,')')),side=1,line=2.3,at=-30)
for(i in 1:length(days.fire)){
  subdat.fire <- fire[fire$Treatment==2 & fire$ExpDay==days.fire[i],]
  points(subdat.fire$PAR,subdat.fire$ETR,pch=21,bg=TAtoHPcolset2[i],col=TAtoHPcolset2[i])
  nls.summ <- summary(nls(ETR ~ P * tanh(a * PAR / P), data= subdat.fire, start = list(P = P.est, a = a.est),nls.control(tol=1e-7)))
  Pmax.fit <- nls.summ$p[1,1]   # Save various statistical parameters
	a.fit <- nls.summ$p[2,1]
	predictset <- Pmax.fit*tanh(a.fit*PARset/Pmax.fit)  
	lines(PARset,predictset, col=TAtoHPcolset[i],lwd=2)  # Overlay the curve fit
}
text(x=-10,y=285,expression(paste('(B) Fed ',italic('H. pacifica'))),pos=4)
text(x=293,y=252,'Day 0',pos=4,cex=.7)
text(x=293,y=170,'Day 10',pos=4,cex=.7,col=TAto00colset[7])
text(x=293,y=60,'Day 22',pos=4,cex=.7,col=TAto00colset[length(days.fire)])

# Add reference line from HP data
#points(HP.ref$PAR,HP.ref$ETR,col=addalpha(HPcol.bg,.2),bg=addalpha(HPcol.bg,.2),pch=21)
nls.summ <- summary(nls(ETR ~ P * tanh(a * PAR / P), data= HP.ref, start = list(P = P.est, a = a.est),nls.control(tol=1e-7)))
Pmax.fit <- nls.summ$p[1,1]   # Save various statistical parameters
a.fit <- nls.summ$p[2,1]
predictset <- Pmax.fit*tanh(a.fit*PARset2/Pmax.fit)  
lines(PARset2,predictset, lwd=2,lty=3, col='gray30') #col=addalpha(HPcol.bg,.8),
#text(315,Pmax.fit*.85,expression(paste('Free-living ',italic('H. pacifica'))),pos=2,cex=.85,col='black')
HPfit <- nls.summ

# Add reference line from TA data
#points(TA.ref$PAR,TA.ref$ETR,col=addalpha(TAcol.bg,.2),bg=addalpha(TAcol.bg,.2),pch=21)
nls.summ <- summary(nls(ETR ~ P * tanh(a * PAR / P), data= TA.ref, start = list(P = P.est, a = a.est),nls.control(tol=1e-7)))
Pmax.fit <- nls.summ$p[1,1]   # Save various statistical parameters
a.fit <- nls.summ$p[2,1]
predictset <- Pmax.fit*tanh(a.fit*PARset2/Pmax.fit)  
lines(PARset2,predictset, col='gray30',lwd=2,lty=2)
#text(315,Pmax.fit*.93,expression(paste('Free-living ',italic('T. amphioxeia'))),pos=2,cex=.85,col='black')
TAfit <- nls.summ

```

```{r,fig.height=4, fig.width=8}
# Color spectrum for experimental days
TAto00cols2 <- colorRampPalette(c('black','gray80'))
TAto00colset2 <- addalpha(TAto00cols2(length(days.fire)),.5)
TAto00colset <- TAto00cols2(length(days.fire))

TAtoHPcols2 <- colorRampPalette(c('black','gray90'))
TAtoHPcolset2 <- addalpha(TAtoHPcols2(length(expt.day)),.5)
TAtoHPcolset <- TAtoHPcols2(length(expt.day))

PARset2 <- seq(from = 0, to = 340, length.out=200)

par(mar=c(4,3.5,1,0),mfrow=c(1,2))
# Panel 1: Treatment 1
subdat <- PEres[PEres$Treatment==1,]
subdat.fire <- fire[fire$Treatment==1,]
plot(subdat.fire$PAR,subdat.fire$ETR,xlim=c(0,333),ylim=c(0,295),type='n',xlab='',ylab='',las=1)
mtext(expression(paste('Electron transport rate (e- chl-',italic(a)^-1,' ',s^-1,')')),side=2,line=2.5)
for(i in 1:length(days.fire)){
  subdat.fire <- fire[fire$Treatment==1 & fire$ExpDay==days.fire[i],]
  points(subdat.fire$PAR,subdat.fire$ETR,pch=21,bg=TAto00colset2[i],col=TAto00colset2[i])
  nls.summ <- summary(nls(ETR ~ P * tanh(a * PAR / P), data= subdat.fire, start = list(P = P.est, a = a.est),nls.control(tol=1e-7)))
  Pmax.fit <- nls.summ$p[1,1]   # Save various statistical parameters
	a.fit <- nls.summ$p[2,1]
	predictset <- Pmax.fit*tanh(a.fit*PARset/Pmax.fit)  
	lines(PARset,predictset, col=TAto00colset[i],lwd=2)  # Overlay the curve fit
}
text(x=-10,y=285,'Starved',pos=4)
text(x=293,y=265,'Day 0',pos=4,cex=.7)
text(x=293,y=193,'Day 10',pos=4,cex=.7,col=TAto00colset[7])
text(x=293,y=93,'Day 22',pos=4,cex=.7,col=TAto00colset[length(days.fire)])

# Add reference line from HP data
#points(HP.ref$PAR,HP.ref$ETR,col=addalpha(HPcol.bg,.2),bg=addalpha(HPcol.bg,.2),pch=21)
nls.summ <- summary(nls(ETR ~ P * tanh(a * PAR / P), data= HP.ref, start = list(P = P.est, a = a.est),nls.control(tol=1e-7)))
Pmax.fit <- nls.summ$p[1,1]   # Save various statistical parameters
a.fit <- nls.summ$p[2,1]
predictset <- Pmax.fit*tanh(a.fit*PARset2/Pmax.fit)  
lines(PARset2,predictset, col='gray30',lwd=2,lty=2)
text(335,Pmax.fit*.88,expression(paste('Free-living ',italic('H. pacifica'))),pos=2,cex=.7,col='black')

# Add reference line from TA data
#points(TA.ref$PAR,TA.ref$ETR,col=addalpha(TAcol.bg,.2),bg=addalpha(TAcol.bg,.2),pch=21)
nls.summ <- summary(nls(ETR ~ P * tanh(a * PAR / P), data= TA.ref, start = list(P = P.est, a = a.est),nls.control(tol=1e-7)))
Pmax.fit <- nls.summ$p[1,1]   # Save various statistical parameters
a.fit <- nls.summ$p[2,1]
predictset <- Pmax.fit*tanh(a.fit*PARset2/Pmax.fit)  
lines(PARset2,predictset, col='gray30',lwd=2,lty=2)
text(335,Pmax.fit*.96,expression(paste('Free-living ',italic('T. amphioxeia'))),pos=2,cex=.7,col='black')


# Panel 1: Treatment 1
par(mar=c(4,1,1,2.5))
subdat.fire <- fire[fire$Treatment==2,]
plot(subdat.fire$PAR,subdat.fire$ETR,xlim=c(0,333),ylim=c(0,295),type='n',xlab='',ylab='',las=1,yaxt='n')
axis(side=2,labels=F)
mtext(expression(paste('Light level (mol quanta ',m^-2,' ',s^-1,')')),side=1,line=2.3,at=-30)
for(i in 1:length(days.fire)){
  subdat.fire <- fire[fire$Treatment==2 & fire$ExpDay==days.fire[i],]
  points(subdat.fire$PAR,subdat.fire$ETR,pch=21,bg=TAtoHPcolset2[i],col=TAtoHPcolset2[i])
  nls.summ <- summary(nls(ETR ~ P * tanh(a * PAR / P), data= subdat.fire, start = list(P = P.est, a = a.est),nls.control(tol=1e-7)))
  Pmax.fit <- nls.summ$p[1,1]   # Save various statistical parameters
	a.fit <- nls.summ$p[2,1]
	predictset <- Pmax.fit*tanh(a.fit*PARset/Pmax.fit)  
	lines(PARset,predictset, col=TAtoHPcolset[i],lwd=2)  # Overlay the curve fit
}
text(x=-10,y=285,expression(paste('Fed ',italic('H. pacifica'))),pos=4)
text(x=293,y=252,'Day 0',pos=4,cex=.7)
text(x=293,y=170,'Day 10',pos=4,cex=.7,col=TAto00colset[7])
text(x=293,y=60,'Day 22',pos=4,cex=.7,col=TAto00colset[length(days.fire)])

# Add reference line from HP data
#points(HP.ref$PAR,HP.ref$ETR,col=addalpha(HPcol.bg,.2),bg=addalpha(HPcol.bg,.2),pch=21)
nls.summ <- summary(nls(ETR ~ P * tanh(a * PAR / P), data= HP.ref, start = list(P = P.est, a = a.est),nls.control(tol=1e-7)))
Pmax.fit <- nls.summ$p[1,1]   # Save various statistical parameters
a.fit <- nls.summ$p[2,1]
predictset <- Pmax.fit*tanh(a.fit*PARset2/Pmax.fit)  
lines(PARset2,predictset, lwd=2,lty=2, col='gray30') #col=addalpha(HPcol.bg,.8),
#text(315,Pmax.fit*.85,expression(paste('Free-living ',italic('H. pacifica'))),pos=2,cex=.85,col='black')
HPfit <- nls.summ

# Add reference line from TA data
#points(TA.ref$PAR,TA.ref$ETR,col=addalpha(TAcol.bg,.2),bg=addalpha(TAcol.bg,.2),pch=21)
nls.summ <- summary(nls(ETR ~ P * tanh(a * PAR / P), data= TA.ref, start = list(P = P.est, a = a.est),nls.control(tol=1e-7)))
Pmax.fit <- nls.summ$p[1,1]   # Save various statistical parameters
a.fit <- nls.summ$p[2,1]
predictset <- Pmax.fit*tanh(a.fit*PARset2/Pmax.fit)  
lines(PARset2,predictset, col='gray30',lwd=2,lty=2)
#text(315,Pmax.fit*.93,expression(paste('Free-living ',italic('T. amphioxeia'))),pos=2,cex=.85,col='black')
TAfit <- nls.summ

```


Chlorophyll content and photophysiology metrics. 

```{r,fig.height=2.5*2,fig.width=7.5,warning=F}
Chlcols <- c('white','black')
Chlcols.bg <- c('white','gray70')
Chlcol.bg <- 'gray70'

par(mfrow=c(2,3))

ax.lab.cex <- 0.7

jittamt <- 1

# First row
par(mar=c(1,4,4,.5))
# Chlorophyll per cell
plot(jitter(days.chl,jittamt),dat[1,Chlcolumns],las=1,xlab='',ylab='', type='n',ylim=c(min(dat[,Chlcolumns],na.rm=T),max(dat[,Chlcolumns],na.rm = T)), xlim=c(min(days.chl)-.1,max(days.chl)+.1),xaxt='n'); axis(side=1,labels=F)
mtext(expression(paste('Cellular chlorophyll (pg chl-',italic('a'),' ',cell^-1,')')),side=2,line=2.2,cex=ax.lab.cex)
#mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
for(i in 1:length(treats)){
  subdat <- dat[dat$Treat==treats[i],]
  for(j in 1:dim(dat)[1]){
    points(jitter(days.chl,0.4),subdat[j,Chlcolumns],pch=21,bg=Chlcols.bg[i],col=Chlcol.bg,cex=1.5)
  }
  lines(days.chl,colMeans(subdat[,Chlcolumns]))
}
for(i in 1:length(days.chl)){
  for(j in 1:length(treats)){
    subdat <- dat[dat$Treat==treats[j],]
    arrows(days.chl[i],mean(subdat[,Chlcolumns[i]])+se(subdat[,Chlcolumns[i]]),days.chl[i],mean(subdat[,Chlcolumns[i]])-se(subdat[,Chlcolumns[i]]), angle=90, code = 3, length=0.03)
    points(days.chl[i],mean(subdat[,Chlcolumns[i]]),pch=21,cex=1.5,col='black',bg=Chlcols[j])
  }
}
legend(x='topright',inset=c(.01,.01), legend=c('Starved',expression(paste('Fed ',italic('H. pacifica')))),pch=21,pt.bg=Chlcols,pt.cex=1.5, bty='n')
text(0.3,33,'(A)')

# # Chlorophyll per mL
# Chlcol.bg <- 'black'
# 
# plot(jitter(days.chl,jittamt),dat[1,TotChlcolumns],las=1,xlab='',ylab='', type='n',ylim=c(min(dat[,TotChlcolumns],na.rm=T),max(dat[,TotChlcolumns],na.rm = T)), xlim=c(min(days.chl)-.1,max(days.chl)+.1))
# mtext(expression(paste('Total chlorophyll (ng chl-',italic('a'),' ',mL^-1,')')),side=2,line=2.2,cex=ax.lab.cex)
# mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
# for(i in 1:length(treats)){
#   subdat <- dat[dat$Treat==treats[i],]
#   for(j in 1:dim(dat)[1]){
#     points(jitter(days.chl,0.4),subdat[j,TotChlcolumns],pch=21,bg=Chlcols.bg[i],col=Chlcol.bg,cex=1.5)
#   }
#   lines(days.chl,colMeans(subdat[,TotChlcolumns]))
# }
# for(i in 1:length(days.chl)){
#   for(j in 1:length(treats)){
#     subdat <- dat[dat$Treat==treats[j],]
#     arrows(days.chl[i],mean(subdat[,TotChlcolumns[i]])+se(subdat[,TotChlcolumns[i]]),days.chl[i],mean(subdat[,TotChlcolumns[i]])-se(subdat[,TotChlcolumns[i]]), angle=90, code = 3, length=0.03)
#     points(days.chl[i],mean(subdat[,TotChlcolumns[i]]),pch=21,cex=1.5,col='black',bg=Chlcols[j])
#   }
# }


# Fv/Fm
plot(jitter(PEres$ExpDay,jittamt),PEres$FvFm,las=1,xlab='',ylab='', pch=21, col=Chlcol.bg, bg = Chlcols.bg[as.factor(PEres$Treatment)], cex=1.5, xlim=c(min(PEres$ExpDay)-.1,max(PEres$ExpDay)+.1),ylim=c(.41,.58),xaxt='n'); axis(side=1,labels=F)
mtext(expression(paste('Photosynthetic efficiency, (',F[v],' / ',F[m],')')),side=2,line=2.6,cex=ax.lab.cex)
#mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
FvFmsumm <- summarySE(data = PEres, 'FvFm',groupvars=c('ExpDay','Treatment'))
for(i in 1:length(treats)){
  subdat <- FvFmsumm[FvFmsumm$Treatment==treats[i],]
  lines(subdat$ExpDay,subdat$FvFm)
  arrows(subdat$ExpDay, subdat$FvFm+subdat$se, subdat$ExpDay, subdat$FvFm-subdat$se, angle=90, code = 3, length=0.03)
  points(subdat$ExpDay,subdat$FvFm, cex=1.5, col='black',bg=Chlcols[i], pch=21)
}
# HP reference
abline(h = mean(HP.ref[HP.ref$PAR==0,]$Fv.Fm),lty=3)
# TA reference
abline(h = mean(TA.ref[HP.ref$PAR==0,]$Fv.Fm),lty=2)
points(0.3,.58,pch=22,bg='white',col='white',cex=2); text(0.3,0.575,'(B)')

# P_I.C
plot(jitter(PEres$ExpDay,jittamt),PEres$P_I.C,las=1,xlab='',ylab='', pch=21, col=Chlcol.bg, bg = Chlcols.bg[as.factor(PEres$Treatment)], cex=1.5, xlim=c(min(PEres$ExpDay)-.1,max(PEres$ExpDay)+.1),ylim=c(.3,.58),xaxt='n')
axis(side=1,labels=F)
mtext(expression(paste('Phot. rate, ',P[I][,][C],' (pg C pg chl-',italic('a')^-1,' h',r^-1,')')),side=2,line=2.6,cex=ax.lab.cex)
#mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
FvFmsumm <- summarySE(data = PEres, 'P_I.C',groupvars=c('ExpDay','Treatment'))
for(i in 1:length(treats)){
  subdat <- FvFmsumm[FvFmsumm$Treatment==treats[i],]
  lines(subdat$ExpDay,subdat$P_I.C)
  arrows(subdat$ExpDay, subdat$P_I.C+subdat$se, subdat$ExpDay, subdat$P_I.C-subdat$se, angle=90, code = 3, length=0.03)
  points(subdat$ExpDay,subdat$P_I.C, cex=1.5, col='black',bg=Chlcols[i], pch=21)
}
# HP reference
abline(h = HPfit$p[1,1] * tanh(HPfit$p[2,1] * 20 / HPfit$p[1,1])* Cfix.mult,lty=3)
# TA reference
abline(h = TAfit$p[1,1] * tanh(TAfit$p[2,1] * 20 / TAfit$p[1,1])* Cfix.mult,lty=2)
points(0.3,.57,pch=21,bg='white',col='white',cex=3); text(0.3,0.57,'(C)')

# Second row
par(mar=c(4,4,1,.5))

# Pmax
#Chlcol.bg <- 'gray70'

plot(jitter(PEres$ExpDay,jittamt),PEres$Pmax,las=1,xlab='',ylab='', pch=21, col=Chlcol.bg, bg = Chlcols.bg[as.factor(PEres$Treatment)], cex=1.5, xlim=c(min(PEres$ExpDay)-.1,max(PEres$ExpDay)+.1))
mtext(expression(paste('Max. phot., ',P[m][a][x],' (e- molec. chl-',italic('a')^-1,' ',s^-1,')')),side=2,line=2.6,cex=ax.lab.cex)
mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
FvFmsumm <- summarySE(data = PEres, 'Pmax',groupvars=c('ExpDay','Treatment'))
for(i in 1:length(treats)){
  subdat <- FvFmsumm[FvFmsumm$Treatment==treats[i],]
  lines(subdat$ExpDay,subdat$Pmax)
  arrows(subdat$ExpDay, subdat$Pmax+subdat$se, subdat$ExpDay, subdat$Pmax-subdat$se, angle=90, code = 3, length=0.03)
  points(subdat$ExpDay,subdat$Pmax, cex=1.5, col='black',bg=Chlcols[i], pch=21)
}
# HP reference
abline(h = HPfit$p[1,1],lty=3)
# TA reference
abline(h = TAfit$p[1,1],lty=2)
points(0.3,293,pch=21,bg='white',col='white',cex=3); text(0.3,293,'(D)')

# a
plot(jitter(PEres$ExpDay,jittamt),PEres$a,las=1,xlab='',ylab='', pch=21, col=Chlcol.bg, bg = Chlcols.bg[as.factor(PEres$Treatment)], cex=1.5, xlim=c(min(PEres$ExpDay)-.1,max(PEres$ExpDay)+.1),ylim=c(0.9,1.8))
mtext(expression(paste('Light sensitivity, a')),side=2,line=2.9,cex=ax.lab.cex)
mtext(expression(paste('(e- ',m^2,' mol chl-',italic('a')^-1,' ',quanta^-1,')')),side=2,line=1.9,cex=ax.lab.cex)
mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
FvFmsumm <- summarySE(data = PEres, 'a',groupvars=c('ExpDay','Treatment'))
for(i in 1:length(treats)){
  subdat <- FvFmsumm[FvFmsumm$Treatment==treats[i],]
  lines(subdat$ExpDay,subdat$a)
  arrows(subdat$ExpDay, subdat$a+subdat$se, subdat$ExpDay, subdat$a-subdat$se, angle=90, code = 3, length=0.03)
  points(subdat$ExpDay,subdat$a, cex=1.5, col='black',bg=Chlcols[i], pch=21)
}
# HP reference
abline(h = HPfit$p[2,1],lty=3)
# TA reference
abline(h = TAfit$p[2,1],lty=2)
points(0.3,1.785,pch=21,bg='white',col='white',cex=3); text(0.3,1.785,'(E)')

# E_k
plot(jitter(PEres$ExpDay,jittamt),PEres$Ek,las=1,xlab='',ylab='', pch=21, col=Chlcol.bg, bg = Chlcols.bg[as.factor(PEres$Treatment)], cex=1.5, xlim=c(min(PEres$ExpDay)-.1,max(PEres$ExpDay)+.1))
mtext(expression(paste('Saturating light intensity, ',E[k])),side=2,line=2.6,cex=ax.lab.cex)
mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
FvFmsumm <- summarySE(data = PEres, 'Ek',groupvars=c('ExpDay','Treatment'))
for(i in 1:length(treats)){
  subdat <- FvFmsumm[FvFmsumm$Treatment==treats[i],]
  lines(subdat$ExpDay,subdat$Ek)
  arrows(subdat$ExpDay, subdat$Ek+subdat$se, subdat$ExpDay, subdat$Ek-subdat$se, angle=90, code = 3, length=0.03)
  points(subdat$ExpDay,subdat$Ek, cex=1.5, col='black',bg=Chlcols[i], pch=21)
}
# HP reference
abline(h = HPfit$p[1,1]/HPfit$p[2,1],lty=3)
# TA reference
abline(h = TAfit$p[1,1]/TAfit$p[2,1],lty=2)
text(-1.5,HPfit$p[1,1]/HPfit$p[2,1]*1.07,expression(paste('Free-living ',italic('H. pacifica'))),pos=4,cex=1,col='black')
text(23.5,TAfit$p[1,1]/TAfit$p[2,1]*1.02,expression(paste('Free-living ',italic('T. amphioxeia'))),pos=2,cex=1,col='black')
points(0.3,192,pch=21,bg='white',col='white',cex=3); text(0.3,192,'(F)')
```


Cleaner version

```{r,fig.height=2.5*2,fig.width=7.5,warning=F}
Chlcols <- c('white','black')
Chlcols.bg <- c('white','gray70')
Chlcol.bg <- 'gray70'

par(mar=c(4,4,1,.5),mfrow=c(2,3))

ax.lab.cex <- 0.7

jittamt <- 1

# Chlorophyll per cell
plot(jitter(days.chl,jittamt),dat[1,Chlcolumns],las=1,xlab='',ylab='', type='n', xlim=c(min(days.chl)-.1,max(days.chl)+.1), ylim=c(10,32))
mtext(expression(paste('Cellular chlorophyll (pg chl-',italic('a'),' ',cell^-1,')')),side=2,line=2.2,cex=ax.lab.cex)
mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
for(i in 1:length(treats)){
  subdat <- dat[dat$Treat==treats[i],]
  for(j in 1:dim(dat)[1]){
    #points(jitter(days.chl,0.4),subdat[j,Chlcolumns],pch=21,bg=Chlcols.bg[i],col=Chlcol.bg,cex=1.5)
  }
  lines(days.chl,colMeans(subdat[,Chlcolumns]))
}
for(i in 1:length(days.chl)){
  for(j in 1:length(treats)){
    subdat <- dat[dat$Treat==treats[j],]
    arrows(days.chl[i],mean(subdat[,Chlcolumns[i]])+se(subdat[,Chlcolumns[i]]),days.chl[i],mean(subdat[,Chlcolumns[i]])-se(subdat[,Chlcolumns[i]]), angle=90, code = 3, length=0.03)
    points(days.chl[i],mean(subdat[,Chlcolumns[i]]),pch=21,cex=1.5,col='black',bg=Chlcols[j])
  }
}
legend(x='topright',inset=c(.01,.01), legend=c('Starved',expression(paste('Fed ',italic('H. pacifica')))),pch=21,pt.bg=Chlcols,pt.cex=1.5)

# Chlorophyll per mL
plot(jitter(days.chl,jittamt),dat[1,TotChlcolumns],las=1,xlab='',ylab='', type='n',ylim=c(min(dat[,TotChlcolumns],na.rm=T),max(dat[,TotChlcolumns],na.rm = T)), xlim=c(min(days.chl)-.1,max(days.chl)+.1))
mtext(expression(paste('Total chlorophyll (ng chl-',italic('a'),' ',mL^-1,')')),side=2,line=2.4,cex=ax.lab.cex)
mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
for(i in 1:length(treats)){
  subdat <- dat[dat$Treat==treats[i],]
  for(j in 1:dim(dat)[1]){
    #points(jitter(days.chl,0.4),subdat[j,TotChlcolumns],pch=21,bg=Chlcols.bg[i],col=Chlcol.bg,cex=1.5)
  }
  lines(days.chl,colMeans(subdat[,TotChlcolumns]))
}
for(i in 1:length(days.chl)){
  for(j in 1:length(treats)){
    subdat <- dat[dat$Treat==treats[j],]
    arrows(days.chl[i],mean(subdat[,TotChlcolumns[i]])+se(subdat[,TotChlcolumns[i]]),days.chl[i],mean(subdat[,TotChlcolumns[i]])-se(subdat[,TotChlcolumns[i]]), angle=90, code = 3, length=0.03)
    points(days.chl[i],mean(subdat[,TotChlcolumns[i]]),pch=21,cex=1.5,col='black',bg=Chlcols[j])
  }
}


# Fv/Fm
plot(jitter(PEres$ExpDay,jittamt),PEres$FvFm,las=1,xlab='',ylab='', pch=21, col=Chlcol.bg, bg = Chlcols.bg[as.factor(PEres$Treatment)], cex=1.5, xlim=c(min(PEres$ExpDay)-.1,max(PEres$ExpDay)+.1),type='n',ylim=c(0.42,0.58))
# HP reference
abline(h = mean(HP.ref[HP.ref$PAR==0,]$Fv.Fm),lty=3)
# TA reference
abline(h = mean(TA.ref[HP.ref$PAR==0,]$Fv.Fm),lty=2)
mtext(expression(paste('Photosynthetic efficiency, (',F[v],' / ',F[m],')')),side=2,line=2.6,cex=ax.lab.cex)
mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
FvFmsumm <- summarySE(data = PEres, 'FvFm',groupvars=c('ExpDay','Treatment'))
for(i in 1:length(treats)){
  subdat <- FvFmsumm[FvFmsumm$Treatment==treats[i],]
  lines(subdat$ExpDay,subdat$FvFm)
  arrows(subdat$ExpDay, subdat$FvFm+subdat$se, subdat$ExpDay, subdat$FvFm-subdat$se, angle=90, code = 3, length=0.03)
  points(subdat$ExpDay,subdat$FvFm, cex=1.5, col='black',bg=Chlcols[i], pch=21)
}


# P_I.C
plot(jitter(PEres$ExpDay,jittamt),PEres$P_I.C,las=1,xlab='',ylab='', pch=21, col=Chlcol.bg, bg = Chlcols.bg[as.factor(PEres$Treatment)], cex=1.5, xlim=c(min(PEres$ExpDay)-.1,max(PEres$ExpDay)+.1),type='n',ylim=c(.32,.58))
# HP reference
abline(h = HPfit$p[1,1] * tanh(HPfit$p[2,1] * 20 / HPfit$p[1,1])* Cfix.mult,lty=3)
# TA reference
abline(h = TAfit$p[1,1] * tanh(TAfit$p[2,1] * 20 / TAfit$p[1,1])* Cfix.mult,lty=2)
mtext(expression(paste('Phot. rate, ',P[I][,][C],' (pg C pg chl-',italic('a')^-1,' h',r^-1,')')),side=2,line=2.6,cex=ax.lab.cex)
mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
FvFmsumm <- summarySE(data = PEres, 'P_I.C',groupvars=c('ExpDay','Treatment'))
for(i in 1:length(treats)){
  subdat <- FvFmsumm[FvFmsumm$Treatment==treats[i],]
  lines(subdat$ExpDay,subdat$P_I.C)
  arrows(subdat$ExpDay, subdat$P_I.C+subdat$se, subdat$ExpDay, subdat$P_I.C-subdat$se, angle=90, code = 3, length=0.03)
  points(subdat$ExpDay,subdat$P_I.C, cex=1.5, col='black',bg=Chlcols[i], pch=21)
}

# Pmax
plot(jitter(PEres$ExpDay,jittamt),PEres$Pmax,las=1,xlab='',ylab='', pch=21, col=Chlcol.bg, bg = Chlcols.bg[as.factor(PEres$Treatment)], cex=1.5, xlim=c(min(PEres$ExpDay)-.1,max(PEres$ExpDay)+.1),type='n')
# HP reference
abline(h = HPfit$p[1,1],lty=3)
# TA reference
abline(h = TAfit$p[1,1],lty=2)
mtext(expression(paste('Max. phot., ',P[m][a][x],' (e- molec. chl-',italic('a')^-1,' ',s^-1,')')),side=2,line=2.4,cex=ax.lab.cex)
mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
FvFmsumm <- summarySE(data = PEres, 'Pmax',groupvars=c('ExpDay','Treatment'))
for(i in 1:length(treats)){
  subdat <- FvFmsumm[FvFmsumm$Treatment==treats[i],]
  lines(subdat$ExpDay,subdat$Pmax)
  arrows(subdat$ExpDay, subdat$Pmax+subdat$se, subdat$ExpDay, subdat$Pmax-subdat$se, angle=90, code = 3, length=0.03)
  points(subdat$ExpDay,subdat$Pmax, cex=1.5, col='black',bg=Chlcols[i], pch=21)
}

# # a
# plot(jitter(PEres$ExpDay,jittamt),PEres$a,las=1,xlab='',ylab='', pch=21, col=Chlcol.bg, bg = Chlcols.bg[as.factor(PEres$Treatment)], cex=1.5, xlim=c(min(PEres$ExpDay)-.1,max(PEres$ExpDay)+.1))
# mtext(expression(paste('Light sensitivity, a')),side=2,line=2.6,cex=ax.lab.cex)
# mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
# FvFmsumm <- summarySE(data = PEres, 'a',groupvars=c('ExpDay','Treatment'))
# for(i in 1:length(treats)){
#   subdat <- FvFmsumm[FvFmsumm$Treatment==treats[i],]
#   lines(subdat$ExpDay,subdat$a)
#   arrows(subdat$ExpDay, subdat$a+subdat$se, subdat$ExpDay, subdat$a-subdat$se, angle=90, code = 3, length=0.03)
#   points(subdat$ExpDay,subdat$a, cex=1.5, col='black',bg=Chlcols[i], pch=21)
# }

# E_k
plot(jitter(PEres$ExpDay,jittamt),PEres$Ek,las=1,xlab='',ylab='', pch=21, col=Chlcol.bg, bg = Chlcols.bg[as.factor(PEres$Treatment)], cex=1.5, xlim=c(min(PEres$ExpDay)-.1,max(PEres$ExpDay)+.1),type='n')
mtext(expression(paste('Saturating light intensity, ',E[k])),side=2,line=2.6,cex=ax.lab.cex)
mtext('Time (days)',side=1,line=2,cex=ax.lab.cex)
# HP reference
abline(h = HPfit$p[1,1]/HPfit$p[2,1],lty=3)
# TA reference
abline(h = TAfit$p[1,1]/TAfit$p[2,1],lty=2)
text(-1.5,HPfit$p[1,1]/HPfit$p[2,1]*1.07,expression(paste('Free-living ',italic('H. pacifica'))),pos=4,cex=1,col='black')
text(23.5,TAfit$p[1,1]/TAfit$p[2,1]*1.02,expression(paste('Free-living ',italic('T. amphioxeia'))),pos=2,cex=1,col='black')
FvFmsumm <- summarySE(data = PEres, 'Ek',groupvars=c('ExpDay','Treatment'))
for(i in 1:length(treats)){
  subdat <- FvFmsumm[FvFmsumm$Treatment==treats[i],]
  lines(subdat$ExpDay,subdat$Ek)
  arrows(subdat$ExpDay, subdat$Ek+subdat$se, subdat$ExpDay, subdat$Ek-subdat$se, angle=90, code = 3, length=0.03)
  points(subdat$ExpDay,subdat$Ek, cex=1.5, col='black',bg=Chlcols[i], pch=21)
}



```
